### 2017-12-22 paper/paper.tex
create latex template for paper and technical documentation

\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\graphicspath{ {images/} }

%% Language and font encodings
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

%% Sets page size and margins
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
\setlength{\parskip}{1em}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{csquotes}
\usepackage{graphicx}
\usepackage{setspace}

% Abkuerzungsverzeichnis
\usepackage{acronym}

% Specify bibliography package
\usepackage{csquotes}% Recommended
\usepackage[style=apa,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

% Section Title Margins
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
\titlespacing*{\subsection}
{0pt}{1.4ex}{0pt}

\title{Review of Assigned Readings}
\author{Your Name Goes Here}

    \begin{document}
    \begin{titlepage}
        \centering
        {\scshape\LARGE University of St.Gallen \par}
        \vspace{1cm}
        {\scshape\Large Software Engineering for Economists \par}
        \vspace{1.3cm}
        {\huge\bfseries Name of Project  \par}
        \vspace{3cm}
        {\Large\itshape Joël Sonderegger\par}
        \begin{spacing}{1.2}
        joel.sonderegger{@}student.unisg.ch\linebreak
        11-495-488\linebreak

        \vspace{1cm}
        Fall Term 2017
        \vfill
        Supervisor
        \linebreak
        Prof. Dr. Philipp \textsc{Zahn}
        \linebreak
        Department of Economics
        \end{spacing}

        \vfill

    % Bottom of the page
     {\large \today\par}

    \end{titlepage}
    \begin{abstract}
    \pagenumbering{Roman}
    \begin{spacing}{1.5}

  (Insert text)

    \end{spacing}

    \end{abstract}

    \clearpage
    \tableofcontents

    \clearpage

    \listoffigures

    \clearpage

\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Section 1}

\subsection{Subsection 1}

\cend{spacing}
\clearpage

\printbibliography

\end{document}

### 2017-12-23 aggregate_twitter_bpi.py
add functionatly to merge number of tweets per hour with bitcoin price index (bpi) data. And generate csv-file containing that merged data.

@@ -10,20 +10,42 @@ import pprint
 import csv
 import io
 
+from datetime import datetime
+from dateutil.parser import parse
 
-# Gets tweets from CSV-File. Returns a list of tweets (of type dict)
+# Gets tweets from CSV-File. Returns a data frame with tweets
 def load_tweets():
     df = pd.read_csv('data/twitterData.csv')
 
     return df
 
+# Gets bpi data from CSV-File. Returns a data frame with bpi data
+def load_bpi():
+    bpi_data = pd.read_csv('data/bpi.csv')
+
+    # create new column 'close'. The close price is the open price of the previous hour
+    bpi_data['close'] = bpi_data['open']
+    bpi_data['close'] = bpi_data['close'].shift(-1)
+    
+    # Set time as DataFrame index.
+    times = bpi_data.set_index(pd.DatetimeIndex(bpi_data['time']))
+    
+    bpi_data = bpi_data.set_index([times.index.year, times.index.month, times.index.day, times.index.hour])
+ 
+    # set correct index names for Y, M, D, H
+    bpi_data.index = bpi_data.index.set_names('Y', level=0)
+    bpi_data.index = bpi_data.index.set_names('M', level=1)
+    bpi_data.index = bpi_data.index.set_names('D', level=2)
+    bpi_data.index = bpi_data.index.set_names('H', level=3)
+  
+
+    return bpi_data
 
 # Order Tweets by Date and return as list of dicts. For each day there is one dict that contains (1) a date and (2) a list of containing all tweets
 # {'date': '23-23-4302', "tweets" : ["bla","bla","bla"]}
-
 def count_tweets_per_hour(tweets):
 
-    # drop the tweet text as the timestamp are enough to count the number of tweets
+    # drop the tweet texts as the timestamp are enough to count the number of tweets
     tweets.drop('text', axis=1, inplace=True)
 
     # use create_at as the index of the df tweets
@@ -32,6 +54,7 @@ def count_tweets_per_hour(tweets):
     #group by year, month, day and hour
     grouped_tweets_per_hour = tweets.groupby([times.index.year, times.index.month, times.index.day, times.index.hour]).count()
     
+
     # set correct index names for Y, M, D, H
     grouped_tweets_per_hour.index = grouped_tweets_per_hour.index.set_names('Y', level=0)
     grouped_tweets_per_hour.index = grouped_tweets_per_hour.index.set_names('M', level=1)
@@ -40,23 +63,54 @@ def count_tweets_per_hour(tweets):
 
[…]

### 2017-12-26 paper/paper.tex
I took the babel package out of the paper.tex to be able to run it on my compiler. Nothing valuable lost

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[a4paper,american,12pt]{article}
 \usepackage{graphicx}
@@
 \usepackage[utf8]{inputenc}
-\usepackage[american]{babel}
 
@@
 \usepackage{setspace}
+\usepackage[noconfigs,british]{babel}
 
@@
         \centering
-        {\scshape\LARGE University of St.Gallen \par}
+        {\scshape\LARGE University of St.Gallen \\ \large School of Management, Economics, Law, Social Schiences and International Affairs \par}
+        \vspace{2cm}
+        {\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
+		\vspace{1.5cm}        
+        {\large\today\par}
+        \vspace{1.5cm}
+        {\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
+        \vspace{1.5cm}
+        {\itshape\large Alen Stepic - XX-XXX-XXX \\Chi Xu - XX-XXX-XXX \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - XX-XXX-XX \par}
+
+        \begin{spacing}{1.5}
         \vspace{1cm}
-        {\scshape\Large Software Engineering for Economists \par}
-        \vspace{1.3cm}
-        {\huge\bfseries Name of Project  \par}
-        \vspace{3cm}
-        {\Large\itshape Joël Sonderegger\par}
-        \begin{spacing}{1.2}
-        joel.sonderegger{@}student.unisg.ch\linebreak
-        11-495-488\linebreak
+        {Fall Term 2017 \par}
+        \vspace{1cm}
+        Supervisor\\
+        {Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par} 
+        \end{spacing}
+    \end{titlepage}
 
-        \vspace{1cm}
-        Fall Term 2017
-        \vfill
-        Supervisor
-        \linebreak
-        Prof. Dr. Philipp \textsc{Zahn}
-        \linebreak
-        Department of Economics
-        \end{spacing}
-
-        \vfill
-
-    % Bottom of the page
-     {\large \today\par}
-
-    \end{titlepage}
     \begin{abstract}
@@
 
-\cend{spacing}
+\end{spacing}
 \clearpage

### 2017-12-26 CollectCryptocurrencyData.py
.gitignore file extended for LaTeX projects aux files

@@ -7,7 +7,7 @@
 """
 
 
-import urllib2
+
 import numpy as np
 import json
 import datetime

### 2017-12-26 aggregate_twitter_bpi.py

@@ -15,8 +15,7 @@ from dateutil.parser import parse
 
 # Gets tweets from CSV-File. Returns a data frame with tweets
 def load_tweets():
-    df = pd.read_csv('data/twitterData.csv')
-
+    df = pd.read_csv('data/20171223_0056_twitterData.csv')
     return df
 
 # Gets bpi data from CSV-File. Returns a data frame with bpi data
@@ -105,6 +104,7 @@ def main():
 
     # count number of tweets per hour
     tweets_per_hour = count_tweets_per_hour(tweets)
+    print('Counting the number of tweets. This can take a while...')
     
     # merge number of tweets per hour with bitcoin price index (bpi) data
     df_merged = tweets_per_hour.join(bpi_data, how='left')

### 2017-12-26 aggregate_twitter_bpi.py
delete redundant latex files

@@ -104,7 +104,7 @@ def main():
 
     # count number of tweets per hour
     tweets_per_hour = count_tweets_per_hour(tweets)
-    print('Counting the number of tweets. This can take a while...')
+    print('Counting the number of tweets. This can take some minutes...')
     
     # merge number of tweets per hour with bitcoin price index (bpi) data
     df_merged = tweets_per_hour.join(bpi_data, how='left')

### 2017-12-26 paper/paper.tex
delete redundant latex files
change location of date on paper title page

@@
 \usepackage{graphicx}
-\graphicspath{ {images/} }
+\graphicspath{{images/}}
 
@@
 % Specify bibliography package
-\usepackage{csquotes}% Recommended
+\usepackage{csquotes}
 \usepackage[style=apa,backend=biber]{biblatex}
@@
 \begin{document}
+
     \begin{titlepage}
@@
     {\scshape\LARGE University of St.Gallen \\ \large School of Management, Economics, Law, Social Schiences and International Affairs \par}
-        \vspace{2cm}
+    \vspace{2.0cm}
     {\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
-		\vspace{1.5cm}        
-        {\large\today\par}
-        \vspace{1.5cm}
+	\vspace{2.0cm}
     {\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
-        \vspace{1.5cm}
+    \vspace{2.0cm}
     {\itshape\large Alen Stepic - XX-XXX-XXX \\Chi Xu - XX-XXX-XXX \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - XX-XXX-XX \par}
-
-        \begin{spacing}{1.5}
-        \vspace{1cm}
+    	\begin{spacing}{1}
+    	\vspace{1.2cm}
     	{Fall Term 2017 \par}
-        \vspace{1cm}
-        Supervisor\\
+    	\vspace{1.2cm}
+    	Supervisor:\\
     	{Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par} 
     	\end{spacing}
+	\vfill
+	{\large \today\par}
     \end{titlepage}
@@
     	\begin{spacing}{1.5}
-
     	(Insert text)
-
     	\end{spacing}
-
     \end{abstract}
@@
 \tableofcontents
-
-    \clearpage
-
-    \listoffigures
-
 \clearpage
@@
 	\cleardoublepage\pagenumbering{arabic}
-\section{Section 1}
+		\section{Research Question}
+		\clearpage
+		\section{Brief Background and Data Collection}
+		\clearpage
+		\section{Econometric Modelling and Results}
+		\clearpage
+		\section{Conclusion}
+	\end{spacing}
 
-\subsection{Subsection 1}
-
-\end{spacing}
 \clearpage
-
 \printbibliography

### 2017-12-26 CollectTwitterData.py
Deleate CollectTwitterData
I deleate the file, as we work with CollectTwitterData_CreatedAtText

@@ -1,76 +1,0 @@
-# Script: CollectTwitterData.py
-# Authors: Alen
-
-""" This script gets tweets for a defined period that contain a certain word.
-    The output is a csv-file with the tweets.
- To use twitter APIs you have to open a twitteraccount on twitter application
-for the api credentials. A good tutorial can be found under
-https://pythonprogramming.net/twitter-api-streaming-tweets-python-tutorial/
-"""
-
-import tweepy
-from tweepy import Stream
-from tweepy import OAuthHandler
-from tweepy.streaming import StreamListener
-import time
-import argparse
-import string
-import config
-import json
-import csv
-
-#consumer key, consumer secret, access token, access secret.
-ckey="ANR2xCLJwM24NirkkFLlurkJY"
-csecret="KFAiqNSVErT7QzAlBYSkUmhGaCoEJJLnfmnG0x7SJJbDT2Qe1k"
-atoken="933214447291604992-xWBg0xEPzsWvrXSVTe5mWEr5o4SVH2n"
-asecret="DRJUfwWxk8MqKUZILnq8zu0pcsKahtTWZCKB64C822VQv"
-
-
-class listener(StreamListener):
-    def on_data(self, data):
-        # Twitter returns data in JSON format - we need to decode it first
-        decodedTweet = json.loads(data)
-   
-        # prints data for one tweet
-        print("===========")
-        #print(decodedTweet)
-
-        # defines where the data is saved. Opening the file 'a' stands for appending
-        saveFile = open('data/twitterData.csv', 'a')
-
-        # gets relevant data from data object
-        created_at = decodedTweet['created_at']
-        text = decodedTweet['text'].encode('utf-8')
-        user_id = decodedTweet['user']['id']
-         # tweet_id = decodedTweet['id']
-         # tweet_id_str = decodedTweet['id_str'].encode('utf-8')
-         # in_reply_to_status_id = decodedTweet['in_reply_to_status_id']
-         # in_reply_to_user_id = ['in_reply_to_user_id']
-        # user =['id', 'id_str', 'name', 'location', 'verified', 'followers_count', 'friends_count', 'listed_count','favourites_count', 'statuses_count','lang']
-        # reply_Tweet_count = ['reply_count']
-         # favorite_count = ['favorite_count']
-         # language = ['lang'].encode('utf-8')
-        #coordinatesTweet = ['coordinates']
-        #place = ['place']
-
-        # Create a row that contains all relevant twitter data
[…]

### 2017-12-26 documentation/documentation.tex
added documentation/documentation.tex
delete redundant latex files

--- 2017-12-22 paper/paper.tex
@@
 \setlength{\parskip}{1em}
+
+%% package for formatting and highlighting source code
+\usepackage{listings}
+\usepackage{color}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Python,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
 
@@
         {\huge\bfseries Name of Project  \par}
+        {\Large\itshape Documentation\par}
         \vspace{3cm}
@@
 \cleardoublepage\pagenumbering{arabic}
-\section{Section 1}
+\section{Introduction}
 
 \subsection{Subsection 1}
+\clearpage
+\section{Data Collection}
+Here, we provide a detailed description of how the data for the sequential analysis is gathered.
+\subsection{Tweets Data}
+\subsubsection{Python Script}
+(Alan's Part)
+\subsubsection{Hardware Setup}
+(Severin's Part)
 
-\cend{spacing}
+\subsection{Bitcoin Price Data}
+We wrote a Python script which collects Bitcoin price data as there was no preexisting data collection that satisfied our needs.
+The Bitcoin price is best expressed by the Bitcoin Price Index.
+The Bitcoin price index (BPI) is an index of the exchange rate between the Bitcoin (BTC) and the US dollar (USD) (\cite{kristoufek2015main}).
+The objective of the script was to gather hourly Bitcoin Price Index Data for the time period in which we gather the Tweets data.
+\subsubsection{Execution}
+By executing the python script \verb|CollectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
+\begin{lstlisting}[language=bash]
+    $ python CollectCryptocurrencyData.py
+\end{lstlisting}
+
+\subsubsection{Output}
+After successfully running the python script \verb|CollectCryptocurrencyData.py| the file \verb|bpi.csv| is generated in the folder \verb|/data|.
+It is important to note that every execution of the script overwrites any existing \verb|bpi.csv| file.
+
+The file \verb|bpi.csv| contains historical Bitcoin Price Index data for one month on an hourly basis. Each data point consists of the following parameters:
+\begin{itemize}
+    \item time: Time
+    \item average: Average price (in USD)
+    \item high: Highest price (in USD)
+    \item low: Lowest price (in USD)
+    \item open: Opening price (in USD)
+\end{itemize}
+
+\subsubsection{API: Bitcoinaverage.com}
+Bitcoinaverage.com offers a free API that provides historical Bitcoin Price Index data. The following requests delivers data for an per hour monthly sliding window.
+\begin{lstlisting}[language=bash]
+https://apiv2.bitcoinaverage.com/indices/global/history/BTCUSD?period=monthly&?format=json
+\end{lstlisting}
+
+\section{Data Aggregation}
+(Joel's Part)
+\section{Data Analysis}
+(Dimitri's Part)
+
+\end{spacing}
 \clearpage

### 2017-12-26 documentation/documentation.tex
adding to titlepage (logo, structure, studentid's), to introduction (text proposal draft), twitter data (draft text)

@@
     \begin{titlepage}
+      	\begin{figure}
       	\centering
-        {\scshape\LARGE University of St.Gallen \par}
-        \vspace{1cm}
-        {\scshape\Large Software Engineering for Economists \par}
+        \includegraphics[scale=0.35]{logohsg}
+        \end{figure}
+        \centering
+        School of Management, Economics, Law, Social Schiences and International Affairs \par
+        \vspace{2.5cm}
+        {\huge\bfseries The effect of Twitter activity on
+Bitcoin price\par}      
+        {\Huge\itshape Documentation\par}
+        \vspace{1.5cm}     
+        {Software Engineering for Economists \\ (7,610,1.00) \par}
         \vspace{1.3cm}
-        {\huge\bfseries Name of Project  \par}
-        {\Large\itshape Documentation\par}
-        \vspace{3cm}
-        {\Large\itshape Joël Sonderegger\par}
-        \begin{spacing}{1.2}
-        joel.sonderegger{@}student.unisg.ch\linebreak
-        11-495-488\linebreak
-
+        {Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\
+       	Alen Stepic - 11-475-258 \\Chi Xu - XX-XXX-XXX \par}
         \vspace{1cm}
@@
         Department of Economics
-        \end{spacing}
-
-        \vfill
 
     % Bottom of the page
-     {\large \today\par}
+     {\centering \today\par}
 
     \end{titlepage}
+
     \begin{abstract}
@@
 \section{Introduction}
+In academics accountability and reproducibility is important.
+However, the publishing process of papers and journals seem to be outdated, as many new ways of data collection and processing exist.
+Examples of academic papers, which are often cited exist where the initial computation are not reproducible and contain errors.
+Even though just replicating data or existing results do not provide any new knowledge at all, it gives a good indication about the quality of the work done and hence increases trustworthiness.
+This explains why reproduction is of great relevance and point out the existing problems.
 
-\subsection{Subsection 1}
+\subsection{Goal of the paper}
+The goal of this documentation paper is to provide a description how the data discussed in the separate paper have been gathered, stored, aggregated and analysed.
+By reading the documentation the reader should be able to reproduce the results.
+
+\subsection{Methodology}
+This documentation consists out of four chapters.
+The first chapters contains a short introduction and provides the reader with an overview about the topic.
+Furthermore it points out the relevance of documentation.
+The second chapter contains an description how the twitter tweets were collected and stored.
+The third chapter discusses how the bitcoin data is gathered.
+Finally the fifth chapter discusses how the analysis has been conducted.
+
+\subsection{Scope}
+The scope of the documentation is provide an overview about the different steps which have been conducted to obtain the results in the paper.
+It does not contain any discussions about the results of the separate academic paper.
+It is not a deep description of the code as the code itself was documented separately.
+Nevertheless, important lines of code are discussed.
 \clearpage
+
 \section{Data Collection}
-Here, we provide a detailed description of how the data for the sequential analysis is gathered.
+Here, we provide a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
 \subsection{Tweets Data}
+To collect the needed twitter data a python script has been written and the real-time twitter data were streamed and stored by the usage of a raspberry pi.
 \subsubsection{Python Script}
-(Alan's Part)
+Twitter offers different Application Programming Interfaces (API) for collecting data.
+Based on twitter, the four most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API.
+However, the timeframe for gathering data for free is limited to 7 day's.
+....
+....
+
 \subsubsection{Hardware Setup}

### 2017-12-26 CollectCryptocurrencyData.py
add functionality for first difference and log first difference (nr of tweets, btc close price)

@@ -36,6 +36,7 @@ def getHourlyBPI():
     result = requests.get(url=url, headers=headers)
 
     bpi_data = result.json()
+    print(bpi_data)
 
     return bpi_data
 

### 2017-12-26 aggregate_twitter_bpi.py

@@ -13,6 +13,9 @@ import io
 from datetime import datetime
 from dateutil.parser import parse
 
+# required for logarithmic function
+import math
+
 # Gets tweets from CSV-File. Returns a data frame with tweets
 def load_tweets():
     df = pd.read_csv('data/20171223_0056_twitterData.csv')
@@ -21,6 +24,11 @@ def load_tweets():
 # Gets bpi data from CSV-File. Returns a data frame with bpi data
 def load_bpi():
     bpi_data = pd.read_csv('data/bpi.csv')
+
+    # drop not needed columns
+    bpi_data.drop('average', axis=1, inplace=True)
+    bpi_data.drop('high', axis=1, inplace=True)
+    bpi_data.drop('low', axis=1, inplace=True)
 
     # create new column 'close'. The close price is the open price of the previous hour
     bpi_data['close'] = bpi_data['open']
@@ -36,9 +44,63 @@ def load_bpi():
     bpi_data.index = bpi_data.index.set_names('M', level=1)
     bpi_data.index = bpi_data.index.set_names('D', level=2)
     bpi_data.index = bpi_data.index.set_names('H', level=3)
-  
+
 
     return bpi_data
+
+# Enriches BPI data frame with first difference and log first difference
+def first_difference_bpi(bpi_df):
+
+    # assigning the variable here to check later if there is a 'previous' btc close price.
+    prev_btc_close = None
+
+    for index, row in bpi_df.iterrows():
+        
+        # get btc closing price for index
+        this_btc_close = bpi_df.get_value(index, 'close', takeable=False)
+
+        # prev_tw = DataFrame.get_value(index, 'close', takeable=False)
+        if prev_btc_close is not None:
+
+            # calculate the first difference for the btc closing price
+            first_difference_btc_close = this_btc_close - prev_btc_close
+            bpi_df.set_value(index, 'df_btc_close', first_difference_btc_close, takeable=False)
+
+            # calculate the log first difference for the btc closing price
+            log_first_difference_btc_close = math.log(this_btc_close) - math.log(prev_btc_close)
+            bpi_df.set_value(index, 'log_df_btc_close', log_first_difference_btc_close, takeable=False)
+
+        # set prev_tw for nex iteration
+        prev_btc_close = this_btc_close
+
+    return bpi_df
+
+# Enriches tweets_per_hour data frame with first difference and log first difference
+def first_difference_tweets(tweets_per_hour):
+
[…]

### 2017-12-26 documentation/documentation.tex
add functionality for first difference and log first difference (nr of tweets, btc close price)
adding @online bibliography and text about tweepy

@@
 \subsection{Tweets Data}
-To collect the needed twitter data a python script has been written and the real-time twitter data were streamed and stored by the usage of a raspberry pi.
+To collect the needed twitter data a python script has been written. Whit the python script real-time twitter data are streamed and stored by the usage of a raspberry pi.
 \subsubsection{Python Script}
 Twitter offers different Application Programming Interfaces (API) for collecting data.
-Based on twitter, the four most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API.
-However, the timeframe for gathering data for free is limited to 7 day's.
+Based on twitter, the biggest an probably most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API.
+(How to add a reference???) However, the timeframe for gathering data for free is limited to 7 day's.
+As python offers different libaries tweepy a open-source libary is been used for streaming the data.
+By using tweepy twitter can be reached in two way's (??) or by the streaming API.
+The latter has been used in contex of the assignment.
+
+Stream - push then pull, easier
+- authentic
+\subsubsubsection{Twitter Authentification}
+- printscreens and how to proceed
+- pip install??
+
+\subsubsubsection{Twitter Streaming API}
 ....

### 2017-12-27 aggregate_twitter_bpi.py
changed filenames

@@ -1,4 +1,4 @@
-# Script: CollectCrypocurrencyData.py
+# Script: collectCrypocurrencyData.py
 # Authors: Joel Sonderegger
 
 """ This script calculates the correlation between tweets containing 'bearish' or 'bullish' and the bitcoin price
@@ -44,7 +44,6 @@ def load_bpi():
     bpi_data.index = bpi_data.index.set_names('M', level=1)
     bpi_data.index = bpi_data.index.set_names('D', level=2)
     bpi_data.index = bpi_data.index.set_names('H', level=3)
-
 
     return bpi_data
 
@@ -165,20 +164,21 @@ def main():
 
     # enrich BPI data frame with first difference and log first difference
     bpi_data = first_difference_bpi(bpi_data)
+    print(bpi_data)
 
     # count number of tweets per hour
-    print('Counting the number of tweets. This can take some minutes...')
-    tweets_per_hour = count_tweets_per_hour(tweets)
+    #print('Counting the number of tweets. This can take some minutes...')
+    #tweets_per_hour = count_tweets_per_hour(tweets)
     
     # enrich tweets_per_hour data frame with first difference and log first difference
-    tweets_per_hour = first_difference_tweets(tweets_per_hour)
+    #tweets_per_hour = first_difference_tweets(tweets_per_hour)
 
     # merge number of tweets per hour with bitcoin price index (bpi) data
-    df_merged = tweets_per_hour.join(bpi_data, how='left')
+    #df_merged = tweets_per_hour.join(bpi_data, how='left')
 
-    print(df_merged)
+    #print(df_merged)
     # Write out to csv
-    generate_csv(df_merged)
+    #generate_csv(df_merged)
 
 if __name__ == '__main__':
     main()

### 2017-12-27 aggregate_twitter_bpi.py
changed filenames

@@ -1,187 +1,0 @@
-# Script: collectCrypocurrencyData.py
-# Authors: Joel Sonderegger
-
-""" This script calculates the correlation between tweets containing 'bearish' or 'bullish' and the bitcoin price
-"""
-
-import pandas as pd
-import numpy as np
-import pprint
-import csv
-import io
-
-from datetime import datetime
-from dateutil.parser import parse
-
-# required for logarithmic function
-import math
-
-# Gets tweets from CSV-File. Returns a data frame with tweets
-def load_tweets():
-    df = pd.read_csv('data/20171223_0056_twitterData.csv')
-    return df
-
-# Gets bpi data from CSV-File. Returns a data frame with bpi data
-def load_bpi():
-    bpi_data = pd.read_csv('data/bpi.csv')
-
-    # drop not needed columns
-    bpi_data.drop('average', axis=1, inplace=True)
-    bpi_data.drop('high', axis=1, inplace=True)
-    bpi_data.drop('low', axis=1, inplace=True)
-
-    # create new column 'close'. The close price is the open price of the previous hour
-    bpi_data['close'] = bpi_data['open']
-    bpi_data['close'] = bpi_data['close'].shift(-1)
-    
-    # Set time as DataFrame index.
-    times = bpi_data.set_index(pd.DatetimeIndex(bpi_data['time']))
-    
-    bpi_data = bpi_data.set_index([times.index.year, times.index.month, times.index.day, times.index.hour])
- 
-    # set correct index names for Y, M, D, H
-    bpi_data.index = bpi_data.index.set_names('Y', level=0)
-    bpi_data.index = bpi_data.index.set_names('M', level=1)
-    bpi_data.index = bpi_data.index.set_names('D', level=2)
-    bpi_data.index = bpi_data.index.set_names('H', level=3)
-
-    return bpi_data
-
-# Enriches BPI data frame with first difference and log first difference
-def first_difference_bpi(bpi_df):
-
-    # assigning the variable here to check later if there is a 'previous' btc close price.
-    prev_btc_close = None
-
-    for index, row in bpi_df.iterrows():
-        
-        # get btc closing price for index
-        this_btc_close = bpi_df.get_value(index, 'close', takeable=False)
-
-        # prev_tw = DataFrame.get_value(index, 'close', takeable=False)
-        if prev_btc_close is not None:
-
-            # calculate the first difference for the btc closing price
-            first_difference_btc_close = this_btc_close - prev_btc_close
[…]

### 2017-12-27 twitter_stream_download.py
delete twitter_stream_download.py

@@ -1,96 +1,0 @@
-# To run this code, first edit config.py with your configuration, then:
-#
-# mkdir data
-# python twitter_stream_download.py -q apple -d data
-# 
-# It will produce the list of tweets for the query "apple" 
-# in the file data/stream_apple.json
-
-import tweepy
-from tweepy import Stream
-from tweepy import OAuthHandler
-from tweepy.streaming import StreamListener
-import time
-import argparse
-import string
-import config
-import json
-
-def get_parser():
-    """Get parser for command line arguments."""
-    parser = argparse.ArgumentParser(description="Twitter Downloader")
-    parser.add_argument("-q",
-                        "--query",
-                        dest="query",
-                        help="Query/Filter",
-                        default='-')
-    parser.add_argument("-d",
-                        "--data-dir",
-                        dest="data_dir",
-                        help="Output/Data Directory")
-    return parser
-
-
-class MyListener(StreamListener):
-    """Custom StreamListener for streaming data."""
-
-    def __init__(self, data_dir, query):
-        query_fname = format_filename(query)
-        self.outfile = "%s/stream_%s.json" % (data_dir, query_fname)
-
-    def on_data(self, data):
-        try:
-            with open(self.outfile, 'a') as f:
-                f.write(data)
-                print(data)
-                return True
-        except BaseException as e:
-            print("Error on_data: %s" % str(e))
-            time.sleep(5)
-        return True
-
-    def on_error(self, status):
-        print(status)
-        return True
-
-
-def format_filename(fname):
-    """Convert file name into a safe string.
-
-    Arguments:
-        fname -- the file name to convert
-    Return:
-        String -- converted file name
-    """
-    return ''.join(convert_valid(one_char) for one_char in fname)
-
-
-def convert_valid(one_char):
-    """Convert a character into '_' if invalid.
-
-    Arguments:
-        one_char -- the char to convert
-    Return:
-        Character -- converted char
-    """
-    valid_chars = "-_.%s%s" % (string.ascii_letters, string.digits)
-    if one_char in valid_chars:
-        return one_char
-    else:
-        return '_'
-
-@classmethod
-def parse(cls, api, raw):
-    status = cls.first_parse(api, raw)
-    setattr(status, 'json', json.dumps(raw))
-    return status
-
-if __name__ == '__main__':
-    parser = get_parser()
-    args = parser.parse_args()
[…]

### 2017-12-27 documentation/documentation.tex
changed subsubsubsections in to paragraphs
different changes in the introduction (text rewriting)

@@
 \section{Introduction}
-In academics accountability and reproducibility is important.
-However, the publishing process of papers and journals seem to be outdated, as many new ways of data collection and processing exist.
-Examples of academic papers, which are often cited exist where the initial computation are not reproducible and contain errors.
-Even though just replicating data or existing results do not provide any new knowledge at all, it gives a good indication about the quality of the work done and hence increases trustworthiness.
-This explains why reproduction is of great relevance and point out the existing problems.
+In the academic environment accountability and reproducibility is important.
+However, the publishing process of papers and journals seem to be outdated.
+New ways of data collection and data processing exist by using computational economics.
+The usage of algorithms can increase effectiveness and efficiency.
+Hence, much lager data sets can be proceeded.
+However this creates also new problems regarding to traceability and reproducibility.
+Academic paper, which were often cited exist, where the initial computation is not reproducible.
+Furthermore, some academic paper even contain errors.
+Replicating data or existing results do not provide any new knowledge at all.
+Nevertheless, the ability to reproduce increases trustworthiness and indicate the quality of the conducted work.
+This explains why reproduction is of great relevance.
 
 \subsection{Goal of the paper}
-The goal of this documentation paper is to provide a description how the data discussed in the separate paper have been gathered, stored, aggregated and analysed.
-By reading the documentation the reader should be able to reproduce the results.
+The goal of this documentation is the provision of a description.
+This description should enable the reader to reproduce the results discussed in the separate paper.
+Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed.
+In other words, the input data, the model core, the model parameters and the applied math program are explained.
 
@@
 This documentation consists out of four chapters.
-The first chapters contains a short introduction and provides the reader with an overview about the topic.
+The first chapter contains a short introduction and provides the reader with an overview about the topic.
 Furthermore it points out the relevance of documentation.
-The second chapter contains an description how the twitter tweets were collected and stored.
-The third chapter discusses how the bitcoin data is gathered.
+The second chapter discusses the input data.
+This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data.
+The third chapter discusses how the data is aggregated by pointing out the core model and its parameters.
 Finally the fifth chapter discusses how the analysis has been conducted.
@@
 \subsection{Scope}
-The scope of the documentation is provide an overview about the different steps which have been conducted to obtain the results in the paper.
-It does not contain any discussions about the results of the separate academic paper.
-It is not a deep description of the code as the code itself was documented separately.
+The scope of the documentation is the provision of an overview about the different steps which have been conducted to obtain the results in the paper.
+It does not contain any discussions about the results of the separate paper.
+It is not a deep description of the code as the code itself as the code is documented separately.
 Nevertheless, important lines of code are discussed.
@@
 Twitter offers different Application Programming Interfaces (API) for collecting data.
-Based on twitter, the biggest an probably most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API.
+Based on twitter, the biggest and probably most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API.
 (How to add a reference???) However, the timeframe for gathering data for free is limited to 7 day's.
-As python offers different libaries tweepy a open-source libary is been used for streaming the data.
+As python offers different libraries tweepy a open-source library is been used for streaming the data.
 By using tweepy twitter can be reached in two way's (??) or by the streaming API.
-The latter has been used in contex of the assignment.
+The latter has been used in context of the assignment.
 
@@
 \begin{itemize}
-    \item time: Time
+    \item time: Timestamp on an hourly basis
     \item average: Average price (in USD)
@@
 
+The time timestamps is UTC time.
+
 \section{Data Aggregation}

### 2017-12-27 documentation/documentation.tex
extended the btc api description part

--- 2017-12-26 documentation/documentation.tex
@@
 - authentic
-\subsubsubsection{Twitter Authentification}
+\paragraph{Twitter Authentification}
 - printscreens and how to proceed
@@
 
-\subsubsubsection{Twitter Streaming API}
+\paragraph{Twitter Streaming API}
 ....
@@
 The Bitcoin price index (BPI) is an index of the exchange rate between the Bitcoin (BTC) and the US dollar (USD) (\cite{kristoufek2015main}).
-The objective of the script was to gather hourly Bitcoin Price Index Data for the time period in which we gather the Tweets data.
+The objective of the script was to gather hourly Bitcoin Price Index data for at least the time period in which we gather the tweets data.
+We found the an API by bitcoinaverage.com which sufficed our needs.
+An API description follows later.
 \subsubsection{Execution}

### 2017-12-27 documentation/documentation.tex
extend the API: Bitcoinaverage.com description part

@@
 \subsubsection{Execution}
-By executing the python script \verb|CollectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
+By executing the python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
 \begin{lstlisting}[language=bash]
-    $ python CollectCryptocurrencyData.py
+    $ python collectCryptocurrencyData.py
 \end{lstlisting}
@@
 \subsubsection{API: Bitcoinaverage.com}
-Bitcoinaverage.com offers a free API that provides historical Bitcoin Price Index data. The following requests delivers data for an per hour monthly sliding window.
+Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin.
+The following requests delivers data for an per hour monthly sliding window.
+\paragraph{Request}\mbox{}\\
+The request to get the data for an per hour monthly sliding window looks as follows.
+This request require authentication that requires registration and the generation of an API key.
+The registration and generation of an API key is freely available on bitcoinaverage.com.
+The collectCryptocurrencyData.py already contains the necessary keys.
+This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.
 \begin{lstlisting}[language=bash]
@@
 \end{lstlisting}
+\paragraph{Response}
 

### 2017-12-27 documentation/documentation.tex
add collectTwitterData.py

@@
 \paragraph{Response}
+An excerpt of an example response looks like the following:
+\begin{lstlisting}
+[
+    {
+        "high": 8271.04, 
+        "average": 8247.83, 
+        "open": 8242.39,
+        "low": 8217.72, 
+        "time": '2017-11-22 15:00:00'
+    }, 
+    {
+        "high': 8246.82,
+        "average": 8203.19,
+        'open': 8203.81,
+        'low': 8157.25,
+        'time': '2017-11-22 14:00:00'
+    }, 
+    {
+        'high': 8267.27, 
+        "average": 8238.62, 
+        'open': 8248.77, 
+        'low': 8198.54, 
+        'time': '2017-11-22 13:00:00'
+    }
+]
+\end{lstlisting}
 

### 2017-12-27 CollectCryptocurrencyData.py

@@ -36,7 +36,7 @@ def getHourlyBPI():
     result = requests.get(url=url, headers=headers)
 
     bpi_data = result.json()
-
+    print(bpi_data)
     return bpi_data
 
 # not used so far

### 2017-12-27 collectTwitterData.py

@@ -1,0 +1,171 @@
+# Script: CollectTwitterData.py
+# Authors: Alen
+
+""" This script gets tweets for a defined period that contain the word bitcoin.
+    The output is a csv-file with the tweets.
+ To use twitter APIs you have to open a twitteraccount on twitter application
+for the api credentials. A good tutorial can be found under
+https://pythonprogramming.net/twitter-api-streaming-tweets-python-tutorial/
+"""
+
+import tweepy
+from tweepy import Stream
+from tweepy import OAuthHandler
+from tweepy.streaming import StreamListener
+import time
+import argparse
+import string
+import config
+import json
+import csv
+import pprint
+from pathlib import Path
+
+# Import smtplib for the email sending function
+import smtplib
+
+
+
+#consumer key, consumer secret, access token, access secret.
+ckey="ANR2xCLJwM24NirkkFLlurkJY"
+csecret="KFAiqNSVErT7QzAlBYSkUmhGaCoEJJLnfmnG0x7SJJbDT2Qe1k"
+atoken="933214447291604992-xWBg0xEPzsWvrXSVTe5mWEr5o4SVH2n"
+asecret="DRJUfwWxk8MqKUZILnq8zu0pcsKahtTWZCKB64C822VQv"
+
+# function to send email with error
+def send_email(sbjt, msg):
+    fromaddr = 'twitterbitcoinanalysis@gmail.com'
+    toaddrs = 'joel.sonderegger@googlemail.com'
+    bodytext = 'From: %s\nTo: %s\nSubject: %s\n\n%s' %(fromaddr, toaddrs, sbjt, msg)
+   
+    # Credentials (if needed)
+    username = 'twitterbitcoinanalysis@gmail.com'
+    password = 'wNvfuXAiek9i' 
+  
+    # The actual mail sent
+    server = smtplib.SMTP('smtp.gmail.com:587')
+    server.starttls()
+    server.login(username,password)
+    server.sendmail(fromaddr, toaddrs, bodytext)
+    server.quit()
+
+
+class listener(StreamListener):
+    def on_data(self, data):
+        # Twitter returns data in JSON format - we need to decode it first
+        decoded_tweet = json.loads(data)
+        
+        # Exception handling for KeyError. LookupError is the base class for the exceptions that are raised when a key or index used on a mapping or sequence is invalid: IndexError, KeyError
+        try:
+            # prints data for one tweet
+            print("===========")
+
+            # check if text has key created_at (there where tweets without crashing the program)
[…]

### 2017-12-27 documentation/documentation.tex
added 	aggregateTwitterBpi.py

--- 2017-12-27 documentation/documentation.tex
@@
 \usepackage{color}
+
+%% Useful packages
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage[colorlinks=true, allcolors=black]{hyperref}
+\usepackage{graphicx}
+\usepackage{setspace}
+
+% Abkuerzungsverzeichnis
+\usepackage{acronym}
+
+% Specify bibliography package
+\usepackage{csquotes}% Recommended
+\usepackage[style=apa]{biblatex}
+%\DeclareLanguageMapping{american}{american-apa}
+\addbibresource{references.bib}
+
+% Section Title Margins
+\usepackage{titlesec}
+\titlespacing*{\section}
+{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
+\titlespacing*{\subsection}
+{0pt}{1.4ex}{0pt}
 
@@
 }
-
-%% Useful packages
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage[colorlinks=true, allcolors=black]{hyperref}
-\usepackage{csquotes}
-\usepackage{graphicx}
-\usepackage{setspace}
-
-% Abkuerzungsverzeichnis
-\usepackage{acronym}
-
-% Specify bibliography package
-\usepackage{csquotes}% Recommended
-\usepackage[style=apa,backend=biber]{biblatex}
-\DeclareLanguageMapping{american}{american-apa}
-\addbibresource{references.bib}
-
-% Section Title Margins
-\usepackage{titlesec}
-\titlespacing*{\section}
-{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
-\titlespacing*{\subsection}
-{0pt}{1.4ex}{0pt}
 
@@
 In academics accountability and reproducibility is important.
-However, the publishing process of papers and journals seem to be outdated, as many new ways of data collection and processing exist.
+However, the publishing process of papers and journals seem to be outdated, as many new ways of data set and processing exist.
 Examples of academic papers, which are often cited exist where the initial computation are not reproducible and contain errors.
@@
 \subsection{Bitcoin Price Data}
-We wrote a Python script which collects Bitcoin price data as there was no preexisting data collection that satisfied our needs.
+We wrote a Python script which collects Bitcoin price data as there was no preexisting data set that satisfied our needs.
 The Bitcoin price is best expressed by the Bitcoin Price Index.
@@
 \subsubsection{Execution}
+\cite{Twitter}
 By executing the python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
@@
 \begin{itemize}
-    \item time: Timestamp on an hourly basis
+    \item time: Timestamp on an hourly basis in UTC time
     \item average: Average price (in USD)
@@
 \paragraph{Response}
-
-The time timestamps is UTC time.
+An excerpt of an example response looks like the following:
+\begin{lstlisting}
+[
+    {
+        "high": 8271.04, 
+        "average": 8247.83, 
+        "open": 8242.39,
+        "low": 8217.72, 
+        "time": "2017-11-22 15:00:00"
+    }, 
+    {
+        "high": 8246.82,
+        "average": 8203.19,
+        "open": 8203.81,
+        "low": 8157.25,
+        "time": "2017-11-22 14:00:00"
+    }, 
+    {
+        "high": 8267.27, 
+        "average": 8238.62, 
+        "open": 8248.77, 
+        "low": 8198.54, 
+        "time": "2017-11-22 13:00:00"
+    }
+]
+\end{lstlisting}
 
 \section{Data Aggregation}
-(Joel's Part)
+After the two data sets (tweets and Bitcoin Price Index) are gathered
+
 \section{Data Analysis}
@@
 
+%************************** Bibliography **************************
 \printbibliography
+\clearpage
 
+%************************** DOCUMENT-END **************************
 \end{document}

### 2017-12-27 aggregateTwitterBpi.py

@@ -1,0 +1,187 @@
+# Script: collectCrypocurrencyData.py
+# Authors: Joel Sonderegger
+
+""" This script calculates the correlation between tweets containing 'bearish' or 'bullish' and the bitcoin price
+"""
+
+import pandas as pd
+import numpy as np
+import pprint
+import csv
+import io
+
+from datetime import datetime
+from dateutil.parser import parse
+
+# required for logarithmic function
+import math
+
+# Gets tweets from CSV-File. Returns a data frame with tweets
+def load_tweets():
+    df = pd.read_csv('data/20171223_0056_twitterData.csv')
+    return df
+
+# Gets bpi data from CSV-File. Returns a data frame with bpi data
+def load_bpi():
+    bpi_data = pd.read_csv('data/bpi.csv')
+
+    # drop not needed columns
+    bpi_data.drop('average', axis=1, inplace=True)
+    bpi_data.drop('high', axis=1, inplace=True)
+    bpi_data.drop('low', axis=1, inplace=True)
+
+    # create new column 'close'. The close price is the open price of the previous hour
+    bpi_data['close'] = bpi_data['open']
+    bpi_data['close'] = bpi_data['close'].shift(-1)
+    
+    # Set time as DataFrame index.
+    times = bpi_data.set_index(pd.DatetimeIndex(bpi_data['time']))
+    
+    bpi_data = bpi_data.set_index([times.index.year, times.index.month, times.index.day, times.index.hour])
+ 
+    # set correct index names for Y, M, D, H
+    bpi_data.index = bpi_data.index.set_names('Y', level=0)
+    bpi_data.index = bpi_data.index.set_names('M', level=1)
+    bpi_data.index = bpi_data.index.set_names('D', level=2)
+    bpi_data.index = bpi_data.index.set_names('H', level=3)
+
+    return bpi_data
+
+# Enriches BPI data frame with first difference and log first difference
+def first_difference_bpi(bpi_df):
+
+    # assigning the variable here to check later if there is a 'previous' btc close price.
+    prev_btc_close = None
+
+    for index, row in bpi_df.iterrows():
+        
+        # get btc closing price for index
+        this_btc_close = bpi_df.get_value(index, 'close', takeable=False)
+
+        # prev_tw = DataFrame.get_value(index, 'close', takeable=False)
+        if prev_btc_close is not None:
+
+            # calculate the first difference for the btc closing price
+            first_difference_btc_close = this_btc_close - prev_btc_close
[…]

### 2017-12-27 documentation/documentation.tex

--- 2017-12-27 documentation/documentation.tex
@@
 
-% Abkuerzungsverzeichnis
+% List of abbreviations
 \usepackage{acronym}
@@
     \listoffigures 	
-
+    \section*{List of Abbreviation} 
+	\begin{acronym}[ASECRETTT] 
+	\acro{API}{Application Programming Interface}
+	\acro{CKEY}{Consumer Key}
+	\acro{CSECRET}{Consumer Secret}
+	\acro{ATOKEN}{Access Token}
+	\acro{ASECRET}{Access Token Secret}
+	\end{acronym}
     \clearpage
@@
 \section{Introduction}
-In academics accountability and reproducibility is important.
-However, the publishing process of papers and journals seem to be outdated, as many new ways of data collection and processing exist.
-Examples of academic papers, which are often cited exist where the initial computation are not reproducible and contain errors.
-Even though just replicating data or existing results do not provide any new knowledge at all, it gives a good indication about the quality of the work done and hence increases trustworthiness.
-This explains why reproduction is of great relevance and point out the existing problems.
+In the academic environment accountability and reproducibility is important.
+However, the publishing process of papers and journals seem to be outdated.
+New ways of data collection and data processing exist by using computational economics.
+The usage of algorithms can increase effectiveness and efficiency.
+Hence, much lager data sets can be proceeded.
+However this creates also new problems regarding to traceability and reproducibility.
+Often cited academic paper exist, where the initial computation is not reproducible.
+Furthermore, some academic paper even contain computational errors.
+Replicating data or existing results do not provide any new knowledge at all.
+Nevertheless, the ability to reproduce increases trustworthiness and indicate the quality of the conducted work.
+This explains why reproduction is of great relevance.
 
 \subsection{Goal of the paper}
-The goal of this documentation paper is to provide a description how the data discussed in the separate paper have been gathered, stored, aggregated and analysed.
-By reading the documentation the reader should be able to reproduce the results.
+The goal of this documentation is the provision of a description.
+This description should enable the reader to reproduce the results discussed in the separate paper.
+Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed.
+In other words, the input data, the model core, the model parameters and the applied math program are explained.
 
@@
 \subsection{Tweets Data}
-To collect the needed twitter data a python script has been written. Whit the python script real-time twitter data are streamed and stored by the usage of a raspberry pi.
+Whit the python script real-time twitter data are streamed and stored. This happens with help of a raspberry pi.
 \subsubsection{Python Script}
 Twitter offers different Application Programming Interfaces (API) for collecting data.
-Based on twitter, the biggest an probably most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API.
-(How to add a reference???) However, the timeframe for gathering data for free is limited to 7 day's.
-As python offers different libaries tweepy a open-source libary is been used for streaming the data.
-By using tweepy twitter can be reached in two way's (??) or by the streaming API.
-The latter has been used in contex of the assignment.
+However, the time frame for gathering data on a free base is limited to 7 days.
+On the other hand, python offers different twitter libraries.
+Such as the open-source package tweepy.
+This package has been used for streaming the twitter data as it simplify the script.
 
-Stream - push then pull, easier
-- authentic
-\paragraph{Twitter Authentification}
-- printscreens and how to proceed
-- pip install??
+\paragraph{Installing Tweepy}\mbox{}\\{}
+Tweepy can be installed very simple by running following commands in the command prompt. 
+\begin{lstlisting}[language=bash]
+pip install tweepy
+\end{lstlisting}
 
-\paragraph{Twitter Streaming API}
-....
-....
+If the previous downloaded python installation package does not contain the tweepy library, the tweepy library has to be downloaded. The package can be downloaded for free from the following link:
+\begin{lstlisting}[language=bash]
+https://pypi.python.org/pypi/tweepy
+\end{lstlisting}
+
+\paragraph{Twitter Authentication}\mbox{}\\{}
+To access the twitter data, twitter requests an identification of the user.
+The identification is assured by different keys and access tokens.
+Those are the (1) consumer key (ckey), (2) consumer secret (csecret), (3) access token (atoken) and (4) access token secret (asecret).
+
+To get the mentioned key and tokens a twitter account is needed.
+Once, an twitter account exist an application has to be created.
+This has to be conducted by login with the twitter account credentials under the following link:
+\begin{lstlisting}[language=bash]
+https://apps.twitter.com/
+\end{lstlisting}
+
+After the creation of an application the keys and tokens can be extracted. Figure 1 illustrates how to retrieve the keys and tokens.
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.6]{twitteraccess}
+\caption{Twitter Keys and Access Tokens}
+\end{figure}
+
+\paragraph{Twitter Streaming API}\mbox{}\\{}
+By running the python script \verb|collectTwitterData.py| real-time twitter data is pushed in a JSON format. Tweets are pushed just in case the tweet contains the defined key word \verb|bitcoin|.
+\begin{lstlisting}[language=bash]
+$ python collectTwitterData.py
+\end{lstlisting}
+
+From the JSON format the following parameters are decoded
+\begin{itemize}
+    \item created at: Timestamp of the created tweet
+    \item text: text of the tweet
+\end{itemize}
+The time timestamps is UTC time.
 
@@
 \subsubsection{Execution}
-By executing the python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
+By executing the python script \verb|CollectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
 \begin{lstlisting}[language=bash]
-    $ python collectCryptocurrencyData.py
+    $ python CollectCryptocurrencyData.py
 \end{lstlisting}
@@
 \subsubsection{API: Bitcoinaverage.com}
-Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin.
-The following requests delivers data for an per hour monthly sliding window.
-\paragraph{Request}\mbox{}\\
-The request to get the data for an per hour monthly sliding window looks as follows.
-This request require authentication that requires registration and the generation of an API key.
-The registration and generation of an API key is freely available on bitcoinaverage.com.
-The collectCryptocurrencyData.py already contains the necessary keys.
-This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.
+Bitcoinaverage.com offers a free API that provides historical Bitcoin Price Index data. The following requests delivers data for an per hour monthly sliding window.
 \begin{lstlisting}[language=bash]
@@
 \end{lstlisting}
-\paragraph{Response}
 

### 2017-12-27 documentation/documentation.tex
deleated the header from introduction created by the previous merge

@@
 \usepackage{color}
+
+%% Useful packages
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage[colorlinks=true, allcolors=black]{hyperref}
+\usepackage{graphicx}
+\usepackage{setspace}
+
+% List of abbreviations
+\usepackage{acronym}
+
+% Specify bibliography package
+\usepackage{csquotes}% Recommended
+\usepackage[style=apa]{biblatex}
+%\DeclareLanguageMapping{american}{american-apa}
+\addbibresource{references.bib}
+
+% Section Title Margins
+\usepackage{titlesec}
+\titlespacing*{\section}
+{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
+\titlespacing*{\subsection}
+{0pt}{1.4ex}{0pt}
 
@@
 }
-
-%% Useful packages
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage[colorlinks=true, allcolors=black]{hyperref}
-\usepackage{csquotes}
-\usepackage{graphicx}
-\usepackage{setspace}
-
-% List of abbreviations
-\usepackage{acronym}
-
-% Specify bibliography package
-\usepackage{csquotes}% Recommended
-\usepackage[style=apa,backend=biber]{biblatex}
-\DeclareLanguageMapping{american}{american-apa}
-\addbibresource{references.bib}
-
-% Section Title Margins
-\usepackage{titlesec}
-\titlespacing*{\section}
-{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
-\titlespacing*{\subsection}
-{0pt}{1.4ex}{0pt}
 
@@
 \subsubsection{Execution}
-By executing the python script \verb|CollectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
+\cite{Twitter}
+By executing the python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
 \begin{lstlisting}[language=bash]
-    $ python CollectCryptocurrencyData.py
+    $ python collectCryptocurrencyData.py
 \end{lstlisting}
@@
 \end{lstlisting}
-
-The time timestamps is UTC time.
+\paragraph{Response}
+An excerpt of an example response looks like the following:
+\begin{lstlisting}
+[
+    {
+        "high": 8271.04, 
+        "average": 8247.83, 
+        "open": 8242.39,
+        "low": 8217.72, 
+        "time": "2017-11-22 15:00:00"
+    }, 
+    {
+        "high": 8246.82,
+        "average": 8203.19,
+        "open": 8203.81,
+        "low": 8157.25,
+        "time": "2017-11-22 14:00:00"
+    }, 
+    {
+        "high": 8267.27, 
+        "average": 8238.62, 
+        "open": 8248.77, 
+        "low": 8198.54, 
+        "time": "2017-11-22 13:00:00"
+    }
+]
+\end{lstlisting}
 
 \section{Data Aggregation}
-(Joel's Part)
+After the two data sets (tweets and Bitcoin Price Index) are gathered
+
 \section{Data Analysis}

### 2017-12-27 documentation/documentation.tex
start to describe Data Aggregation and Data Wrangling

--- 2017-12-27 documentation/documentation.tex
@@
 \usepackage[american]{babel}
+
+% Specify bibliography package
+\usepackage{csquotes}% Recommended
+\usepackage[style=apa]{biblatex}
+%\DeclareLanguageMapping{american}{american-apa}
+\addbibresource{references.bib}
 
@@
 \usepackage{acronym}
-
-% Specify bibliography package
-\usepackage{csquotes}% Recommended
-\usepackage[style=apa]{biblatex}
-%\DeclareLanguageMapping{american}{american-apa}
-\addbibresource{references.bib}
 
@@
 An API description follows later.
+
 \subsubsection{Execution}
-\cite{Twitter}
 By executing the python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
@@
 
-\section{Data Aggregation}
-After the two data sets (tweets and Bitcoin Price Index) are gathered
+\section{Data Aggregation and Data Wrangling}
+Before the collected data sets can be analyzed they need to be aggregated. In addition, some data wrangling is necessary to bring the data in a format which than can be analyzed.
+
+\subsubsection{Execution}
+By executing the python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
+\begin{lstlisting}[language=bash]
+    $ python aggregateTwitterBpi.py
+\end{lstlisting}
+
+\subsubsection{Output}
+After successfully running the python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
+It is important to note that every execution of the script overwrites any existing \verb|nr_of_tweets_bpi_closing_price.csv| file.
+
+The file \verb|aggregateTwitterBpi.csv| contains historical tweets and Bitcoin Price Index data. Each data point consists of the following parameters:
+\begin{itemize}
+    \item time: Timestamp on an hourly basis in UTC time
+    \item {nr\_of\_tweets}: 
+    \item {df\_nr\_of\_tweets}: 
+    \item {log\_df\_nr\_of\_tweets}: 
+    \item {df\_bpi\_closing\_price}: 
+    \item {log\_df\_bpi\_closing\_price}: 
+\end{itemize}
 

### 2017-12-27 documentation/documentation.tex
created section hardware setup

@@
 \subsubsection{Hardware Setup}
-(Severin's Part)
+As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin".
+The python program was running for seven days without interruption (to be checked!!!!!!!!!!!) on a raspberry pi (rpi) which was accessed with a secure shell (SSH) connection.
+This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime.
+Furthermore due to a low energy consumption of the rpi the method is also the most cost efficient one compared to a personal computer or NAS Server.
+The following section describes the different steps that have been taken in order to setup the rpi, ssh, git and python3.\newline The following steps were conducted by using a Raspberry Pi 2, a micro SD card and Python3.
+
+\paragraph{(1)Setup of the Raspberry Pi}\mbox{}\\
+- Burn image 2017-11-29-raspbian-stretch.zip to micro SD card available from \newline https://www.raspberrypi.org/downloads/raspbian/ \newline
+- Boot image from micro SD card \newline
+- Open SSH session using PuTTY SSH client for Windows available from \newline https://www.chiark.greenend.org.uk/\~sgtatham/putty/latest.html \newline
+- Login to server with credentials \newline
+
+\paragraph{(3) Update system to the newest software}\mbox{}\\
+- Update list of applications with the command: sudo apt-get update \newline
+- Update applications with the command: sudo apt-get upgrade \newline
+
+\paragraph{(4) Setup Git}\mbox{}\\
+- Install git using the command: sudo apt-get install git \newline
+- Clone git repository from https://github.com/joelsonderegger/twitterbitcoin.git \newline
+
+\paragraph{(5) Setup Pyhton3}\mbox{}\\
+- Install Python3 using the command: sudo apt-get install Python3 \newline
+- Install the tweepy module for python using the command: pip install tweepy \newline
+
+\paragraph{(6) Collect Twitter Data}\mbox{}\\
+- Open a new screen using the command: screen -S 'name' \newline
+- start python program using the command: python3 CollectTwitterData.py \newline
+- Detach the screen to keep the program running after secure shell connection has been terminated using the commands: Ctrl+A , Ctrl+D \newline
+- Re-attach the screen to check whether the script is still running using the command: screen -r 'name' \newline
+
+\paragraph{(7) Download the collected data}\mbox{}\\
+- Install FileZilla available https://filezilla-project.org/ \newline
+- Connect to rpi and navigate to data location \newline
+- Download data manually \newline \newline In summary, this approach worked quite well and run smoothly after all bugs have been resolved from the file CollectTwitterData.py A clean setup is crucial to ensure continuous data collection over a longer period.
 

### 2017-12-27 documentation/documentation.tex
adding details to twitter streamp api

--- 2017-12-27 documentation/documentation.tex
@@
 	\acro{ASECRET}{Access Token Secret}
+	\acro{JSON}{Java Script Object Notation}
 	\end{acronym}
@@
 \section{Data Collection}
-Here, we provide a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
+This section contains a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
 \subsection{Tweets Data}
@@
 Twitter offers different Application Programming Interfaces (API) for collecting data.
-However, the time frame for gathering data on a free base is limited to 7 days.
+However, the time frame for gathering data on a freely base is limited to 7 days.
 On the other hand, python offers different twitter libraries.
@@
 \paragraph{Installing Tweepy}\mbox{}\\{}
-Tweepy can be installed very simple by running following commands in the command prompt. 
+Tweepy is installed very simply by running following commands in the command prompt. 
 \begin{lstlisting}[language=bash]
@@
 
-If the previous downloaded python installation package does not contain the tweepy library, the tweepy library has to be downloaded. The package can be downloaded for free from the following link:
+If the previous downloaded python installation package does not contain the tweepy library, the tweepy package has to be downloaded. The package can be downloaded for free from the following link:
 \begin{lstlisting}[language=bash]
@@
 
-To get the mentioned key and tokens a twitter account is needed.
-Once, an twitter account exist an application has to be created.
+To obtain the mentioned keys and tokens a twitter account is needed.
+Once, a twitter account exist a application has to be created.
 This has to be conducted by login with the twitter account credentials under the following link:
@@
 
-After the creation of an application the keys and tokens can be extracted. Figure 1 illustrates how to retrieve the keys and tokens.
+After the creation of a application, the keys and tokens can be extracted. Figure 1 illustrates how to retrieve the keys and tokens.
 \begin{figure}[h]
@@
 \paragraph{Twitter Streaming API}\mbox{}\\{}
-By running the python script \verb|collectTwitterData.py| real-time twitter data is pushed in a JSON format. Tweets are pushed just in case the tweet contains the defined key word \verb|bitcoin|.
+By running the python script \verb|collectTwitterData.py| real-time twitter data is pushed in a Java Script Object Notation (JSON) format.
+Tweets are just pushed in case a tweet contains the defined key word \verb|bitcoin|.
 \begin{lstlisting}[language=bash]
@@
 
-From the JSON format the following parameters are decoded
+From the JSON format the following parameters are decoded:
 \begin{itemize}
@@
 \end{itemize}
-The time timestamps is UTC time.
+The time timestamps are in UTC time.
+
+After a successfully decoding the parameters the data is appended to the \verb|twitterData.csv| file in a new row and saved in the folder \verb|/data|.
+
+An excerpt of an example response looks like the following:
+\begin{lstlisting}
+[
+    {
+        "created_at": Tue Dec 19 20:40:48 +0000 2017, 
+        "text": "RT @WhiteBitcoin: New Bitcoin White. Effective, Flexible, Reliable", 
+    }, 
+    {
+        "created_at": Tue Dec 19 20:40:49 +0000 2017 ,
+        "text": "As #bitcoin prices surge, #xrp remains affordable and FAST!",
+    }, 
+    {
+        "created_at": Tue Dec 19 20:40:49 +0000 2017, 
+        "text": "Singapore issues bitcoin warning after price rise - #BTC #Bitcoin #Crypto", 
+    }
+]
+\end{lstlisting}
+
+Furthermore to ensure a high quality data set an exception has been integrated into the \verb|collectTwitterData.py| script.
+If an error occurs an email will be sent with the error message.
+Furthermore the logfile will be  appended to \verb|/data/tweet_collection_error_log.csv|.
 

### 2017-12-27 documentation/documentation.tex
changes design of hardware section

--- 2017-12-27 documentation/documentation.tex
@@
 \subsubsection{Hardware Setup}
-(Severin's Part)
+As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin".
+The python program was running for seven days without interruption (to be checked!!!!!!!!!!!) on a raspberry pi (rpi) which was accessed with a secure shell (SSH) connection.
+This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime.
+Furthermore due to a low energy consumption of the rpi the method is also the most cost efficient one compared to a personal computer or NAS Server.
+The following section describes the different steps that have been taken in order to setup the rpi, ssh, git and python3.\newline The following steps were conducted by using a Raspberry Pi 2, a micro SD card and Python3 and Windows 10 64Bit.
+
+\begin{enumerate}
+\item Setup of the Raspberry Pi
+\begin{enumerate}
+\item Burn image 2017-11-29-raspbian-stretch.zip to micro SD card available from
+\begin{lstlisting}[language=bash]
+https://www.raspberrypi.org/downloads/raspbian/
+\end{lstlisting}
+\item Boot image from micro SD card 
+\item Open SSH session using PuTTY SSH client for Windows available from
+\begin{lstlisting}[language=bash] 
+https://www.chiark.greenend.org.uk/~sgtatham/putty/latest.html
+\end{lstlisting}
+\item Login to server with credentials 
+\end{enumerate}
+
+\item Update system to the newest software
+\begin{enumerate}
+\item Update list of applications with the command
+\begin{lstlisting}[language=bash]
+sudo apt-get update
+\end{lstlisting}
+\item Update applications with the command
+\begin{lstlisting}[language=bash]
+sudo apt-get upgrade
+\end{lstlisting}
+\end{enumerate}
+
+\item Setup Git
+\begin{enumerate}
+\item Install Git using the command
+\begin{lstlisting}[language=bash]
+ sudo apt-get install git
+\end{lstlisting}
+\item Clone Git repository from
+\begin{lstlisting}[language=bash] 
+https://github.com/joelsonderegger/twitterbitcoin.git
+\end{lstlisting}
+\end{enumerate}
+
+\item Setup Pyhton3
+\begin{enumerate}
+\item Install Python3 using the command: sudo apt-get install Python3 \newline
+\item Install the tweepy module for python using the command
+\begin{lstlisting}[language=bash]
+pip install tweepy
+\end{lstlisting}
+\end{enumerate}
+
+\item Collect Twitter Data
+\begin{enumerate}
+\item Open a new screen using the command
+\begin{lstlisting}[language=bash] 
+screen -S 'name' 
+\end{lstlisting}
+\item Start python program using the command
+\begin{lstlisting}[language=bash]
+python3 CollectTwitterData.py
+\end{lstlisting}
+\item Detach the screen to keep the program running after secure shell connection has been terminated using the commands
+\begin{lstlisting}[language=bash]
+Ctrl+A
+Ctrl+D
+\end{lstlisting}
+\item Re-attach the screen to check whether the script is still running using the command
+\begin{lstlisting}[language=bash]
+screen -r 'name'
+\end{lstlisting}
+\end{enumerate}
+
+\item Download the collected data
+\begin{enumerate}
+\item Install FileZilla available from
+\begin{lstlisting}[language=bash] 
+https://filezilla-project.org/
+\end{lstlisting}
+\item Connect to rpi and navigate to data location \newline
+\item Download data manually \newline \newline \end{enumerate}
+\end{enumerate}
+In summary, this approach worked quite well and run smoothly after all bugs have been resolved from the file CollectTwitterData.py A clean setup is crucial to ensure continuous data collection over a longer period.
 

### 2017-12-27 documentation/documentation.tex
minor spelling mistakes and list of abbreviations

@@
 	\acro{API}{Application Programming Interface}
+	\acro{ATOKEN}{Access Token}
+	\acro{ASECRET}{Access Token Secret}
 	\acro{CKEY}{Consumer Key}
 	\acro{CSECRET}{Consumer Secret}
-	\acro{ATOKEN}{Access Token}
-	\acro{ASECRET}{Access Token Secret}
 	\acro{JSON}{Java Script Object Notation}
+	\acro{RPI}{Raspberry Pi}
+	\acro{SSH}{Secure Shell}
 	\end{acronym}
@@
 As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin".
-The python program was running for seven days without interruption (to be checked!!!!!!!!!!!) on a raspberry pi (rpi) which was accessed with a secure shell (SSH) connection.
+The python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
 This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime.
-Furthermore due to a low energy consumption of the rpi the method is also the most cost efficient one compared to a personal computer or NAS Server.
-The following section describes the different steps that have been taken in order to setup the rpi, ssh, git and python3.\newline The following steps were conducted by using a Raspberry Pi 2, a micro SD card and Python3 and Windows 10 64Bit.
+Furthermore due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server.
+The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline
 
@@
 \end{enumerate}
-In summary, this approach worked quite well and run smoothly after all bugs have been resolved from the file CollectTwitterData.py A clean setup is crucial to ensure continuous data collection over a longer period.
+In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.
 

### 2017-12-27 paper/paper.tex
I tried to make the structure of the paper.tex more clear and easier to understand
Logo on titlepage, StudentIDs on titlepage, first and very raw text in most of the paper.tex sections

@@
 
-%% Language and font encodings
+%************************** Language and font encodings **************************
 \usepackage[utf8]{inputenc}
 
-%% Sets page size and margins
+%************************** Sets page size and margins **************************
 \usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
@@
 
-%% Useful packages
+%************************** Useful packages **************************
 \usepackage{amsmath}
@@
 
-% Abkuerzungsverzeichnis
+%************************** List of abbreviations **************************
 \usepackage{acronym}
 
-% Specify bibliography package
+%************************** Specify bibliography package **************************
 \usepackage{csquotes}
@@
 
-% Section Title Margins
+%************************** Section Title Margins **************************
 \usepackage{titlesec}
@@
 {0pt}{1.4ex}{0pt}
-
 \title{Review of Assigned Readings}
@@
 
+%************************** DOCUMENT-START **************************
 \begin{document}
 
+%************************** Title Page **************************   
     \begin{titlepage}
+      	\begin{figure}
       	\centering
-    {\scshape\LARGE University of St.Gallen \\ \large School of Management, Economics, Law, Social Schiences and International Affairs \par}
+        \includegraphics[scale=0.35]{logohsg}
+        \end{figure}    
+    \centering
+    {\scshape\large School of Management, Economics, Law, Social Schiences and International Affairs \par}
     \vspace{2.0cm}
@@
     \vspace{2.0cm}
-    {\itshape\large Alen Stepic - XX-XXX-XXX \\Chi Xu - XX-XXX-XXX \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - XX-XXX-XX \par}
+    {\itshape\large Alen Stepic - 11-475-258 \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - 13-606-355 \\Chi Xu - XX-XXX-XXX \par}
     	\begin{spacing}{1}
@@
 
+\clearpage
+
+%************************** Abstract Page ************************** 
     \begin{abstract}
     \pagenumbering{Roman}
-    	\begin{spacing}{1.5}
-    	(Insert text)
-    	\end{spacing}
+    This paper, examines the dynamics between the amount of twitter activity regarding bitcoin and the actual price fluctuation of bitcoin.
+For the analysis two sets of data have been collected.
+One reflecting twitter activity and the other one showing the bitcoin prices for the same period.
+Based on that an econometric model is used for the statistical analysis and the interpretation of the results.
+This work was created in the context of a programming course for economists at the university of St.
+Gallen.
+To not exceed the framework of this study we require extensive knowledge in econometrics and take concepts as known.
+The underlying goal was to get familiar with software engineering tools and project management.
+Therefore, the academic content of this work is neither completed nor concluding.\\
     \end{abstract}
@@
 \clearpage
+
+%************************** Contenttable Page ************************** 
 	\tableofcontents
+
 \clearpage
 
+%************************** Chapters 1-4 **************************
 	\begin{spacing}{1.2}
 	\cleardoublepage\pagenumbering{arabic}
+
 		\section{Research Question}
+		\textnormal {In this paper, we aim to examine the existence of a correlation between the price development of bitcoin and how much people talk about bitcoin online on Twitter.
+We have been inspired by the large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network where people interact.
+For orientation, we used the paper by Mao, Counts and Bollen (2015), who claim that sentiment analysis using Twitter data can significantly predict Market prices.
+We want to examine if this statement holds when we look at a specific asset like bitcoin.}\\
+
 		\clearpage
+
 		\section{Brief Background and Data Collection}
+		\itshape\textbf {Bitcoin}\\
+		\textnormal {(Text for Bitcoin)}\\
+
+		\itshape\textbf {Twitter}\\
+		\textnormal {(Text for Twitter)}\\
+
+		\itshape\textbf {Data Collection}\\
+		\textnormal {For our dataset, we used 2 different sources.
+We first collected historical data on bitcoin prices to USD and secondly, we gathered twitter massages related to bitcoin.
+We fulfil this relationship by selecting tweets that contain the term “bitcoin” in the text message.
+The time period for both collected data sets was from 21.12.2017 16:00:00 UTC to 26.12.2017 16:00:00 in an hourly basis.
+We chose an hourly basis to be able to do a statistical analysis with a certain amount of observation for the restricted processing time of this homework.\\
+For the bitcoin prices, a publicly available API from CoinDesk was used (Source?
+See documentation?).
+The prices collected represent the final price level of bitcoin before every hour changes.
+For example, our first listed price of bitcoin was on 21.12.2017 at 16:59:59 and our last value on 26.12.2017 at 15:59:59.
+These values construct our first time series data set and are shown in the following graph.\\}
+
 		\clearpage
+
 		\section{Econometric Modelling and Results}
+		\textnormal {As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
+From our data collection, we are left with two time series datasets representing two variables.
+A broadly used statistical method to simultaneously analyze multiple time series is the VAR (Vector Autoregression) approach.
+In this approach the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (Lütkepohl, 2005, p.
+4-5).\\
+To generate the econometric results that follow we used the statistical software STATA.}
+
+		\itshape\textbf {Stationarity}\\
+		\textnormal {Before estimating a VAR model, the time series data must be checked for stationary.
+Thus, the means and variances are constant over time and the datasets do not show any trending behavior.
+Non-stationary data can lead to an inaccurate model which is undesirable.
+To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test and get following results from STATA.\\
+Interpreting the results and accepting or rejecting stationarity.}
+
+		\itshape\textbf {Lag Specification}\\
+		\textnormal {To select the optimal number of lags in our VAR regression we check for various information criteria.
+Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (Brandt and Williams, 2007, p.
+27).
+The calculations of these criteria for our given data set is easily done by a statistical software and given in the following table.\\}
+
+		\itshape\textbf {VAR Regression Model}\\
+		\textnormal {In this paper, we use a basic unrestricted VAR model which consists of two endogenous variables, T for aggregate tweets and B for bitcoin prices.
+The selected time lag is 3 and this choice will be discussed later.
+Given that the model equations can be written as follows:\\}
+
+		\itshape\textbf {Granger Causality}\\
+		\textnormal {To assess the causal relationship between our two endogenous variables and interpret the result we use the Granger causality.
+This test confirms if one variable is statistically useful to predict the other variable.
+If this is given the dynamics stated by the calculated coefficient above can be assumed to be valuable.\\
+A second analysis to interpret our results is the impact response analysis.
+This evaluates the impact of changes in the one variable to the other variable.
+This is also provided by STATA and the results can be seen in the following graphs.}
+
+		\itshape\textbf {Impulse Response Analysis}\\
+
 		\clearpage
+
 		\section{Conclusion}
+		\textnormal {(Insert text)}
+
+		\clearpage
+
 	\end{spacing}
@@
 \clearpage
+
+%************************** Bibliography **************************
 \printbibliography
+\clearpage
 
+%************************** DOCUMENT-END **************************
 \end{document}

### 2017-12-28 CollectCryptocurrencyData.py
add functionality that the first row of the aggregated csv has no values for the df columns

@@ -1,12 +1,10 @@
 
-# Script: CollectCrypocurrencyData.py
+# Script: collectCrypocurrencyData.py
 # Authors: Joel Sonderegger
 
 """ This script gets crypocurrency data.
     The output is a csv-file with the crypocurrency prices.
 """
-
-
 
 import numpy as np
 import json
@@ -22,6 +20,7 @@ import hmac
 import requests
 import time
 
+# keys and variables required for bitcoinaverage api
 secret_key = 'ZTIyNDc2YjE2NmViNGZmMTllZGRkYzM2YWM4MWY4NTk4NTFjZjNiOTI2ZTY0ODQ0OTQzMWNmNzE0ZTU0ODU0YQ'
 public_key = 'NzhlNjI2YjY2MTI2NGEzZmEwN2U2ZDExZGY4NDZiNzk'
 timestamp = int(time.time())
@@ -39,7 +38,7 @@ def getHourlyBPI():
     print(bpi_data)
     return bpi_data
 
-# not used so far
+# Enriching the prices with % changes. not used so far.
 def getEnrichedBPI(bpi):
     enrichedBPI = {}
     prevDayPriceStorage = 0
@@ -48,12 +47,11 @@ def getEnrichedBPI(bpi):
         
         changeInAbsolute = value['price'] - prevDayPriceStorage
 
-        # prevent a division by 0 (would happen on first day)
+        # prevent a division by 0 (would happen for first data point)
         if (prevDayPriceStorage != 0):
             changeInPercentage = (changeInAbsolute / prevDayPriceStorage) * 100
         else:
             changeInPercentage = 0
-
 
         enrichedBPI[key] = {'price': value['price'], 'changeInPercentage': changeInPercentage, 'changeInAbsolute': changeInAbsolute }
 
@@ -72,7 +70,6 @@ def generateCSV(bpi_data):
     # creating list that will contain all bpi data
     bpi_data_array = []
     
-
     # loop through bpi_data(json) and create a list(day_array) which is appended to the list that contains all bpi data(bpi_data_array)
     for day in bpi_data:
         day_array = [day['time'],day['average'],day['high'],day['low'],day['open']]

### 2017-12-28 aggregateTwitterBpi.py

@@ -1,12 +1,11 @@
-# Script: collectCrypocurrencyData.py
-# Authors: Joel Sonderegger
+# Script: aggregateTwitterBpi.py
+# Author: Joel Sonderegger
 
-""" This script calculates the correlation between tweets containing 'bearish' or 'bullish' and the bitcoin price
+""" This script aggregates the Tweets and BPI data. Bascially, it (1) takes the two data sets, (2) drops unnecessary data, (3) counts the nr of tweets of each hour, and (4) merges the remaining data. Additionally, (5) the first differences (+ log first differences) of the nr of tweets and BPI is part of the output.
 """
 
 import pandas as pd
 import numpy as np
-import pprint
 import csv
 import io
 
@@ -21,7 +20,7 @@ def load_tweets():
     df = pd.read_csv('data/20171223_0056_twitterData.csv')
     return df
 
-# Gets bpi data from CSV-File. Returns a data frame with bpi data
+# Gets bpi data from CSV-File. Returns a data frame with bpi data.
 def load_bpi():
     bpi_data = pd.read_csv('data/bpi.csv')
 
@@ -30,13 +29,12 @@ def load_bpi():
     bpi_data.drop('high', axis=1, inplace=True)
     bpi_data.drop('low', axis=1, inplace=True)
 
-    # create new column 'close'. The close price is the open price of the previous hour
+    # create new column 'close'. The close price is the open price of the previous hour (thus, shifting the open price -1 to get the close price)
     bpi_data['close'] = bpi_data['open']
     bpi_data['close'] = bpi_data['close'].shift(-1)
     
     # Set time as DataFrame index.
     times = bpi_data.set_index(pd.DatetimeIndex(bpi_data['time']))
-    
     bpi_data = bpi_data.set_index([times.index.year, times.index.month, times.index.day, times.index.hour])
  
     # set correct index names for Y, M, D, H
@@ -113,7 +111,6 @@ def count_tweets_per_hour(tweets):
 
     #group by year, month, day and hour
     grouped_tweets_per_hour = tweets.groupby([times.index.year, times.index.month, times.index.day, times.index.hour]).count()
-    
 
     # set correct index names for Y, M, D, H
     grouped_tweets_per_hour.index = grouped_tweets_per_hour.index.set_names('Y', level=0)
@@ -129,6 +126,13 @@ def count_tweets_per_hour(tweets):
 
 
 def generate_csv(df_merged):
+
[…]

### 2017-12-28 aggregateTwitterBpi.py
change path of twitter data set in aggregate script

@@ -17,7 +17,7 @@ import math
 
 # Gets tweets from CSV-File. Returns a data frame with tweets
 def load_tweets():
-    df = pd.read_csv('data/20171223_0056_twitterData.csv')
+    df = pd.read_csv('data/twitterData.csv')
     return df
 
 # Gets bpi data from CSV-File. Returns a data frame with bpi data.

### 2017-12-28 documentation/documentation.tex
start describe the process of aggregateTwitterBpi.py

@@
 \usepackage{setspace}
+
+%% packages for tikz diagrams
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+
+%% styling for tikz diagrams
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
+\tikzstyle{process} = [rectangle, minimum width=10cm, minimum height=1cm, text centered, text width=10cm, draw=black, fill=orange!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin".
-The python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
+The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
 This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime.
@@
 
-\item Setup Pyhton3
+\item Setup Python3
 \begin{enumerate}
@@
 \end{lstlisting}
-\item Start python program using the command
+\item Start Python program using the command
 \begin{lstlisting}[language=bash]
-python3 CollectTwitterData.py
+python3 collectTwitterData.py
 \end{lstlisting}
@@
 \section{Data Aggregation and Data Wrangling}
-Before the collected data sets can be analyzed they need to be aggregated. In addition, some data wrangling is necessary to bring the data in a format which than can be analyzed.
+After the tweets and BPI data set is generated needs to be aggregated before it can be analyzed.
+In addition, some data wrangling is necessary to bring the data in a format which than can be analyzed.
+The script \verb|aggregateTwitterBpi.py| does all this.
+
+\subsubsection{Process}
+The process of the script \verb|aggregateTwitterBpi.py| works as follows:
+\begin{figure}[H]
+    \centering
+    \begin{tikzpicture}[node distance=1.6cm]
+        \node (start) [startstop] {Start};
+        \node (pro1) [process, below of=start] {Load BPI data set};
+        \node (pro2) [process, below of=pro1] {Calculate first differences for BPI data};
+        \node (pro3) [process, below of=pro2] {Load tweets data set};
+        \node (pro4) [process, below of=pro3] {Count number of tweets on an hourly basis};
+        \node (pro5) [process, below of=pro4] {Calculate first differences for number of tweets on an hourly basis};
+        \node (pro6) [process, below of=pro5] {Merge number of tweets with BPI data (incl. first differences)};
+        \node (pro7) [process, below of=pro6] {Generate and save CSV file};
+        \node (stop) [startstop, below of=pro7] {Stop};
+
+        \draw [arrow] (start) -- (pro1);
+        \draw [arrow] (pro1) -- (pro2);
+        \draw [arrow] (pro2) -- (pro3);
+        \draw [arrow] (pro3) -- (pro4);
+        \draw [arrow] (pro4) -- (pro5);
+        \draw [arrow] (pro5) -- (pro6);
+        \draw [arrow] (pro6) -- (pro7);
+        \draw [arrow] (pro7) -- (stop);
+    \end{tikzpicture}
+    \caption{Data aggregation and data wrangling process} \label{fig:dataaggregation}
+\end{figure}
+
+Here a short description of what happens at the various steps: 
+\linebreak\linebreak
+\textbf{Load BPI data set} The script takes the BPI data set that is located at \verb|data/bpi.csv|.
+\linebreak\linebreak
+\textbf{Calculate first differences for BPI data} The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated.
+The reason for calculating these values is given in the data analysis section.
+\linebreak\linebreak
+\textbf{Load tweets data set} The script takes the tweets data set that is located at \verb|data/twitterData.csv|.
+\linebreak\linebreak
+\textbf{Count number of tweets on an hourly basis} 
+\linebreak\linebreak
+\textbf{Calculate first differences for number of tweets on an hourly basis} 
+\linebreak\linebreak
+\textbf{Merge number of tweets with BPI data (incl. first differences)} 
+\linebreak\linebreak
+\textbf{Generate and save CSV file}
 
 \subsubsection{Execution}
-By executing the python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
+By executing the Python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
 \begin{lstlisting}[language=bash]
@@
 \subsubsection{Output}
-After successfully running the python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
+After successfully running the Python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
 It is important to note that every execution of the script overwrites any existing \verb|nr_of_tweets_bpi_closing_price.csv| file.
@@
     \item time: Timestamp on an hourly basis in UTC time
-    \item {nr\_of\_tweets}: 
-    \item {df\_nr\_of\_tweets}: 
-    \item {log\_df\_nr\_of\_tweets}: 
-    \item {df\_bpi\_closing\_price}: 
-    \item {log\_df\_bpi\_closing\_price}: 
+    \item {nr\_of\_tweets}: Sum of tweets
+    \item {df\_nr\_of\_tweets}: First difference of the sum of tweets
+    \item {log\_df\_nr\_of\_tweets}: Natural logarithm of the first difference of the sum of tweets
+    \item {bpi\_closing\_price}: BPI closing price
+    \item {df\_bpi\_closing\_price}: First difference of the BPI closing price
+    \item {log\_df\_bpi\_closing\_price}: Natural logarithm of the first difference of the BPI closing price
 \end{itemize}

### 2017-12-28 CollectCryptocurrencyData.py

@@ -90,9 +90,6 @@ def generateCSV(bpi_data):
        writer = csv.writer(csvFile)
        writer.writerows(bpi_data_array)
 
-    # (bpi_data_array) - 1 because we don't want to count the header
-    print("Added " + str(len(bpi_data_array)-1) + " entries to data/bpi.csv")
-
     return None
 
 # Begin the Python script that will do the workdef main():

### 2017-12-28 aggregateTwitterBpi.py

@@ -1,7 +1,7 @@
 # Script: aggregateTwitterBpi.py
 # Author: Joel Sonderegger
 
-""" This script aggregates the Tweets and BPI data. Bascially, it (1) takes the two data sets, (2) drops unnecessary data, (3) counts the nr of tweets of each hour, and (4) merges the remaining data. Additionally, (5) the first differences (+ log first differences) of the nr of tweets and BPI is part of the output.
+""" This script aggregates Tweets and BPI data. Bascially, it (1) takes the two data sets, (2) drops unnecessary columns, (3) counts the number of tweets for each hour, and (4) merges the remaining data. Additionally, (5) the first differences (+ log first differences) of the number of tweets and BPI is part of the output.
 """
 
 import pandas as pd
@@ -160,14 +160,14 @@ def generate_csv(df_merged):
 
 def main():
 
-    # load tweets from csv-file
-    tweets = load_tweets()
-
     # load bitcoin price index (bpi) data from csv-file
     bpi_data = load_bpi()
 
     # enrich BPI data frame with first difference and log first difference
     bpi_data = first_difference_bpi(bpi_data)
+
+    # load tweets from csv-file
+    tweets = load_tweets()
 
     # count number of tweets per hour
     print('Counting the number of tweets. This can take some minutes...')

### 2017-12-28 documentation/documentation.tex
adjusted spelling and punctuation mistakes

@@
 \subsubsection{Hardware Setup}
-As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin".
+As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword "bitcoin".
 The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
-This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime.
-Furthermore due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server.
+This approach allowed us to ensure a continuous data stream while being able to access the program output regardless of time and location.
+Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server.
 The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline

### 2017-12-28 documentation/documentation.tex
added sources in intro, twitter, bib.file and abbreviations of bitcoin part

--- 2017-12-27 documentation/documentation.tex
@@
 % List of abbreviations
-\usepackage{acronym}
+\usepackage {acronym}
 
@@
 
-    \begin{abstract}
-    \pagenumbering{Roman}
-    \begin{spacing}{1.5}
-
-  (Insert text)
-
-    \end{spacing}
-
-    \end{abstract}
-
     \clearpage
@@
 	\acro{SSH}{Secure Shell}
+	\acro{BPI}{Bitcoin Price Index}
+	\acro{BTC}{Bitcoin}
+	\acro{USD}{US Dollar}
 	\end{acronym}
@@
 In the academic environment accountability and reproducibility is important.
-However, the publishing process of papers and journals seem to be outdated.
-New ways of data collection and data processing exist by using computational economics.
+However, the publishing process of papers and journals seem to be outdated as reproducability is not evaluated by many journals.
+(\cite{mccullough2013}) New ways of data collection and data processing exist by using computational economics.
 The usage of algorithms can increase effectiveness and efficiency.
@@
 However this creates also new problems regarding to traceability and reproducibility.
-Often cited academic paper exist, where the initial computation is not reproducible.
-Furthermore, some academic paper even contain computational errors.
+Often cited academic paper exist, where the initial computation is not reproducible (\cite{mccullough2013}).
 Replicating data or existing results do not provide any new knowledge at all.
-Nevertheless, the ability to reproduce increases trustworthiness and indicate the quality of the conducted work.
+Nevertheless, the ability to reproduce is key in science and non-reproducable work can not be characterized as science or used as a basis for policy making (\cite{mccullough2013}).
 This explains why reproduction is of great relevance.
@@
 Twitter offers different Application Programming Interfaces (API) for collecting data.
-However, the time frame for gathering data on a freely base is limited to 7 days.
+However, the time frame for gathering data on a freely base with full access is limited to 7 days (\cite{twitterinc2017a}).
 On the other hand, python offers different twitter libraries.
@@
 The identification is assured by different keys and access tokens.
-Those are the (1) consumer key (ckey), (2) consumer secret (csecret), (3) access token (atoken) and (4) access token secret (asecret).
+Those are the (1) consumer key (CKEY), (2) consumer secret (CSECRET), (3) access token (ATOKEN) and (4) access token secret (ASECRET).(\cite{twitterinc2017b})
 
@@
 \begin{lstlisting}[language=bash]
-https://apps.twitter.com/
+%https://apps.twitter.com/
 \end{lstlisting}
 
-After the creation of a application, the keys and tokens can be extracted. Figure 1 illustrates how to retrieve the keys and tokens.
+After the creation of a application, the keys and tokens can be extracted. Figure \ref{Fig:Keys and Tokens} illustrates how to retrieve the keys and tokens.
 \begin{figure}[h]
@@
 \includegraphics[scale=0.6]{twitteraccess}
-\caption{Twitter Keys and Access Tokens}
+\caption{Twitter Keys and Access Tokens, based on \cite{twitterinc2017c}.}
+\label{Fig:Keys and Tokens}
 \end{figure}
@@
     \item created at: Timestamp of the created tweet
-    \item text: text of the tweet
+    \item text: Text of the tweet
 \end{itemize}
-The time timestamps are in UTC time.
+The timestamps are in UTC time.
 

### 2017-12-28 documentation/documentation.tex
add requirement.txt and add setup part to documentation

@@
 \clearpage
+
+\section{Setup}
+\subsection{Requirements to run Python scripts}
+Before you go any further, make sure that at least Python version 3.0.0 available from your command line. You can check this by running:
+\begin{lstlisting}[language=bash]
+    python --version
+\end{lstlisting}
+You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
+\newline
+On top you need various packages.
+We created a the requirements file \verb|requirements.txt|, which contains all required packages to run Python scripts of the project.
+The list of packages to be installed using pip install like so:
+\begin{lstlisting}[language=bash]
+    pip install -r requirements.txt
+\end{lstlisting}
+Now you should be ready to run the Python scripts.
+
+\subsection{Stata}
+(Dimitri's Part: stata version and anything else required to do your calculations)
 
@@
 
-\subsubsection{Process}
+\subsection{Process}
 The process of the script \verb|aggregateTwitterBpi.py| works as follows:
@@
 \linebreak\linebreak
-\textbf{Count number of tweets on an hourly basis} 
+\textbf{Count number of tweets on an hourly basis} First, groups the tweets by hour. Second, counts the number of tweets for every hour.
 \linebreak\linebreak
-\textbf{Calculate first differences for number of tweets on an hourly basis} 
+\textbf{Calculate first differences for number of tweets on an hourly basis} The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated.
+Again, the reason for calculating these values is given in the data analysis section.
 \linebreak\linebreak
 \textbf{Merge number of tweets with BPI data (incl. first differences)} 
+Insert Image
 \linebreak\linebreak
-\textbf{Generate and save CSV file}
+\textbf{Generate and save CSV file} Finally, a CSV file is generated with the merged data.
 
-\subsubsection{Execution}
+\subsection{Execution}
 By executing the Python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
@@
 
-\subsubsection{Output}
+\subsection{Output}
 After successfully running the Python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.

### 2017-12-28 aggregateTwitterBpi.py

@@ -147,16 +147,10 @@ def generate_csv(df_merged):
     # addind the header to the list which contains contains nr of tweets and the bpi closing price for every hour
     data_array = [header] + data_array
 
-    # Defines the path where the data should be written
-    #csvFile = open('data/nr_of_tweets_bpi_closing_price.csv', 'w')
-
     # write the the list which contains nr of tweets and the bpi closing price for every hour (inkl. header) to csv-file
     with open('data/nr_of_tweets_bpi_closing_price.csv', 'w', newline='') as outfile:
         writer = csv.writer(outfile)
         writer.writerows(data_array)
-
-   
-       
 
     return None
 
@@ -180,6 +174,8 @@ def main():
     # enrich tweets_per_hour data frame with first difference and log first difference
     tweets_per_hour = first_difference_tweets(tweets_per_hour)
 
+    print(tweets_per_hour)
+    print(bpi_data)
     # merge number of tweets per hour with bitcoin price index (bpi) data
     df_merged = tweets_per_hour.join(bpi_data, how='left')
     print('Tweets and BPI data is merged.')

### 2017-12-28 paper/paper.tex

@@
 Based on that an econometric model is used for the statistical analysis and the interpretation of the results.
+
+    INPUT ALEN: ADD JUST KEY FINDING THE REST I LIKE
+
     This work was created in the context of a programming course for economists at the university of St.
@@
 	\tableofcontents
+	\clearpage
+%************************** List of Figures ************************** 	
+    \listoffigures
+%************************** List of Figures ************************** 	   
+    \section*{List of Abbreviation} 
+	\begin{acronym}[ASECRETTT] 
+	\acro{VAR}{Vector Autoregression}
+	\acro{EMH}{Efficient Market Hypothesis}
+	\end{acronym}
 
@@
 \cleardoublepage\pagenumbering{arabic}
+\section{Introduction}
+Malkil and Fama introduced in 1970 the Efficient Market Hypothesis (EMH), where actual prices include all information and investors act rational.
+This hypothesis is broadly accepted in the financial world.
+However, the digitalisation leads to an increased network effect where information can be share within second over the globe.
+Furthermore, the EMH fails to address the behavioural and emotional role of investors.
+The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
+Mao, Counts and Bollen (2015), claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as an sentiment indicator for bitcoin prices.
+As digitalization is expected to continue in the future, crypotocurrencies will hypothetical get more important.
+Thus, the topic is relevant.
 
-		\section{Research Question}
-		\textnormal {In this paper, we aim to examine the existence of a correlation between the price development of bitcoin and how much people talk about bitcoin online on Twitter.
-We have been inspired by the large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network where people interact.
-For orientation, we used the paper by Mao, Counts and Bollen (2015), who claim that sentiment analysis using Twitter data can significantly predict Market prices.
-We want to examine if this statement holds when we look at a specific asset like bitcoin.}\\
+\subsection{Research Question and Goal of the Paper}
+As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount people talk about bitcoin on twitter.
+The goal should be reached by answering the following research question:
+
+In what extend does the amount of twitter tweets influence the price of bitcoin?
+
+\subsection{Methodology}
+To answer the above mentioned research question a scientific approach has been applied.
+The paper consists out of three parts.
+The first part contains an introduction into the topic by pointing out the relevance of the topic, the research question, methodology and the scope.
+This is conducted in chapter 1.
+The second part is characterized as the theory part.
+The theory aims to provide to the reader the necessary background information by an introduction of relevant bitcoin and twitter information in context of the paper.
+The conducted research is based on forward research and using relevant sources.
+Furthermore, it contains a short introduction into the Vector Autoregression approach (VAR) and the constrains in context with the paper.
+Chapter XYZ The third part contains the discussion of the results and a conclusion.
+The conclusion is based on the theory and the own conducted mathematical computation.
+Those computations are based on a data set, which was gathered by own coded python scripts for the timeperiod ADD TIME PERIOD.
+The data set contains out of two data sources (1) twitter tweets which contain the buzzword "bitcoin" and (2) historical bitcoin prices.
+Those two sources has been aggregated with a separate python script.
+The output of aggregation was further proceeded with stata to conduct the VAR on a daily basis.
+Chapter 4 and 5
+
+INPUT: IS IT NOW DAILY? WHAT IS THE REASON?
+
+\subsection{Scope}
+The paper's focus lies on the scientific discussion and answer of the research question mentioned above.
+The research question has consciously been design very tiny, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high quality scientifc paper.
+The approach and technical issues (like code scripts etc.) are not addressed.
+Those points are explained in the separate documentation paper.
+It is not a deep description of the code as the code itself as the code is documented separately.
+Nevertheless, important lines of code are discussed.
 
@@
 		\itshape\textbf {Bitcoin}\\
-		\textnormal {(Text for Bitcoin)}\\
+		\textnormal {(Text for Bitcoin) Input Alen: Explain why bitcoin is of relevance, short intro what bitcoin is}\\
 
 		\itshape\textbf {Twitter}\\
-		\textnormal {(Text for Twitter)}\\
+		\textnormal {(Text for Twitter) Input Alen: Explain why twitter is the right source and and some facts about it}\\
 

### 2017-12-28 documentation/documentation.tex
added dokumentation for section 4: Data Analysis

@@
 \section{Data Analysis}
-(Dimitri's Part)
+The data analysis was performed with the statistical software STATA.
+The corresponding stata file and .do file are stored in the folder statistical\_analysis\_stata.
+Following we describe all the commands used to produce our econometric model.
+
+\smallskip Step 1:\\
+After starting data the first step was to import the data file (.csv file) into stata. We did so by following command (be carefull your location of the .csv file may differ):\\
+	\begin{lstlisting}[language=bash]
+    import delimited "your_location.csv"
+	\end{lstlisting}
+
+\smallskip Step 2:\\
+STATA is not recognizing our variable "time" as a date variable and therefore we create a new variable "time2" and giving it the same values as "time" and giving it the same format as "time" has.
+At the end we define "time2" to be a time series with an hourly progress\\
+	\begin{lstlisting}[language=bash]
+    gen double time2 = clock(time, "YMD hms")\\
+	format time2 %tcNN-DD-CCYY_HH:MM:SS\\
+	order time2, after(time)\\
+	tsset time2, format(%tcNN-DD-CCYY_HH:MM:SS) delta(1 hours)
+	\end{lstlisting}
+
+\smallskip Step 3:\\
+Checking for stationarity for all variables by using the Augmented Dickey-Fuller (ADF) test with a time delay of 0 periods (lag 0).\\
+	\begin{lstlisting}[language=bash]
+	dfuller nr_of_tweets, lags(0)
+	dfuller df_nr_of_tweets, lags(0)
+	dfuller log_df_nr_of_tweets, lags(0)
+	dfuller bpi_closing_price, lags(0)
+	dfuller df_bpi_closing_price, lags(0)
+	dfuller log_df_bpi_closing_price, lags(0)
+	\end{lstlisting}
+
+\smallskip Step 4:\\
+Calling the lag-order selection criteria statistics for our VAR model.
+The maximum amount of lags is 7 and the variables that we chose for the latter VAR model are df\_nr\_of\_tweets and df\_btc\_closing\_price.\\
+	\begin{lstlisting}[language=bash]
+	varsoc df_nr_of_tweets df_btc_closing_price, maxlag(7)
+	\end{lstlisting}
+
+\smallskip Step 5:\\
+Running the VAR regression for our two variables and recommended lag of 2 (from Results of Step 4).\\
+	\begin{lstlisting}[language=bash]
+	var df_nr_of_tweets df_btc_closing_price, lags(1/2)
+	\end{lstlisting}
+
+\smallskip Step 6:\\
+Calling the granger causality test with lag length 2.\\
+	\begin{lstlisting}[language=bash]
+	Vargranger
+	\end{lstlisting}
+
+\smallskip Additionally:\\
+The Regression Results were exportet to a latex format by instaling and using the outreg2 package.
+This piece of latex code was then inserted into in the paper.
+All other results we edited with an image software and inserted them as .png file into the paper\\
+	\begin{lstlisting}[language=bash]
+	ssc install outreg2
+	outreg2 using var_gegression_results.tex, replace
+	\end{lstlisting}
 

### 2017-12-28 documentation/documentation.tex
added section 2.2 about STATA

@@
 \subsection{Stata}
-(Dimitri's Part: stata version and anything else required to do your calculations)
+For the data analysis, we used the statistical software STATA (version 14.2).
+When seeking for statistical analysis, regression analysis or data management, STATA is a capable tool.
+To reproduce our results, you need to have the STATA software installed in your local computer and after starting the program you can follow the guidelines in chapter 4 (data analysis).
 

### 2017-12-28 documentation/documentation.tex
extend aggregation part

--- 2017-12-28 documentation/documentation.tex
@@
 \subsubsection{Hardware Setup}
-As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword "bitcoin".
+As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword \"bitcoin\".
 The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.

### 2017-12-29 paper/paper.tex
added bitcoin part

@@
 		\itshape\textbf {Bitcoin}\\
-		\textnormal {(Text for Bitcoin) Input Alen: Explain why bitcoin is of relevance, short intro what bitcoin is}\\
+		\textnormal {After the global financial crisis, Satoshi Nakamoto (2008, p.
+1) claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
+Starting from his whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions (blockchain) has been developed (Nakamoto, 2008, p.
+1).\newline
+Today, Bitcoin is the most popular of over 1300 so-called cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
+Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for payment purposes.
+Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (Corbet, Lucey \& Yarovya, 2017, Forbes 2017, Yermack, 2013).
+Kristoufek (2015, Discussion) points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term.
+However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency.
+Kristoufek (2015) further explains the correlation is most evident in the long run.
+During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Discussion).
+These findings are in line with other researchers’ findings (see Garcia et.
+al 2014, Kondor et al.
+2014).\newline
+One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices.
+(Mao et al.,2015, p.
+3) A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data.
+Based on analysis of the influence of twitter bullishness on the stock market by Mao et al.
+(2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.
+ }\\
 

### 2017-12-29 paper/paper.tex
adjusted bitcoin part and source

@@
 Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for payment purposes.
-Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (Corbet, Lucey \& Yarovya, 2017, Forbes 2017, Yermack, 2013).
-Kristoufek (2015, Discussion) points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term.
+Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013).
+Kristoufek (2015) points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term.
 However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency.
 Kristoufek (2015) further explains the correlation is most evident in the long run.
-During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Discussion).
-These findings are in line with other researchers’ findings (see Garcia et.
-al 2014, Kondor et al.
-2014).\newline
+During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Kristoufek, 2015).
+These findings are in line with other researchers (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\newline
 One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices.
-(Mao et al.,2015, p.
+(Mao et al., 2015, p.
 3) A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data.

### 2017-12-29 documentation/documentation.tex
add DeclareLanguageMapping to doc to solve issues
correcting scources, references, adding declaration of ownership, figure 1 formatting in the text

@@
 \usepackage[style=apa]{biblatex}
-%\DeclareLanguageMapping{american}{american-apa}
+\DeclareLanguageMapping{american}{american-apa}
+
 \addbibresource{references.bib}
@@
 
-    \listoffigures 	
+    \listoffigures\bigskip 
     \section*{List of Abbreviation} 
@@
 	\acro{ASECRET}{Access Token Secret}
+	\acro{BPI}{Bitcoin Price Index}
+	\acro{BTC}{Bitcoin}
 	\acro{CKEY}{Consumer Key}
@@
 	\acro{SSH}{Secure Shell}
-	\acro{BPI}{Bitcoin Price Index}
-	\acro{BTC}{Bitcoin}
 	\acro{USD}{US Dollar}
@@
 However, the publishing process of papers and journals seem to be outdated as reproducability is not evaluated by many journals.
-(\cite{mccullough2013}) New ways of data collection and data processing exist by using computational economics.
+\parencite[p.~888]{mccullough2003} New ways of data collection and data processing exist by using computational economics.
 The usage of algorithms can increase effectiveness and efficiency.
@@
 However this creates also new problems regarding to traceability and reproducibility.
-Often cited academic paper exist, where the initial computation is not reproducible (\cite{mccullough2013}).
+Often cited academic paper exist, where the initial computation is not reproducible \parencite[pp.~874--887]{mccullough2003}.
 Replicating data or existing results do not provide any new knowledge at all.
-Nevertheless, the ability to reproduce is key in science and non-reproducable work can not be characterized as science or used as a basis for policy making (\cite{mccullough2013}).
+Nevertheless, the ability to reproduce is key in science and non-reproducable work can not be characterized as science or used as a basis for policy making \parencite[p.~888]{mccullough2003}.
 This explains why reproduction is of great relevance.
@@
 Twitter offers different Application Programming Interfaces (API) for collecting data.
-However, the time frame for gathering data on a freely base with full access is limited to 7 days (\cite{twitterinc2017a}).
+However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}.
 On the other hand, python offers different twitter libraries.
@@
 The identification is assured by different keys and access tokens.
-Those are the (1) consumer key (CKEY), (2) consumer secret (CSECRET), (3) access token (ATOKEN) and (4) access token secret (ASECRET).(\cite{twitterinc2017b})
+Those are the (1) consumer key (CKEY), (2) consumer secret (CSECRET), (3) access token (ATOKEN) and (4) access token secret (ASECRET).
+\parencite{twitterinc2017b}
 
@@
 
-After the creation of a application, the keys and tokens can be extracted. Figure \ref{Fig:Keys and Tokens} illustrates how to retrieve the keys and tokens.
-\begin{figure}[h]
+After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.
+\begin{figure}[H]
 \centering
 	\includegraphics[scale=0.6]{twitteraccess}
-\caption{Twitter Keys and Access Tokens, based on \cite{twitterinc2017c}.}
-\label{Fig:Keys and Tokens}
+\caption{Twitter Keys and Access Tokens, based on \textcite{twitterinc2017c}.}
+	\label{figkeysandtokens}
 \end{figure}
@@
 
+%************************** Declaration of Authorship **************************
+\section{Declaration of Authorship}
+We hereby declare,
+\begin{itemize}
+    \item that we have written this thesis without any help from others and without the use of documents and aids other than those stated above;
+    \item that we have mentioned all the sources used and that we have cited them correctly according to established academic citation rules;
+    \item that we have acquired any immaterial rights to materials we may have used such as images or graphs, or that we have produced such materials ourself;
+    \item that the topic or parts of it are not already the object of any work or examination of another course unless this has been explicitly agreed on with the faculty member in advance and is referred to in the thesis;
+    \item that we will not pass on copies of this work to third parties or publish them without the University’s written consent if a direct connection can be established with the University of St.Gallen or its faculty members;
+    \item that we are aware that our work can be electronically checked for plagiarism and that we hereby grant the University of St.Gallen copyright in accordance with the Examination Regulations in so far as this is required for administrative action;
+    \item that we are aware that the University will prosecute any infringement of this declaration of authorship and, in particular, the employment of a ghostwriter, and that any such infringement may result in disciplinary and criminal consequences which may result in our expulsion from the University or us being stripped of our degree.
+\end{itemize}
+
+\begin{flushleft}
+................................\\
+Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip 
+................................\\
+Severin Kranz - 13-606-355\\\bigskip\bigskip
+................................\\
+Joël Sonderegger - 11-495-488\\\bigskip\bigskip
+................................\\
+Alen Stepic - 11-475-258\\\bigskip\bigskip
+................................\\
+Chi Xu - XX-XXX-XXX
+
+By submitting this academic term paper, we confirm through my conclusive action that we are submitting the Declaration of Authorship, that we have read and understood it, and that it is true.
+
+\end{flushleft}
+\clearpage
+
 %************************** DOCUMENT-END **************************

### 2017-12-29 paper/paper.tex
added outline for twitter part

@@
 		\itshape\textbf {Twitter}\\
-		\textnormal {(Text for Twitter) Input Alen: Explain why twitter is the right source and and some facts about it}\\
+		\textnormal { Outline: Growth of Social Media, Opinion Mining, Twitter -> micro-blogging platform, tweets, functionalities, etc.
+; Why good for measuring opinions ?
+"gold mine"; Sentiment Analysis, What we do.
+Comment Severin: This part will contain the following steps and will be mostly based on Stenqvist et al. Predicting Bitcoin price fluctuation
+with Twitter sentiment analysis - sections 2.2, 2.3\newline
+1) Introduction sentence -> growth of social media https://www.statista.com/statistics/278414/number-of-worldwide-social-network-users/\newline
+2) Twitter as a "gold mine" to gather opinions -> What is twitter, Why is it valuable -> length of messages etc.\newline
+3) Sentiment Analysis -> what is a sentiment analysis\newline
+4) Sentiment Analysis of the term bitcoin based on twitter -> explain what we do }\\
 

### 2017-12-29 paper/paper.tex
added doc: references to toc, pap: doO,scources,bib

--- 2017-12-29 paper/paper.tex
@@
 
-    INPUT ALEN: ADD JUST KEY FINDING THE REST I LIKE
+INPUT ALEN @DIMI: ADD JUST KEY FINDING THE REST I LIKE
 
@@
 %************************** List of Figures ************************** 	
-    \listoffigures
+    \listoffigures\bigskip\bigskip 
 %************************** List of Figures ************************** 	   
@@
 	\acro{EMH}{Efficient Market Hypothesis}
+	\acro{etc}{et cetera}
 	\end{acronym}
@@
 \section{Introduction}
-Malkil and Fama introduced in 1970 the Efficient Market Hypothesis (EMH), where actual prices include all information and investors act rational.
+\label{sec:intro}
+\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information.
 This hypothesis is broadly accepted in the financial world.
-However, the digitalisation leads to an increased network effect where information can be share within second over the globe.
-Furthermore, the EMH fails to address the behavioural and emotional role of investors.
+The digitalisation leads to an increased network effect, where information can be share within second over the globe.
+Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~TBD]{shiller2015irrational}; \cite[][pp.~TBD]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors .
 The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
-Mao, Counts and Bollen (2015), claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as an sentiment indicator for bitcoin prices.
+\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as an sentiment indicator for stock prices.
 As digitalization is expected to continue in the future, crypotocurrencies will hypothetical get more important.
-Thus, the topic is relevant.
+Thus, the topic is characterized as relevant.
 
 \subsection{Research Question and Goal of the Paper}
+\label{sec:ResearchQandGoal}
 As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount people talk about bitcoin on twitter.
@@
 \subsection{Methodology}
+\label{sec:Methodology}
 To answer the above mentioned research question a scientific approach has been applied.
@@
 The first part contains an introduction into the topic by pointing out the relevance of the topic, the research question, methodology and the scope.
-This is conducted in chapter 1.
+This is conducted in chapter \ref{sec:intro}.
 The second part is characterized as the theory part.
@@
 Furthermore, it contains a short introduction into the Vector Autoregression approach (VAR) and the constrains in context with the paper.
-Chapter XYZ The third part contains the discussion of the results and a conclusion.
+This is conducted in chapters \ref{sec:Background} and \ref{sec:EconometricModellingandResults}.
+The third part contains the discussion of the results and a conclusion.
 The conclusion is based on the theory and the own conducted mathematical computation.
-Those computations are based on a data set, which was gathered by own coded python scripts for the timeperiod ADD TIME PERIOD.
+Those computations are based on a data set, which was gathered by own coded python scripts for the timeperiod December 20th - 27th.
+Based on the short time of observation the results have to be interpreted carefully.
 The data set contains out of two data sources (1) twitter tweets which contain the buzzword "bitcoin" and (2) historical bitcoin prices.
@@
 The output of aggregation was further proceeded with stata to conduct the VAR on a daily basis.
-Chapter 4 and 5
-
-INPUT: IS IT NOW DAILY? WHAT IS THE REASON?
+The third part of the paper is discussed in the chapters \ref{sec:EconometricModellingandResults} and \ref{sec:Conclustion}.
 
 \subsection{Scope}
+\label{sec:Scope}
 The paper's focus lies on the scientific discussion and answer of the research question mentioned above.
-The research question has consciously been design very tiny, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high quality scientifc paper.
+The research question has consciously been design very tiny, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high quality scientific paper.
+As already mentioned above, the results have to be interpreted carefully because of the limited observation time of seven days.
 The approach and technical issues (like code scripts etc.) are not addressed.
 Those points are explained in the separate documentation paper.
-It is not a deep description of the code as the code itself as the code is documented separately.
-Nevertheless, important lines of code are discussed.
-
 \clearpage
@@
 		\section{Brief Background and Data Collection}
+		\label{sec:Background}
 		\itshape\textbf {Bitcoin}\\
@@
 		\section{Econometric Modelling and Results}
+		\label{sec:EconometricModellingandResults}
 		\textnormal {As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
@@
 		\section{Conclusion}
+		\label{sec:Conclustion}
 		\textnormal {(Insert text)}
@@
 %************************** Bibliography **************************
-\printbibliography
+\section{References}
+\printbibliography[heading=none]
 \clearpage
+%************************** Declaration of Authorship **************************
+\section{Declaration of Authorship}
+We hereby declare,
+\begin{itemize}
+    \item that we have written this thesis without any help from others and without the use of documents and aids other than those stated above;
+    \item that we have mentioned all the sources used and that we have cited them correctly according to established academic citation rules;
+    \item that we have acquired any immaterial rights to materials we may have used such as images or graphs, or that we have produced such materials ourself;
+    \item that the topic or parts of it are not already the object of any work or examination of another course unless this has been explicitly agreed on with the faculty member in advance and is referred to in the thesis;
+    \item that we will not pass on copies of this work to third parties or publish them without the University’s written consent if a direct connection can be established with the University of St.Gallen or its faculty members;
+    \item that we are aware that our work can be electronically checked for plagiarism and that we hereby grant the University of St.Gallen copyright in accordance with the Examination Regulations in so far as this is required for administrative action;
+    \item that we are aware that the University will prosecute any infringement of this declaration of authorship and, in particular, the employment of a ghostwriter, and that any such infringement may result in disciplinary and criminal consequences which may result in our expulsion from the University or us being stripped of our degree.
+\end{itemize}
 
+\begin{flushleft}
+................................\\
+Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip 
+................................\\
+Severin Kranz - 13-606-355\\\bigskip\bigskip
+................................\\
+Joël Sonderegger - 11-495-488\\\bigskip\bigskip
+................................\\
+Alen Stepic - 11-475-258\\\bigskip\bigskip
+................................\\
+Chi Xu - XX-XXX-XXX
+
+By submitting this academic term paper, we confirm through my conclusive action that we are submitting the Declaration of Authorship, that we have read and understood it, and that it is true.
+
+\end{flushleft}
+\clearpage
 %************************** DOCUMENT-END **************************

### 2017-12-29 paper/paper.tex
added Ch. 3 Statistical Analysis and worked on the structure and comprehensibilityof the latex file as a whole,

--- 2017-12-29 paper/paper.tex
@@
 
-%************************** DOCUMENT-START **************************
+%************************** DOCUMENT_STARTS_HERE **************************
 \begin{document}
@@
 	\centering
-        \includegraphics[scale=0.35]{logohsg}
+	\includegraphics[scale=0.32]{logohsg}
 	\end{figure}
 \centering
-    {\scshape\large School of Management, Economics, Law, Social Schiences and International Affairs \par}
+{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
 \vspace{2.0cm}
@@
 
-%************************** Abstract Page ************************** 
+%************************** Abstract ************************** 
 \begin{abstract}
@@
 One reflecting twitter activity and the other one showing the bitcoin prices for the same period.
-Based on that an econometric model is used for the statistical analysis and the interpretation of the results.
+Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
 
-INPUT ALEN @DIMI: ADD JUST KEY FINDING THE REST I LIKE
+***INPUT ALEN @DIMI: ADD JUST KEY FINDING THE REST I LIKE***\\
 
@@
 \tableofcontents
+
 \clearpage
+
 %************************** List of Figures ************************** 	
 \listoffigures\bigskip\bigskip
-%************************** List of Figures ************************** 	   
+
 \section*{List of Abbreviation} 
@@
 
-%************************** Chapters 1-4 **************************
+%************************** Chapters 1 - Introduction **************************
 \begin{spacing}{1.2}
@@
 As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount people talk about bitcoin on twitter.
-The goal should be reached by answering the following research question:
-
-In what extend does the amount of twitter tweets influence the price of bitcoin?
+The goal should be reached by answering the following research question: \\
+In what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
 
@@
 Those points are explained in the separate documentation paper.
+
 \clearpage
 
-		\section{Brief Background and Data Collection}
+%************************** Chapters 2 - Background and Data Collection **************************
+\section{Background and Data Collection}
 \label{sec:Background}
-		\itshape\textbf {Bitcoin}\\
-		\textnormal {After the global financial crisis, Satoshi Nakamoto (2008, p.
+\subsection{Bitcoin}
+After the global financial crisis, Satoshi Nakamoto (2008, p.
 1) claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
 Starting from his whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions (blockchain) has been developed (Nakamoto, 2008, p.
-1).\newline
+1).\\
+
 Today, Bitcoin is the most popular of over 1300 so-called cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
@@
 During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Kristoufek, 2015).
-These findings are in line with other researchers (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\newline
+These findings are in line with other researchers (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\
+
 One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices.
@@
 (2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.
- }\\
 
-		\itshape\textbf {Twitter}\\
-		\textnormal {(Text for Twitter) Input Alen: Explain why twitter is the right source and and some facts about it}\\
+\subsection{Twitter}
+Outline: Growth of Social Media, Opinion Mining, Twitter -> micro-blogging platform, tweets, functionalities, etc. ; Why good for measuring opinions ?  "gold mine"; Sentiment Analysis, What we do.
+Comment Severin: This part will contain the following steps and will be mostly based on Stenqvist et al. Predicting Bitcoin price fluctuation with Twitter sentiment analysis  (sections 2.2, 2.3)\\
 
-		\itshape\textbf {Data Collection}\\
-		\textnormal {For our dataset, we used 2 different sources.
+1) Introduction sentence -> growth of social media https://www.statista.com/statistics/278414/number-of-worldwide-social-network-users/\\
+2) Twitter as a "gold mine" to gather opinions -> What is twitter, Why is it valuable -> length of messages etc.\\
+3) Sentiment Analysis -> what is a sentiment analysis\\
+4) Sentiment Analysis of the term bitcoin based on twitter -> explain what we do \\
+
+\subsection{Data Collection}
+For our dataset, we used 2 different sources.\\
 We first collected historical data on bitcoin prices to USD and secondly, we gathered twitter massages related to bitcoin.
 We fulfil this relationship by selecting tweets that contain the term “bitcoin” in the text message.
-The time period for both collected data sets was from 21.12.2017 16:00:00 UTC to 26.12.2017 16:00:00 in an hourly basis.
+The time period for both collected data sets was from 19.12.2017 20:00:00 UTC to 28.12.2017 10:00:00 in an hourly basis.
 We chose an hourly basis to be able to do a statistical analysis with a certain amount of observation for the restricted processing time of this homework.\\
+
 For the bitcoin prices, a publicly available API from CoinDesk was used (Source?
@@
 The prices collected represent the final price level of bitcoin before every hour changes.
-For example, our first listed price of bitcoin was on 21.12.2017 at 16:59:59 and our last value on 26.12.2017 at 15:59:59.
-These values construct our first time series data set and are shown in the following graph.\\}
+For example, our first listed price of bitcoin was on 19.12.2017 at 19:59:59 and our last value on 28.12.2017 at 09:59:59.
+These values construct our first time series data set and are shown in the following graph.\\
+
+	\begin{figure}[H]
+	\graphicspath{ {stata_export_graphs/} }
+	\includegraphics[scale=0.45]{graph_plot_nr_tweets.png}
+	\end{figure}
+
+	\begin{figure}[H]
+	\graphicspath{ {stata_export_graphs/} }
+	\includegraphics[scale=0.45]{graph_plot_df_nr_tweets.png}
+	\end{figure}
+
+	\begin{figure}[H]
+	\graphicspath{ {stata_export_graphs/} }
+	\includegraphics[scale=0.45]{graph_plot_log_df_nr_tweets.png}
+	\end{figure}
+
+	\begin{figure}[H]
+	\graphicspath{ {stata_export_graphs/} }
+	\includegraphics[scale=0.45]{graph_plot_bpi.png}
+	\end{figure}
+
+	\begin{figure}[H]
+	\graphicspath{ {stata_export_graphs/} }
+	\includegraphics[scale=0.45]{graph_plot_df_bpi.png}
+	\end{figure}
+
+	\begin{figure}[H]
+	\graphicspath{ {stata_export_graphs/} }
+	\includegraphics[scale=0.45]{graph_plot_log_df_bpi.png}
+	\end{figure}
 
@@
 
+%************************** Chapters 3 - Econometric Modelling and Results **************************
 \section{Econometric Modelling and Results}
 \label{sec:EconometricModellingandResults}
-		\textnormal {As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
+As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
 From our data collection, we are left with two time series datasets representing two variables.
@@
 4-5).\\
-To generate the econometric results that follow we used the statistical software STATA.}
+To generate the econometric results that follow we used the statistical software STATA.
 
-		\itshape\textbf {Stationarity}\\
-		\textnormal {Before estimating a VAR model, the time series data must be checked for stationary.
-Thus, the means and variances are constant over time and the datasets do not show any trending behavior.
+\subsection{Stationarity}
+Before estimating a VAR model, the time series data must be checked for stationary.
+Thus, the means and variances are constant over time and the dataset do not show any trending behavior.
 Non-stationary data can lead to an inaccurate model which is undesirable.
-To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test and get following results from STATA.\\
-Interpreting the results and accepting or rejecting stationarity.}
+To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test.\\
+First, we check for stationarity of the number of tweets (variable name in data set: nr\_of\_tweets).
+Because there this variable may not be stationary we have also vreated the first difference of the number of tweets (variable name: df\_nr\_of\_tweets) and the logarithmic first difference of the number of tweets (variable name: log\_df\_nr\_of\_tweets).
+The augmented Dickey-Fuller test for these variables gives the following results (via STATA):\\
 
-		\itshape\textbf {Lag Specification}\\
-		\textnormal {To select the optimal number of lags in our VAR regression we check for various information criteria.
+\begin{figure}[H]
+\centering
+\graphicspath{ {stata_export_graphs/} }
+\includegraphics[scale=0.85]{ADF_twitter_variables.png}
+\end{figure}
+
+From these result we can see that only the first variable in not stationary.
+This is because the absolute value of the test statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475).
+The second variable is stationary (14.167 $>$ 3.475) and from here onwards we are going to continuous the analysis by using this first difference transformetion of the variable number of tweets, which fulfils stationarity.\\
+
+Secondly, we have to check for stationarity for our second variable, the bitcoin prices (variable name in data set: bpi\_closing\_price).
+Here we also included the first difference (variable name: df\_bpi\_closing\_price) and the logarithmic first difference (variable name: log\_df\_bpi\_closing\_price) transformations.
+The ADF test for these variables gives the following results:\\
+
+\begin{figure}[H]
+\centering
+\graphicspath{ {stata_export_graphs/} }
+\includegraphics[scale=0.85]{ADF_bpi_variables.png}
+\end{figure}
+
+These result also suggest to use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
+
+\subsection{Lag-Specification}
+To select the optimal number of lags in our VAR regression we check for various information criteria.
 Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (Brandt and Williams, 2007, p.
 27).
-The calculations of these criteria for our given data set is easily done by a statistical software and given in the following table.\\}
+The calculations of these criteria for our given data set are shown in the following table.\\
 
-		\itshape\textbf {VAR Regression Model}\\
-		\textnormal {In this paper, we use a basic unrestricted VAR model which consists of two endogenous variables, T for aggregate tweets and B for bitcoin prices.
-The selected time lag is 3 and this choice will be discussed later.
-Given that the model equations can be written as follows:\\}
+\begin{figure}[H]
+\centering
+\graphicspath{ {stata_export_graphs/} }
+\includegraphics[scale=0.85]{LAG_crit_df_nr_tweets_df_bpi.png}
+\end{figure}
 
-		\itshape\textbf {Granger Causality}\\
-		\textnormal {To assess the causal relationship between our two endogenous variables and interpret the result we use the Granger causality.
-This test confirms if one variable is statistically useful to predict the other variable.
-If this is given the dynamics stated by the calculated coefficient above can be assumed to be valuable.\\
-A second analysis to interpret our results is the impact response analysis.
-This evaluates the impact of changes in the one variable to the other variable.
-This is also provided by STATA and the results can be seen in the following graphs.}
+As can be seen on the table, STATA calculates and presents various information criteria (AIC, HQIC, SBIC).
+The asterisk indicates the optimal lag lenght to use for the regression analysis.
+In this case all criteria suggest a lag lenght of 1.
 
-		\itshape\textbf {Impulse Response Analysis}\\
+\subsection{Regression Model}
+After determining the optimal lag gength the next step is to build the vector autoregression model (VAR model).
+For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T which repesents the variable df\_nr\_of\_tweets and B which represents bpi\_closing\_price.
+As defined in the previous section the selected otpimal time lag is 1.
+Given these information, the model equations can be written as follows:
+
+\begin{equation}
+\begin{split}
+T_t = c_1 + a_{11}T_{t-1} + a_{12}B_{t-1} + \epsilon_1 \\
+B_t = c_2 + a_{21}T_{t-1} + a_{22}B_{t-1} + \epsilon_2
+\end{split}
+\end{equation}
+
+This model shows that the current value of our endogenous variavles is determined by its own past values, the past values of the other variable and an error term.
+In our research approach we ask the question, if the amount of tweets mentioning bitcoin in the past, has an effect on the bitcoin prices in the periods that follow.
+This question is pictured in the second equation of this model.\\
+
+After running the above VAR regression in STATA we get following results:
+
+\begin{tabular}{lcc} \hline
+ & (T\textsubscript{t}) & (B\textsubscript{t}) \\
+VARIABLES & df\_nr\_of\_tweets & df\_bpi\_closing\_price \\ \hline
+ &  &  \\
+L.df\_nr\_of\_tweets (T\textsubscript{t-1}) & 0.00999 (a\textsubscript{11}) & 0.00463 (a\textsubscript{21}) \\
+ & (0.0693) & (0.0104) \\
+L.df\_bpi\_closing\_price (B\textsubscript{t-1}) & -0.675 (a\textsubscript{12}) & -0.125* (a\textsubscript{22}) \\
+ & (0.469) & (0.0707) \\
+Constant  & -88.34 (c\textsubscript{1}) & -18.48 (c\textsubscript{2}) \\
+ & (177.9) & (26.79) \\
+ &  &  \\
+ Observations & 205 & 205 \\ \hline
+\multicolumn{3}{c}{ Standard errors in parentheses} \\
+\multicolumn{3}{c}{ *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
+\end{tabular}
+
+The equation of our VAR model are displayed vertically in this table.
+As said before the relevant equation in the model is the second one and it is listed on the second column (B\textsubscript{t}) in the above table.
+The coefficient of 0.00463 (a\textsubscript{21}) implies that an increase of tweets by 1 increases the bitcoin price by 0.005 \$.
+This effect is very small and statistically insignificant (p value $>$ 0.1).
+This means that based on our data set the amount of tweets have no significant effect on the price development of bitcoin.
+
+\subsection{Granger Causality}
+To assess the reliability (causality) of the previous results we use the Granger causality test.
+This test confirms if the statements by the regression are valid.
+The following table shows the results of the Granger causality test\\
+
+\begin{figure}[H]
+\centering
+\graphicspath{ {stata_export_graphs/} }
+\includegraphics[scale=0.85]{granger_test.png}
+\end{figure}
+
+The Null hypothesis here is... In the second row the chi2 is greater then the Prob value which allows as to reject the Null hypothesis and conclude that the regression results are valid...\\
+
+...the Null hypothesis in our case is that lagged number of Tweets does not cause changes in bitcoin prices.
+As the Table shows, we can reject the Null hypothesis because the probability is around 1\%.
+Therefore, we accept the alternative hypothesis, which says that the lagged number of tweets does cause changes in bitcoin prices.
+How these changes look exactly we have discussed in the previous section.
+The granger causality confirmed that the effect is valid.
 
@@
 
+%************************** Chapters 4 - Conclusion **************************
 \section{Conclusion}
 \label{sec:Conclustion}
-		\textnormal {(Insert text)}
+(Insert text)
 
@@
 \printbibliography[heading=none]
+
 \clearpage
+
 %************************** Declaration of Authorship **************************
@@
 By submitting this academic term paper, we confirm through my conclusive action that we are submitting the Declaration of Authorship, that we have read and understood it, and that it is true.
+\end{flushleft}
 
-\end{flushleft}
 \clearpage
-%************************** DOCUMENT-END **************************
+
 \end{document}
+%************************** DOCUMENT_ENDS_HERE **************************

### 2017-12-29 aggregateTwitterBpi.py
changed df var names

@@ -22,53 +22,56 @@ def load_tweets():
 
 # Gets bpi data from CSV-File. Returns a data frame with bpi data.
 def load_bpi():
-    bpi_data = pd.read_csv('data/bpi.csv')
+    df_bpi = pd.read_csv('data/bpi.csv')
 
     # drop not needed columns
-    bpi_data.drop('average', axis=1, inplace=True)
-    bpi_data.drop('high', axis=1, inplace=True)
-    bpi_data.drop('low', axis=1, inplace=True)
+    df_bpi.drop('average', axis=1, inplace=True)
+    df_bpi.drop('high', axis=1, inplace=True)
+    df_bpi.drop('low', axis=1, inplace=True)
 
     # create new column 'close'. The close price is the open price of the previous hour (thus, shifting the open price -1 to get the close price)
-    bpi_data['close'] = bpi_data['open']
-    bpi_data['close'] = bpi_data['close'].shift(-1)
+    df_bpi['close'] = df_bpi['open']
+    df_bpi['close'] = df_bpi['close'].shift(-1)
+
+    # drop no more needed open column
+    df_bpi.drop('open', axis=1, inplace=True)
     
     # Set time as DataFrame index.
-    times = bpi_data.set_index(pd.DatetimeIndex(bpi_data['time']))
-    bpi_data = bpi_data.set_index([times.index.year, times.index.month, times.index.day, times.index.hour])
+    times = df_bpi.set_index(pd.DatetimeIndex(df_bpi['time']))
+    df_bpi = df_bpi.set_index([times.index.year, times.index.month, times.index.day, times.index.hour])
  
     # set correct index names for Y, M, D, H
-    bpi_data.index = bpi_data.index.set_names('Y', level=0)
-    bpi_data.index = bpi_data.index.set_names('M', level=1)
-    bpi_data.index = bpi_data.index.set_names('D', level=2)
-    bpi_data.index = bpi_data.index.set_names('H', level=3)
+    df_bpi.index = df_bpi.index.set_names('Y', level=0)
+    df_bpi.index = df_bpi.index.set_names('M', level=1)
+    df_bpi.index = df_bpi.index.set_names('D', level=2)
+    df_bpi.index = df_bpi.index.set_names('H', level=3)
 
-    return bpi_data
+    return df_bpi
 
 # Enriches BPI data frame with first difference and log first difference
 def first_difference_bpi(bpi_df):
 
-    # assigning the variable here to check later if there is a 'previous' btc close price.
[…]

### 2017-12-29 documentation/documentation.tex
stucturing the title page

@@
 
-%% Language and font encodings
+% Language and font encodings
 \usepackage[utf8]{inputenc}
@@
 \DeclareLanguageMapping{american}{american-apa}
-
 \addbibresource{references.bib}
 
-%% Sets page size and margins
+% Sets page size and margins
 \usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
@@
 
-%% package for formatting and highlighting source code
+% package for formatting and highlighting source code
 \usepackage{listings}
@@
 
-%% Useful packages
+% Useful packages
 \usepackage{amsmath}
@@
 
-%% packages for tikz diagrams
+% packages for tikz diagrams
 \usepackage{tikz}
@@
 
-%% styling for tikz diagrams
+% styling for tikz diagrams
 \tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
@@
 {0pt}{1.4ex}{0pt}
-
 \definecolor{dkgreen}{rgb}{0,0.6,0}
@@
   breakatwhitespace=true,
-  tabsize=3
-}
+  tabsize=3}
 
-\title{Review of Assigned Readings}
+\title{Your Title Goes Here}
 \author{Your Name Goes Here}
 
+%************************** DOCUMENT_STARTS_HERE **************************
 \begin{document}
+
 \begin{titlepage}
@@
 	\centering
-        \includegraphics[scale=0.35]{logohsg}
+	\includegraphics[scale=0.32]{logohsg}
 	\end{figure}
 \centering
-        School of Management, Economics, Law, Social Schiences and International Affairs \par
-        \vspace{2.5cm}
-        {\huge\bfseries The effect of Twitter activity on
-Bitcoin price\par}      
+\centering
+{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
+\vspace{1.7cm}
+{\huge\bfseries The effect of Twitter activity on \\ Bitcoin price\par}
+\vspace{1.0cm}
 {\Huge\itshape Documentation\par}
-        \vspace{1.5cm}     
-        {Software Engineering for Economists \\ (7,610,1.00) \par}
-        \vspace{1.3cm}
-        {Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\
-       	Alen Stepic - 11-475-258 \\Chi Xu - XX-XXX-XXX \par}
-        \vspace{1cm}
-        Fall Term 2017
-        \vfill
-        Supervisor
-        \linebreak
-        Prof. Dr. Philipp \textsc{Zahn}
-        \linebreak
-        Department of Economics
-
-    % Bottom of the page
-     {\centering \today\par}
-
+\vspace{1.0cm}     
+{\Large Software Engineering for Economists \\ (7,610,1.00) \par}
+\vspace{1.2cm}
+{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - XX-XXX-XXX \par}
+\vspace{1.2cm}
+Fall Term 2017 \\
+\vspace{1.2cm}
+{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
+\vspace{0.8cm}
+{\centering\today\par}
 \end{titlepage}
@@
 \clearpage
+
 \tableofcontents
@@
 %************************** Bibliography **************************
-\printbibliography
+\section{References}
+\printbibliography[heading=none]
 \clearpage

### 2017-12-29 documentation/documentation.tex
worked a bit on the structure of the file not on content

@@
 \end{acronym}
+
 \clearpage
@@
 \cleardoublepage\pagenumbering{arabic}
+
 \section{Introduction}
@@
 Nevertheless, important lines of code are discussed.
+
 \clearpage
@@
 \end{lstlisting}
-You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
-\newline
+You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.\\
 On top you need various packages.
@@
 To reproduce our results, you need to have the STATA software installed in your local computer and after starting the program you can follow the guidelines in chapter 4 (data analysis).
+
+\clearpage
 
@@
 
-After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.
+After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.\\
 \begin{figure}[H]
@@
 \end{itemize}
+
 The timestamps are in UTC time.
@@
 Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server.
-The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline
+The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\\
 
 \begin{enumerate}
+
 \item Setup of the Raspberry Pi
@@
 \end{enumerate}
+
 In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.
@@
 The following requests delivers data for an per hour monthly sliding window.
+
 \paragraph{Request}\mbox{}\\
@@
 \end{lstlisting}
+
 \paragraph{Response}
@@
 \end{lstlisting}
+
+\clearpage
 
@@
 \end{itemize}
+
+\clearpage
 

### 2017-12-29 documentation/documentation.tex
commiting the content of stata_analysis

@@
 \section{Data Analysis}
-The data analysis was performed with the statistical software STATA.
-The corresponding stata file and .do file are stored in the folder statistical\_analysis\_stata.
+The data analysis was performed with the statistical software STATA (version 14.2).
+The corresponding stata file and .do file are stored in the folder stata\_analysis.
 Following we describe all the commands used to produce our econometric model.

### 2017-12-29 documentation/documentation.tex
improved the section 5 data analysis in documentation

@@
 
-\smallskip Step 1:\\
-After starting data the first step was to import the data file (.csv file) into stata. We did so by following command (be carefull your location of the .csv file may differ):\\
+Step 1:\\
+After starting stata the first step was to import the data file (.csv file) into stata. We did so by following command (be carefull your location of the .csv file will differ):\\
 \begin{lstlisting}[language=bash]
-    import delimited "your_location.csv"
+    import delimited C:\Users\Dimi\Desktop\nr_of_tweets_bpi_closing_price.csv
 \end{lstlisting}
 
-\smallskip Step 2:\\
-STATA is not recognizing our variable "time" as a date variable and therefore we create a new variable "time2" and giving it the same values as "time" and giving it the same format as "time" has.
+Step 2:\\
+STATA is not recognizing our variable "time" as a date variable.
+Therefore we create a new variable "time2" and giving it the same values as "time" in the same format as "time".
 At the end we define "time2" to be a time series with an hourly progress\\
@@
 
-\smallskip Step 3:\\
-Checking for stationarity for all variables by using the Augmented Dickey-Fuller (ADF) test with a time delay of 0 periods (lag 0).\\
+Step 3:\\
+Next we plotted all variables by the following commands and exported the produced graphs (and saved in local repository):\\
+	\begin{lstlisting}[language=bash]
+	twoway (tsline nr_of_tweets)
+	twoway (tsline df_nr_of_tweets)
+	twoway (tsline log_df_nr_of_tweets)
+	twoway (tsline bpi_closing_price)
+	twoway (tsline df_bpi_closing_price)
+	twoway (tsline log_df_bpi_closing_price)
+	\end{lstlisting}
+
+Step 4:\\
+To check for stationarity we run the Augmented Dickey-Fuller (ADF) test for all variables with a time delay of 0 periods (lag 0).\\
 	\begin{lstlisting}[language=bash]
@@
 
-\smallskip Step 4:\\
+Step 5:\\
 Calling the lag-order selection criteria statistics for our VAR model.
-The maximum amount of lags is 7 and the variables that we chose for the latter VAR model are df\_nr\_of\_tweets and df\_btc\_closing\_price.\\
+The maximum amount of lags is 7 and the variables that we chose for the later VAR model are df\_nr\_of\_tweets and df\_bpi\_closing\_price.\\
 	\begin{lstlisting}[language=bash]
-	varsoc df_nr_of_tweets df_btc_closing_price, maxlag(7)
+	varsoc df_nr_of_tweets df_bpi_closing_price, maxlag(7)
 	\end{lstlisting}
 
-\smallskip Step 5:\\
-Running the VAR regression for our two variables and recommended lag of 2 (from Results of Step 4).\\
+Step 6:\\
+Running the VAR regression for our two variables. With recommended lag of 1 (from Step 4).\\
 	\begin{lstlisting}[language=bash]
-	var df_nr_of_tweets df_btc_closing_price, lags(1/2)
+	var df_nr_of_tweets df_bpi_closing_price, lags(1/1)
 	\end{lstlisting}
 
-\smallskip Step 6:\\
-Calling the granger causality test with lag length 2.\\
+Step 7:\\
+Calling the granger causality test with lag length 1.\\
 	\begin{lstlisting}[language=bash]
@@
 
-\smallskip Additionally:\\
-The Regression Results were exportet to a latex format by instaling and using the outreg2 package.
-This piece of latex code was then inserted into in the paper.
-All other results we edited with an image software and inserted them as .png file into the paper\\
+Additionally:\\
+The VAR regression results were exportet to a latex format by instaling and using the outreg2 package.
+The generated piece of latex code was then inserted into in the latex file of the paper.
+All other results were exported with an image software and used as .png files in latex\\
 	\begin{lstlisting}[language=bash]
@@
 We hereby declare,
+
 \begin{itemize}

### 2017-12-29 documentation/documentation.tex
corrected setup and tweets collection part. Puls, finished draw version of aggregation process

--- 2017-12-29 documentation/documentation.tex
@@
 
-% Language and font encodings
+%% Language and font encodings
 \usepackage[utf8]{inputenc}
@@
 \DeclareLanguageMapping{american}{american-apa}
+
 \addbibresource{references.bib}
 
-% Sets page size and margins
+%% Sets page size and margins
 \usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
@@
 
-% package for formatting and highlighting source code
+%% package for formatting and highlighting source code
 \usepackage{listings}
@@
 
-% Useful packages
+%% Useful packages
 \usepackage{amsmath}
@@
 
-% packages for tikz diagrams
+%% packages for tikz diagrams
 \usepackage{tikz}
@@
 
-% styling for tikz diagrams
+%% styling for tikz diagrams
 \tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
@@
 {0pt}{1.4ex}{0pt}
+
 \definecolor{dkgreen}{rgb}{0,0.6,0}
@@
   breakatwhitespace=true,
-  tabsize=3}
+  tabsize=3
+}
 
-\title{Your Title Goes Here}
+\title{Review of Assigned Readings}
 \author{Your Name Goes Here}
 
-%************************** DOCUMENT_STARTS_HERE **************************
     \begin{document}
-
     \begin{titlepage}
@@
       	\centering
-	\includegraphics[scale=0.32]{logohsg}
+        \includegraphics[scale=0.35]{logohsg}
         \end{figure}
         \centering
-\centering
-{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
-\vspace{1.7cm}
-{\huge\bfseries The effect of Twitter activity on \\ Bitcoin price\par}
-\vspace{1.0cm}
+        School of Management, Economics, Law, Social Schiences and International Affairs \par
+        \vspace{2.5cm}
+        {\huge\bfseries The effect of Twitter activity on
+Bitcoin price\par}      
         {\Huge\itshape Documentation\par}
-\vspace{1.0cm}     
-{\Large Software Engineering for Economists \\ (7,610,1.00) \par}
-\vspace{1.2cm}
-{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - XX-XXX-XXX \par}
-\vspace{1.2cm}
-Fall Term 2017 \\
-\vspace{1.2cm}
-{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
-\vspace{0.8cm}
-{\centering\today\par}
+        \vspace{1.5cm}     
+        {Software Engineering for Economists \\ (7,610,1.00) \par}
+        \vspace{1.3cm}
+        {Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\
+       	Alen Stepic - 11-475-258 \\Chi Xu - XX-XXX-XXX \par}
+        \vspace{1cm}
+        Fall Term 2017
+        \vfill
+        Supervisor
+        \linebreak
+        Prof. Dr. Philipp \textsc{Zahn}
+        \linebreak
+        Department of Economics
+
+    % Bottom of the page
+     {\centering \today\par}
+
     \end{titlepage}
@@
     \clearpage
-
     \tableofcontents
@@
 	\end{acronym}
-
     \clearpage
@@
 \cleardoublepage\pagenumbering{arabic}
-
 \section{Introduction}
@@
 The usage of algorithms can increase effectiveness and efficiency.
-Hence, much lager data sets can be proceeded.
-However this creates also new problems regarding to traceability and reproducibility.
+Hence, much larger data sets can be proceeded.
+However, this creates also new challenges regarding traceability and reproducibility.
 Often cited academic paper exist, where the initial computation is not reproducible \parencite[pp.~874--887]{mccullough2003}.
 Replicating data or existing results do not provide any new knowledge at all.
-Nevertheless, the ability to reproduce is key in science and non-reproducable work can not be characterized as science or used as a basis for policy making \parencite[p.~888]{mccullough2003}.
+Nevertheless, the ability to reproduce is key in science, and non-reproducible work can not be characterized as science or used as a basis for policy-making \parencite[p.~888]{mccullough2003}.
 This explains why reproduction is of great relevance.
@@
 The goal of this documentation is the provision of a description.
-This description should enable the reader to reproduce the results discussed in the separate paper.
+This description should enable the reader to reproduce the results discussed in the separate (Comment Joel: suggesting-> accompanying paper ) paper.
 Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed.
@@
 This documentation consists out of four chapters.
-The first chapter contains a short introduction and provides the reader with an overview about the topic.
-Furthermore it points out the relevance of documentation.
+The first chapter contains a short introduction and provides the reader with an overview of the topic.
+Furthermore, it points out the relevance of documentation.
 The second chapter discusses the input data.
@@
 The third chapter discusses how the data is aggregated by pointing out the core model and its parameters.
-Finally the fifth chapter discusses how the analysis has been conducted.
+Finally, the fifth chapter explains how the analysis has been conducted.
 
 \subsection{Scope}
-The scope of the documentation is the provision of an overview about the different steps which have been conducted to obtain the results in the paper.
-It does not contain any discussions about the results of the separate paper.
+The scope of the documentation is the provision of an overview of the different steps which have been conducted to obtain the results in the paper.
+It does not contain any discussions about the results of the separate paper (Comment Joel: suggesting-> accompanying paper ).
 It is not a deep description of the code as the code itself as the code is documented separately.
 Nevertheless, important lines of code are discussed.
-
 \clearpage
@@
 \section{Setup}
+This section goes through the setup that you need for exectuing the code that is discussed in this documentation.
+\subsection{Github Repository}
+All code is available on the following github repository:
+\newline
+\verb|https://github.com/joelsonderegger/twitterbitcoin/|
 \subsection{Requirements to run Python scripts}
-Before you go any further, make sure that at least Python version 3.0.0 available from your command line. You can check this by running:
+Before you go any further, make sure that at least Python version 3.0.0 is available from your command line. You can check this by running in your command line:
 \begin{lstlisting}[language=bash]
@@
 \end{lstlisting}
-You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.\\
-On top you need various packages.
-We created a the requirements file \verb|requirements.txt|, which contains all required packages to run Python scripts of the project.
-The list of packages to be installed using pip install like so:
+You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
+\newline \newline
+On top you need various Python packages.
+We created a  requirements file \verb|requirements.txt|, which contains all required packages to run the Python scripts of this project.
+You can find the  \verb|requirements.txt| in the root directory of our github repository.
+The list of packages can be installed using pip install like so:
 \begin{lstlisting}[language=bash]
@@
 \section{Data Collection}
-This section contains a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
+This section contains a detailed description of how the data for the sequential analysis is gathered and stored.
+Two separate data sets will be collected: (1) Tweets data and  (2) Bitcoin price index data.
 \subsection{Tweets Data}
-Whit the python script real-time twitter data are streamed and stored. This happens with help of a raspberry pi.
+Whit the Python script real-time Twitter data are streamed and stored. This happens with help of a Raspberry Pi.
 \subsubsection{Python Script}
@@
 However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}.
-On the other hand, python offers different twitter libraries.
+On the other hand, Python offers different twitter libraries.
 Such as the open-source package tweepy.
 This package has been used for streaming the twitter data as it simplify the script.
+
+(Comment Joel: I think we need a short paragraph about tweepy here. What is tweepy?)
 
@@
 
-After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.\\
+After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.
 \begin{figure}[H]
@@
 
-\paragraph{Twitter Streaming API}\mbox{}\\{}
-By running the python script \verb|collectTwitterData.py| real-time twitter data is pushed in a Java Script Object Notation (JSON) format.
-Tweets are just pushed in case a tweet contains the defined key word \verb|bitcoin|.
+\paragraph{Running the Python Scrupt}\mbox{}\\{}
+By running the Python script \verb|collectTwitterData.py| real-time twitter data is gathered on an ongoing basis until you stop the script forcefully.
 \begin{lstlisting}[language=bash]
@@
 
-From the JSON format the following parameters are decoded:
+The Tweepy API provides the tweets data in a Java Script Object Notation (JSON) format.
+Tweets are only received in case a tweet contains the predefined key word \verb|bitcoin|.
+While a single tweet consists of many attributes we are only interested in two attributes:
 \begin{itemize}
-\item created at: Timestamp of the created tweet
+    \item created\_at: Timestamp of the created tweet (in UTC time)
     \item text: Text of the tweet
@@
 
-The timestamps are in UTC time.
-
-After a successfully decoding the parameters the data is appended to the \verb|twitterData.csv| file in a new row and saved in the folder \verb|/data|.
-
-An excerpt of an example response looks like the following:
+An example for a response from the Tweepy API looks like this (of course this shows only the two attributes we are interested in):
 \begin{lstlisting}
-[
-    {
-        "created_at": Tue Dec 19 20:40:48 +0000 2017, 
-        "text": "RT @WhiteBitcoin: New Bitcoin White. Effective, Flexible, Reliable", 
-    }, 
-    {
-        "created_at": Tue Dec 19 20:40:49 +0000 2017 ,
-        "text": "As #bitcoin prices surge, #xrp remains affordable and FAST!",
-    }, 
     {
@@
     }
-]
 \end{lstlisting}
 
-Furthermore to ensure a high quality data set an exception has been integrated into the \verb|collectTwitterData.py| script.
+The \verb|text| attribute needs to be encoded from the raw JSON format into the UTF-8 format for further analysis.
+After successfully encoding the \verb|text| attribute a tweet is appended to the \verb|twitterData.csv| file as a new row and saved in the fo
+
+Furthermore, to ensure a high quality data set it needs to be complete without missing any data points for the observed period.
+Thus, we have built in an exception handler into the \verb|collectTwitterData.py| script.
 If an error occurs an email will be sent with the error message.
-Furthermore the logfile will be  appended to \verb|/data/tweet_collection_error_log.csv|.
+Additionaly, any exception that occurs during the exectuing of the script will be added to the log file \verb|/data/tweet_collection_error_log.csv|.
 
@@
 Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server.
-The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\\
+The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline
 
 \begin{enumerate}
-
 \item Setup of the Raspberry Pi
@@
 \end{enumerate}
-
 In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.
@@
 The following requests delivers data for an per hour monthly sliding window.
-
 \paragraph{Request}\mbox{}\\
@@
 \end{lstlisting}
-
 \paragraph{Response}
@@
 \end{lstlisting}
-
-\clearpage
 
@@
 Here a short description of what happens at the various steps: 
-\linebreak\linebreak
-\textbf{Load BPI data set} The script takes the BPI data set that is located at \verb|data/bpi.csv|.
-\linebreak\linebreak
-\textbf{Calculate first differences for BPI data} The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated.
+\paragraph{Load BPI data set}\mbox{}\\
+The script takes the BPI data set that is located at \verb|data/bpi.csv|.
+
+\paragraph{Calculate first differences for BPI data}\mbox{}\\
+The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated.
 The reason for calculating these values is given in the data analysis section.
-\linebreak\linebreak
-\textbf{Load tweets data set} The script takes the tweets data set that is located at \verb|data/twitterData.csv|.
-\linebreak\linebreak
-\textbf{Count number of tweets on an hourly basis} First, groups the tweets by hour. Second, counts the number of tweets for every hour.
-\linebreak\linebreak
-\textbf{Calculate first differences for number of tweets on an hourly basis} The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated.
+
+\paragraph{Load tweets data set}\mbox{}\\ 
+The script takes the tweets data set that is located at \verb|data/twitterData.csv|.
+
+\paragraph{Count number of tweets on an hourly basis}\mbox{}\\ F
+irst, groups the tweets by hour. Second, counts the number of tweets for every hour.
+
+\paragraph{Calculate first differences for number of tweets on an hourly basis}\mbox{}\\ 
+The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated.
 Again, the reason for calculating these values is given in the data analysis section.
-\linebreak\linebreak
-\textbf{Merge number of tweets with BPI data (incl. first differences)} 
-Insert Image
-\linebreak\linebreak
-\textbf{Generate and save CSV file} Finally, a CSV file is generated with the merged data.
+
+\paragraph{Merge number of tweets with BPI data (incl. first differences)}\mbox{}\\
+Up to this point there are the two seperate data frames df\_tweets\_per\_hour and df\_bpi.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.52]{dfseperate.png}
+\end{figure}
+By using the \verb|pandas.DataFrame.join| function the columns of the  \verb|df_tweets_per_hour| are joined with  \verb|df_bpi| on the  \verb|MultiIndex(Y, M, D, H)|.
+The code snipped looks as following\:
+\begin{lstlisting}[language=bash]
+...
+df_merged = df_tweets_per_hour.join(df_bpi, how='left')
+...
+\end{lstlisting}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.52]{dfmerged.png}
+\end{figure}
+
+\paragraph{Generate and save CSV file}\mbox{}\\ Finally, a CSV file is generated with the merged data.
 
@@
 \end{itemize}
-
-\clearpage
 

### 2017-12-30 documentation/documentation.tex
edited raspberry setup part. puls sovled some merge issues

@@
 It is not a deep description of the code as the code itself as the code is documented separately.
-Nevertheless, important lines of code are discussed.
+Nevertheless,
 \clearpage
@@
 \end{lstlisting}
+
 You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
@@
 The list of packages can be installed using pip install like so:
+
 \begin{lstlisting}[language=bash]
@@
         "created_at": Tue Dec 19 20:40:49 +0000 2017, 
-        "text": "Singapore issues bitcoin warning after price rise - #BTC #Bitcoin #Crypto", 
+        "text": "Singapore issues bitcoin warning after price rise - #BTC #Bitcoin #Crypto"
     }
@@
 \subsubsection{Hardware Setup}
-As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword \"bitcoin\".
-The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
+As explained in the previous section the Tweepy API was used to gather tweets in real-time based on the buzzword "bitcoin".
+The Python script was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
 This approach allowed us to ensure a continuous data stream while being able to access the program output regardless of time and location.
-Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server.
-The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline
+Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient option compared to a personal computer or NAS Server.
+The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\\
 
 \begin{enumerate}
+
 \item Setup of the Raspberry Pi
@@
 \begin{enumerate}
-\item Install FileZilla available from
+\item Install FileZilla on your local machine available from
 \begin{lstlisting}[language=bash] 
@@
 \end{lstlisting}
-\item Connect to rpi and navigate to data location \newline
+\item Connect to RPI and navigate to data location \newline
 \item Download data manually \newline \newline \end{enumerate}
 \end{enumerate}
+
 In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.
@@
 
-\paragraph{Generate and save CSV file}\mbox{}\\ Finally, a CSV file is generated with the merged data.
-
 \subsection{Execution}
@@
 
+\clearpage
+
 \section{Data Analysis}
-The data analysis was performed with the statistical software STATA.
-The corresponding stata file and .do file are stored in the folder statistical\_analysis\_stata.
+The data analysis was performed with the statistical software STATA (version 14.2).
+The corresponding stata file and .do file are stored in the folder stata\_analysis.
 Following we describe all the commands used to produce our econometric model.
 
-\smallskip Step 1:\\
-After starting data the first step was to import the data file (.csv file) into stata. We did so by following command (be carefull your location of the .csv file may differ):\\
+Step 1:\\
+After starting stata the first step was to import the data file (.csv file) into stata. We did so by following command (be carefull your location of the .csv file will differ):\\
 \begin{lstlisting}[language=bash]
-    import delimited "your_location.csv"
+    import delimited C:\Users\Dimi\Desktop\nr_of_tweets_bpi_closing_price.csv
 \end{lstlisting}
 
-\smallskip Step 2:\\
-STATA is not recognizing our variable "time" as a date variable and therefore we create a new variable "time2" and giving it the same values as "time" and giving it the same format as "time" has.
+Step 2:\\
+STATA is not recognizing our variable "time" as a date variable.
+Therefore we create a new variable "time2" and giving it the same values as "time" in the same format as "time".
 At the end we define "time2" to be a time series with an hourly progress\\

### 2017-12-30 paper/paper.tex

@@
 The digitalisation leads to an increased network effect, where information can be share within second over the globe.
-Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~TBD]{shiller2015irrational}; \cite[][pp.~TBD]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors .
+Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors .
 The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.

### 2017-12-31 documentation/documentation.tex
declaration of authorship (name sorting), input integration, adding some infos to methodology, correcting different typing errors

@@
 The goal of this documentation is the provision of a description.
-This description should enable the reader to reproduce the results discussed in the separate (Comment Joel: suggesting-> accompanying paper ) paper.
+This description should enable the reader to reproduce the results discussed in the accompanying paper.
 Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed.
@@
 \subsection{Methodology}
-This documentation consists out of four chapters.
+This documentation consists out of seven chapters.
+The first five chapters are going to be discussed, as they are relevant for the reproduction of the results.
 The first chapter contains a short introduction and provides the reader with an overview of the topic.
-Furthermore, it points out the relevance of documentation.
-The second chapter discusses the input data.
+Furthermore, it points out the relevance of the documentation.
+In the second chapter the requirements (setup) is discussed to enable the reproducibility and run the own written code scripts in Python.
+Python has been used as it was suggested in the course Software Engineering for Economists.
+The third chapter discusses the input data.
 This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data.
-The third chapter discusses how the data is aggregated by pointing out the core model and its parameters.
-Finally, the fifth chapter explains how the analysis has been conducted.
+The data have been gathered by using Application Programming Interfaces (API)to ensure high quality of the data.
+The fourth chapter discusses how the data is aggregated wrangled to enable the subsequent analysis.
+The fifth chapter explains how the analysis has been conducted whit STATA.
 
@@
 The scope of the documentation is the provision of an overview of the different steps which have been conducted to obtain the results in the paper.
-It does not contain any discussions about the results of the separate paper (Comment Joel: suggesting-> accompanying paper ).
+It does not contain any discussions about the results of the accompanying paper.
 It is not a deep description of the code as the code itself as the code is documented separately.
-Nevertheless,
 \clearpage
@@
 \subsubsection{Python Script}
-Twitter offers different Application Programming Interfaces (API) for collecting data.
+Twitter offers different API for collecting data.
 However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}.
@@
 Such as the open-source package tweepy.
-This package has been used for streaming the twitter data as it simplify the script.
+This package has been used for streaming the twitter data as it simplify the script and enables to gather a broader number of tweets for free.
 
-(Comment Joel: I think we need a short paragraph about tweepy here. What is tweepy?)
+Tweepy is
+TBD
+TBD
+TBD
 
@@
 
-\paragraph{Running the Python Scrupt}\mbox{}\\{}
+\paragraph{Running the Python Script}\mbox{}\\{}
 By running the Python script \verb|collectTwitterData.py| real-time twitter data is gathered on an ongoing basis until you stop the script forcefully.
@@
     \item that the topic or parts of it are not already the object of any work or examination of another course unless this has been explicitly agreed on with the faculty member in advance and is referred to in the thesis;
-    \item that we will not pass on copies of this work to third parties or publish them without the University’s written consent if a direct connection can be established with the University of St.Gallen or its faculty members;
     \item that we are aware that our work can be electronically checked for plagiarism and that we hereby grant the University of St.Gallen copyright in accordance with the Examination Regulations in so far as this is required for administrative action;
@@
 ................................\\
+Alen Stepic - 11-475-258\\\bigskip\bigskip  
+................................\\
 Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip
@@
 Joël Sonderegger - 11-495-488\\\bigskip\bigskip
-................................\\
-Alen Stepic - 11-475-258\\\bigskip\bigskip
 ................................\\

### 2017-12-31 documentation/documentation.tex
correcting some typers

@@
 Furthermore, it points out the relevance of the documentation.
-In the second chapter the requirements (setup) is discussed to enable the reproducibility and run the own written code scripts in Python.
+In the second chapter the requirements (setup) are discussed to enable the reproducibility and run the own written code scripts in Python.
 Python has been used as it was suggested in the course Software Engineering for Economists.
@@
 This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data.
-The data have been gathered by using Application Programming Interfaces (API)to ensure high quality of the data.
+The data have been gathered by using Application Programming Interfaces (API) to ensure high quality of the data.
 The fourth chapter discusses how the data is aggregated wrangled to enable the subsequent analysis.

### 2018-01-02 paper/paper.tex
added my 2 book sources in references.bib and in cited in paper.tex

@@
 A broadly used statistical method to simultaneously analyze multiple time series is the VAR (Vector Autoregression) approach.
-In this approach the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (Lütkepohl, 2005, p.
-4-5).\\
+In this approach the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{lütkepohl2007new}).\\
 To generate the econometric results that follow we used the statistical software STATA.
@@
 To select the optimal number of lags in our VAR regression we check for various information criteria.
-Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (Brandt and Williams, 2007, p.
-27).
+Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (\cite[p.~27]{brandt_williams_2007}).
 The calculations of these criteria for our given data set are shown in the following table.\\

### 2018-01-02 paper/paper.tex
added package (subcaption) for horizontal alignment of images
reworked the graphs/tables and lists of graphs/tables

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{float}
@@
 \listoffigures\bigskip\bigskip
+\listoftables
 
@@
 
+\begin{figure}[H]
+	\begin{subfigure}{.3\textwidth}
+	\centering
+	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_nr_tweets.png}
+	\caption{Number of Tweets regarding bitcoin}
+	\end{subfigure}\hfill
+	\begin{subfigure}{.3\textwidth}
+	\centering
+	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_df_nr_tweets.png}
+	\caption{First difference of number of Tweets}
+	\end{subfigure}\hfill
+	\begin{subfigure}{.3\textwidth}
+	\centering
+	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_log_df_nr_tweets.png}
+	\caption{Log first difference of number of Tweets}
+	\end{subfigure}
+\caption{Twitter variables development}
+\end{figure}
+
 For the bitcoin prices, a publicly available API from CoinDesk was used (Source?
@@
 \begin{figure}[H]
-	\graphicspath{ {stata_export_graphs/} }
-	\includegraphics[scale=0.45]{graph_plot_nr_tweets.png}
-	\end{figure}
-
-	\begin{figure}[H]
-	\graphicspath{ {stata_export_graphs/} }
-	\includegraphics[scale=0.45]{graph_plot_df_nr_tweets.png}
-	\end{figure}
-
-	\begin{figure}[H]
-	\graphicspath{ {stata_export_graphs/} }
-	\includegraphics[scale=0.45]{graph_plot_log_df_nr_tweets.png}
-	\end{figure}
-
-	\begin{figure}[H]
-	\graphicspath{ {stata_export_graphs/} }
-	\includegraphics[scale=0.45]{graph_plot_bpi.png}
-	\end{figure}
-
-	\begin{figure}[H]
-	\graphicspath{ {stata_export_graphs/} }
-	\includegraphics[scale=0.45]{graph_plot_df_bpi.png}
-	\end{figure}
-
-	\begin{figure}[H]
-	\graphicspath{ {stata_export_graphs/} }
-	\includegraphics[scale=0.45]{graph_plot_log_df_bpi.png}
+	\begin{subfigure}{.3\textwidth}
+	\centering
+	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_bpi.png}
+	\caption{Hourly development of bitcoin prices}
+	\end{subfigure}\hfill
+	\begin{subfigure}{.3\textwidth}
+	\centering
+	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_df_bpi.png}
+	\caption{First difference of bitcoin prices}
+	\end{subfigure}\hfill
+	\begin{subfigure}{.3\textwidth}
+	\centering
+	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_log_df_bpi.png}
+	\caption{Log first difference of bitcoin prices}
+	\end{subfigure}
+\caption{Bitcoin price development}
 \end{figure}
@@
 \centering
-\graphicspath{ {stata_export_graphs/} }
-\includegraphics[scale=0.85]{ADF_twitter_variables.png}
+\includegraphics[scale=0.85]{stata_export_graphs/ADF_twitter_variables.png}
+\caption{Twitter variables stationarity test}
+\label{fig:3}
 \end{figure}
@@
 \centering
-\graphicspath{ {stata_export_graphs/} }
-\includegraphics[scale=0.85]{ADF_bpi_variables.png}
+\includegraphics[scale=0.85]{stata_export_graphs/ADF_bpi_variables.png}
+\caption{Bitcoin variables stationarity test}
+\label{fig:4}
 \end{figure}
@@
 \centering
-\graphicspath{ {stata_export_graphs/} }
-\includegraphics[scale=0.85]{LAG_crit_df_nr_tweets_df_bpi.png}
+\includegraphics[scale=0.85]{stata_export_graphs/LAG_crit_df_nr_tweets_df_bpi.png}
+\caption{Lag Specification}
+\label{fig:5}
 \end{figure}
@@
 
+\begin{table}
+\centering
 	\begin{tabular}{lcc} \hline
@@
 	\end{tabular}
+\caption{Var Regression}
+\end{table}
 
@@
 \centering
-\graphicspath{ {stata_export_graphs/} }
-\includegraphics[scale=0.85]{granger_test.png}
+\includegraphics[scale=0.85]{stata_export_graphs/granger_test.png}
+\caption{Granger causality test}
+\label{fig:6}
 \end{figure}

### 2018-01-03 paper/paper.tex
improving the text for 2.3 data collection

@@
 \subsection{Data Collection}
-For our dataset, we used 2 different sources.\\
-We first collected historical data on bitcoin prices to USD and secondly, we gathered twitter massages related to bitcoin.
-We fulfil this relationship by selecting tweets that contain the term “bitcoin” in the text message.
-The time period for both collected data sets was from 19.12.2017 20:00:00 UTC to 28.12.2017 10:00:00 in an hourly basis.
-We chose an hourly basis to be able to do a statistical analysis with a certain amount of observation for the restricted processing time of this homework.\\
+For our data, we collected 2 separated time series datasets.
+One showing the twitter activity regarding bitcoin and the second one showing the bitcoin price development.
+Both datasets, were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
+We chose the hourly basis to be able to do a statistical analysis with a certain amount of observations in the restricted processing time for this homework.
+For the twitter data we aggregated every hour the total number of tweets mentioning bitcoin.
+For the bitcoin prices we selected prices at the last second of every hour.\\
+The following figure displays the twitter activity regarding bitcoin for the observed time period.
+The first plot shows the hourly change of the aggregate number of tweets containing bitcoin.
+In the second and third plots we did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
+The graphs show overall a cyclical movement arount 1200 tweets and a single outburst on the 22.12.2017 for the time interval between 15:00:01 and 21:00:00 with highest value being 4622 tweets in one hour.\\
 
@@
 
-For the bitcoin prices, a publicly available API from CoinDesk was used (Source?
-See documentation?).
-The prices collected represent the final price level of bitcoin before every hour changes.
-For example, our first listed price of bitcoin was on 19.12.2017 at 19:59:59 and our last value on 28.12.2017 at 09:59:59.
-These values construct our first time series data set and are shown in the following graph.\\
+Next we display the time series data on bitcoin price development for the observed time period.
+The first plot shows the hourly changes of bitcoin prices.
+The second and third plots are once again first difference transormations of the main variable for the later analysis.
+In this graph we observe a notably volatile movement and no spesific direction.
+This contradicts the recent trend of rising bitcoin prices in the months, but that happens because we observe a small period of a week in which bitcoin happened to have a neutral price development.\\
 

### 2018-01-03 paper/paper.tex
improving the text for 3 econometric modelling and results

@@
 From our data collection, we are left with two time series datasets representing two variables.
-A broadly used statistical method to simultaneously analyze multiple time series is the VAR (Vector Autoregression) approach.
-In this approach the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{lütkepohl2007new}).\\
+A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach.
+In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{lütkepohl2007new}).\\
 To generate the econometric results that follow we used the statistical software STATA.

### 2018-01-03 paper/paper.tex
started to forumulate twitter part

--- 2018-01-03 paper/paper.tex
@@
 \subsection{Twitter}
-Outline: Growth of Social Media, Opinion Mining, Twitter -> micro-blogging platform, tweets, functionalities, etc. ; Why good for measuring opinions ?  "gold mine"; Sentiment Analysis, What we do.
-Comment Severin: This part will contain the following steps and will be mostly based on Stenqvist et al. Predicting Bitcoin price fluctuation with Twitter sentiment analysis  (sections 2.2, 2.3)\\
-
-1) Introduction sentence -> growth of social media https://www.statista.com/statistics/278414/number-of-worldwide-social-network-users/\\
-2) Twitter as a "gold mine" to gather opinions -> What is twitter, Why is it valuable -> length of messages etc.\\
-3) Sentiment Analysis -> what is a sentiment analysis\\
-4) Sentiment Analysis of the term bitcoin based on twitter -> explain what we do \\
+With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018).
+Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community respectively in a computer-based communication network (p.
+12).
+This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p.
+6) provided by such communities or communication networks.\newline
+Twitter was founded in XXXX and reached XXX active users by 2017 (Twitter 2017). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests for several reasons:
 

### 2018-01-03 paper/paper.tex
improving text for 3.1 stationarity

--- 2018-01-03 paper/paper.tex
@@
 Before estimating a VAR model, the time series data must be checked for stationary.
-Thus, the means and variances are constant over time and the dataset do not show any trending behavior.
+Accordingly, the means and variances are constant over time and the dataset does not show any trending behavior.
 Non-stationary data can lead to an inaccurate model which is undesirable.
 To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test.\\
-First, we check for stationarity of the number of tweets (variable name in data set: nr\_of\_tweets).
-Because there this variable may not be stationary we have also vreated the first difference of the number of tweets (variable name: df\_nr\_of\_tweets) and the logarithmic first difference of the number of tweets (variable name: log\_df\_nr\_of\_tweets).
-The augmented Dickey-Fuller test for these variables gives the following results (via STATA):\\
+
+First, we check for stationarity for the twitter data (variable name: nr\_of\_tweets).
+Because this variable may not be stationary we also check for the first difference (df\_nr\_of\_tweets) and the logarithmic first difference of this variable (log\_df\_nr\_of\_tweets).
+The results of the augmented Dickey-Fuller test are listed in the  following table:\\
 
@@
 
-From these result we can see that only the first variable in not stationary.
-This is because the absolute value of the test statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475).
-The second variable is stationary (14.167 $>$ 3.475) and from here onwards we are going to continuous the analysis by using this first difference transformetion of the variable number of tweets, which fulfils stationarity.\\
+From these result we can see that only the first variable is not stationary.
+This is because the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475).
+The second variable is stationary (14.167 $>$ 3.475) and from here onwards we are going to continuous the analysis by using this first difference transformetion, which fulfils stationarity.\\
 
-Secondly, we have to check for stationarity for our second variable, the bitcoin prices (variable name in data set: bpi\_closing\_price).
+Secondly, we have to check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price).
 Here we also included the first difference (variable name: df\_bpi\_closing\_price) and the logarithmic first difference (variable name: log\_df\_bpi\_closing\_price) transformations.

### 2018-01-03 paper/paper.tex
improving the text for 3.2 Lag-specification

@@
 \subsection{Lag-Specification}
-To select the optimal number of lags in our VAR regression we check for various information criteria.
-Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (\cite[p.~27]{brandt_williams_2007}).
-The calculations of these criteria for our given data set are shown in the following table.\\
+To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria.
+Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandt_williams_2007}).
+The calculations of these criteria for our specific data set are shown in the following table.\\
 
@@
 
-As can be seen on the table, STATA calculates and presents various information criteria (AIC, HQIC, SBIC).
+As can be seen, STATA calculates and presents various information criteria (AIC, HQIC, SBIC).
 The asterisk indicates the optimal lag lenght to use for the regression analysis.
-In this case all criteria suggest a lag lenght of 1.
+In this case all criteria suggest a lag length of 1.
 

### 2018-01-03 paper/paper.tex
extended twitter part by history functionalities and conventions

@@
 6) provided by such communities or communication networks.\newline
-Twitter was founded in XXXX and reached XXX active users by 2017 (Twitter 2017). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests for several reasons:
+Twitter was founded in 2006 and gained rapidly worldwide popularity (Twitter 2018).
+and reached 330 million active users in the third quarter of 2017 (Twitter 2017, Statista 2018).
+As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics.
+In comparison to other social networks, twitter limits its posts (tweets) to relatively short messages of 140 characters.
+Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos.
+Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)
 

### 2018-01-03 paper/paper.tex
elaborated twitter part

@@
 This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p.
-6) provided by such communities or communication networks.\newline
+6) provided by such communities or communication networks.\\
+
 Twitter was founded in 2006 and gained rapidly worldwide popularity (Twitter 2018).
@@
 Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos.
-Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)
+Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)\\
+
+In this way, Twitter users create millions of posts that contain interests, opinions and informations in both a private and professional context.
+Due to the semi-structured form, the message length restriction and classifying nature, Stenqvist and Lönnö (2017, p.
+6) argue, that “Twitter has become a gold mine for opinionated data”, which is further supported in the wide adoption of researchers to analyse sentiments.\\
+
+In relation to Bitcoin, researchers already showed that analysing investors sentiments by either using a polarity classification – classifying the language in tweets as either positive or negative (see Colianni, Rosales \& Signorotti, 2015; COMMENT SEVERIN: ADD FURTHER SOURCES) – or a lexicon based approach – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017; COMMENT SEVERIN: ADD FURTHER SOURCES), can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p.
+7).
+Hence, this paper focuses only on the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further than the mentioning of the term itself.
+This approach is based on the previous research for the stock market of Mao et al.
+(2015).\\
 

### 2018-01-04 paper/paper.tex
improving the text for 3.3 Regression Model

@@
 \subsection{Regression Model}
-After determining the optimal lag gength the next step is to build the vector autoregression model (VAR model).
-For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T which repesents the variable df\_nr\_of\_tweets and B which represents bpi\_closing\_price.
+After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\
+For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T\textsubscript t which repesents the variable {\itshape df\_nr\_of\_tweets} in our data set and B\textsubscript t which represents {\itshape df\_bpi\_closing\_price}.
 As defined in the previous section the selected otpimal time lag is 1.
@@
 
-This model shows that the current value of our endogenous variavles is determined by its own past values, the past values of the other variable and an error term.
+This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term.
 In our research approach we ask the question, if the amount of tweets mentioning bitcoin in the past, has an effect on the bitcoin prices in the periods that follow.
-This question is pictured in the second equation of this model.\\
+This question is reflected in the second equation of this model.\\
 
@@
 
-The equation of our VAR model are displayed vertically in this table.
-As said before the relevant equation in the model is the second one and it is listed on the second column (B\textsubscript{t}) in the above table.
-The coefficient of 0.00463 (a\textsubscript{21}) implies that an increase of tweets by 1 increases the bitcoin price by 0.005 \$.
+The equations of our VAR model are displayed vertically in this table.
+As said before the relevant equation in the model is the second one which is listed on the right column (B\textsubscript{t}).
+The coefficient of 0.00463 (a\textsubscript{21}) implies that a change of tweets by 1 tweet, changes the bitcoin price by 0.005 \$.
 This effect is very small and statistically insignificant (p value $>$ 0.1).
-This means that based on our data set the amount of tweets have no significant effect on the price development of bitcoin.
+This answers our research question with the following statement:\\ The amount of tweets mentioning bitcoin has no significant effect on the price development of bitcoin.
 

### 2018-01-04 paper/paper.tex
improving the text for 3.4 Granger causality

@@
 To assess the reliability (causality) of the previous results we use the Granger causality test.
-This test confirms if the statements by the regression are valid.
-The following table shows the results of the Granger causality test\\
+This test confirms if the statements by an estimated regression are valid.
+The following table shows the results of the Granger causality test for our VAR regression:\\
 
@@
 
-The Null hypothesis here is... In the second row the chi2 is greater then the Prob value which allows as to reject the Null hypothesis and conclude that the regression results are valid...\\
-
-...the Null hypothesis in our case is that lagged number of Tweets does not cause changes in bitcoin prices.
-As the Table shows, we can reject the Null hypothesis because the probability is around 1\%.
-Therefore, we accept the alternative hypothesis, which says that the lagged number of tweets does cause changes in bitcoin prices.
-How these changes look exactly we have discussed in the previous section.
-The granger causality confirmed that the effect is valid.
+The relevant results for our regression are displayed in the lower row.
+The Null hypothesis here is that the lagged (lag 1) values of the number of tweets does not cause a change in the bitcoin prices.
+The Alternative hypothesis would then be that the lagged values of the number of tweets does cause a change in bitcoin prices.
+As the results show, the Probability value is 65.7\% which is clearly more than 5\% and constrain us to accept the Null hypothesis and conclude that the regression results stated above are valid.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 \vspace{2.0cm}
-{\itshape\large Alen Stepic - 11-475-258 \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - 13-606-355 \\Chi Xu - XX-XXX-XXX \par}
+{\itshape\large Alen Stepic - 11-475-258 \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - 13-606-355 \\Chi Xu - 16-300-915 \par}
 	\begin{spacing}{1}

### 2018-01-04 paper/paper.tex
Update paper.tex
Update paper.tex
Minor change

@@
 This hypothesis is broadly accepted in the financial world.
-The digitalisation leads to an increased network effect, where information can be share within second over the globe.
-Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors .
+The digitalisation leads to an increased network effect, where information can be shared over the globe.
+Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors.
 The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.

### 2018-01-04 paper/paper.tex
Update paper.tex
the wording "interact" may be a little imprecise, "exchange information and influence each other's expectation" may be more tailored in this context. What do you say?

@@
 Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors.
-The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
+The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people exchange information and influence each other's expectation, have led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
 \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as an sentiment indicator for stock prices.

### 2018-01-04 paper/paper.tex
Update paper.tex
It is problematic for us to self-assert the relevance of our own article. Perhaps rephrasing may help to captivate readers' attention.

--- 2018-01-04 paper/paper.tex
@@
 The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
-\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as an sentiment indicator for stock prices.
-As digitalization is expected to continue in the future, crypotocurrencies will hypothetical get more important.
-Thus, the topic is characterized as relevant.
+\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices.
+As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict bitcoin prices.
 

### 2018-01-04 paper/paper.tex
Update paper.tex
I suggest that we use "frequency" instead of "amount", since the former expression accentuates "flow" instead of "stock" concept

--- 2018-01-04 paper/paper.tex
@@
 \label{sec:ResearchQandGoal}
-As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount people talk about bitcoin on twitter.
+As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the frequency of bitcoin topics on twitter.
 The goal should be reached by answering the following research question: \\

### 2018-01-04 paper/paper.tex
Update paper.tex
Grammatical errors corrected

@@
 \label{sec:ResearchQandGoal}
-As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the frequency of bitcoin topics on twitter.
+As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount of bitcoin topics on Twitter.
 The goal should be reached by answering the following research question: \\
-In what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
+To what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
 

### 2018-01-04 paper/paper.tex
Update paper.tex
Grammer

@@
 The second part is characterized as the theory part.
-The theory aims to provide to the reader the necessary background information by an introduction of relevant bitcoin and twitter information in context of the paper.
+The theory aims to provide the reader with the necessary background information by introducing relevant bitcoin and twitter information in context of the paper.
 The conducted research is based on forward research and using relevant sources.

### 2018-01-04 paper/paper.tex
added § with research results in the abstract

@@
 Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
-
-***INPUT ALEN @DIMI: ADD JUST KEY FINDING THE REST I LIKE***\\
-
+The evaluation of the model showed that changes in twitter activity on bitcoin have a minimal and insignificant effect on the future price development of bitcoin.
+Accordingly, aggregate twitter fees are not a good source to predict changes in bitcoin prices.
+This result must be understood with caution, because it only applies for the specific time interval of our observations, which is about 8 days and not for the past or future trend of cryptocurrencies.
+\\
 This work was created in the context of a programming course for economists at the university of St.

### 2018-01-04 paper/paper.tex
added first draft text in part 4 conclusion

@@
 \label{sec:Conclustion}
-(Insert text)
+Understanding, describing and predicting the current phenomenon of cryptocurrencies has been the objective of many researchers.
+A variety of methods and approaches have been applied und mixed results have been produced.
+Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between twitter activity regarding bitcoin and the price evolution of bitcoin.
+After collecting hourly data for approximately 8 days we generated 2 time-series datasets and decided to perform a statistical analysis by using the Vector Autoregression (VAR) approach.\\
+
+According to our regression results, changes in twitter activity due to more or less tweets about bitcoin have a very small and insignificant effect on future changes of bitcoin price.
+The validity of this statement was also verified and confirmed by the Granger causality test.
+At this point, however, it must be pointed out that only a small period of time has been considered in this analysis and the results cannot be generalized for the overall trend of cryptocurrencies in the recent time or for the future.
+We are also aware that we may have observed a period of abnormal behavior of bitcoin prices compared to the trend of the last months.\\
+
+We encourage further research in the same direction as this paper and would be interested to see an analysis with observations over a longer period.
 

### 2018-01-04 paper/paper.tex
added sources and improved redline for twitter bitcoin part

@@
 
-One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices.
-(Mao et al., 2015, p.
-3) A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data.
-Based on analysis of the influence of twitter bullishness on the stock market by Mao et al.
-(2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.
+In previous research Madan,Saluja, and Zhao (2015)applied \textit{machine learning} algorithms to predict Bitcoin prices.
+By using the \textit{Bayesian regression}, Shah, Devavrat and Zhang (2015) achieved a return on investment of 89 percent over an investment period of 50 days.
+However, research in this area is still limited and most of them do not take into consideration the individuals' sentiments (Colianni, Rosales \& Signorotti, 2015, p.
+1).\\
+
+One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices(Mao et al., 2015, p.
+3).
+A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data, which will be covered in the following section.\\
 
@@
 With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018).
-Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community respectively in a computer-based communication network (p.
+Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community, respectively in a computer-based communication network (p.
 12).
@@
 
-In relation to Bitcoin, researchers already showed that analysing investors sentiments by either using a polarity classification – classifying the language in tweets as either positive or negative (see Colianni, Rosales \& Signorotti, 2015; COMMENT SEVERIN: ADD FURTHER SOURCES) – or a lexicon based approach – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017; COMMENT SEVERIN: ADD FURTHER SOURCES), can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p.
-7).
-Hence, this paper focuses only on the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further than the mentioning of the term itself.
-This approach is based on the previous research for the stock market of Mao et al.
-(2015).\\
+In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p.
+7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017).
+Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
+Based on analysis of the influence of twitter bullishness on the stock market by Mao et al.
+(2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex
Grammer plus spelling

@@
 The conducted research is based on forward research and using relevant sources.
-Furthermore, it contains a short introduction into the Vector Autoregression approach (VAR) and the constrains in context with the paper.
+Furthermore, it contains a short introduction into the Vector Autoregression (VAR) approach and its constrains in context with the paper.
 This is conducted in chapters \ref{sec:Background} and \ref{sec:EconometricModellingandResults}.
 The third part contains the discussion of the results and a conclusion.
-The conclusion is based on the theory and the own conducted mathematical computation.
-Those computations are based on a data set, which was gathered by own coded python scripts for the timeperiod December 20th - 27th.
-Based on the short time of observation the results have to be interpreted carefully.
-The data set contains out of two data sources (1) twitter tweets which contain the buzzword "bitcoin" and (2) historical bitcoin prices.
-Those two sources has been aggregated with a separate python script.
-The output of aggregation was further proceeded with stata to conduct the VAR on a daily basis.
+The conclusion is based on the theory and our mathematical computation.
+The computation is based on a data set, which was gathered by coded python scripts for the time period December 20th - 27th.
+Since the results are based on the observation of a short period, they have to be interpreted carefully.
+The data set consists of two data sources with the following characteristics: (1) twitter tweets which contain the buzzword "bitcoin" and (2) those containing historical bitcoin prices.
+The two sources has been aggregated with another python script.
+The output of aggregation was further processed with Stata to conduct the VAR on a daily basis.
 The third part of the paper is discussed in the chapters \ref{sec:EconometricModellingandResults} and \ref{sec:Conclustion}.

### 2018-01-04 paper/paper.tex

@@
 \label{sec:ResearchQandGoal}
-As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the amount of bitcoin topics on Twitter.
+
+As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the frequency of bitcoin topics on twitter.
 The goal should be reached by answering the following research question: \\
-To what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
+In what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
 

### 2018-01-04 paper/paper.tex
Update paper.tex
Everyone can create her cryptocurrency, I have created mine (Chicoin) via https://cryptonotestarter.org/inner.html

--- 2018-01-04 paper/paper.tex
@@
 \label{sec:Scope}
-The paper's focus lies on the scientific discussion and answer of the research question mentioned above.
-The research question has consciously been design very tiny, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high quality scientific paper.
-As already mentioned above, the results have to be interpreted carefully because of the limited observation time of seven days.
-The approach and technical issues (like code scripts etc.) are not addressed.
-Those points are explained in the separate documentation paper.
+The paper's focus lies on the scientific discussion of empirical test results.
+The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high-quality scientific paper.
+As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days.
+The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in the separate documentation paper.
 
@@
 \subsection{Bitcoin}
-After the global financial crisis, Satoshi Nakamoto (2008, p.
+In the aftermath of the global financial crisis, Satoshi Nakamoto (2008, p.
 1) claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
-Starting from his whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions (blockchain) has been developed (Nakamoto, 2008, p.
+Starting from this whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions \footnote{blockchain} has been developed (Nakamoto, 2008, p.
 1).\\
 
-Today, Bitcoin is the most popular of over 1300 so-called cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
+Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
 Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for payment purposes.

### 2018-01-04 paper/paper.tex
solve brandtwilliams2007 reference issue

@@
 %************************** Specify bibliography package **************************
-\usepackage{csquotes}
-\usepackage[style=apa,backend=biber]{biblatex}
+\usepackage{csquotes}% Recommended
+\usepackage[style=apa]{biblatex}
 \DeclareLanguageMapping{american}{american-apa}
@@
 To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria.
-Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandt_williams_2007}).
+Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
 The calculations of these criteria for our specific data set are shown in the following table.\\

### 2018-01-04 paper/paper.tex
solved ref issues with malkiel1970efficient

@@
 \label{sec:intro}
+
 \textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information.
@@
 A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach.
-In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{lütkepohl2007new}).\\
+In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
 To generate the econometric results that follow we used the statistical software STATA.

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
-Based on analysis of the influence of twitter bullishness on the stock market by Mao et al.
-(2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
+inspired on analysis of the influence of twitter bullishness on the stock market by Mao et al.
+(2015), this paper applies the similar method to Bitcoin prices.\\
 
 \subsection{Data Collection}
-For our data, we collected 2 separated time series datasets.
+For our data, we collected 2 separate time series datasets.
 One showing the twitter activity regarding bitcoin and the second one showing the bitcoin price development.

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 3).
-A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data, which will be covered in the following section.\\
+A widely used approach to measure investors’ interests is done through sentiment analysis of Twitter data, which will be covered in the following section.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017).
-Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
+Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without futher analysing investors interests implied in the semantics.
 inspired on analysis of the influence of twitter bullishness on the stock market by Mao et al.

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days.
-The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in the separate documentation paper.
+The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in a separate documentation paper.
 
@@
 Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
-Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for payment purposes.
-Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013).
-Kristoufek (2015) points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term.
-However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency.
-Kristoufek (2015) further explains the correlation is most evident in the long run.
-During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (Kristoufek, 2015).
-These findings are in line with other researchers (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\
+Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for a means of payment.
+Even more, several authors argue that the Bitcoin price and transaction volumes are mainly driven by speculative investments rather than its actual use as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013).
+Kristoufek (2015) points out that there are other influencing factors such as its use in trade, the supply of currencies and price level, which all contribute to determining the Bitcoin price in the long term.
+However, according to the same author, evidence shows that investors’ interest plays an even greater role in bitcoin's price movements, and their correlation is even more evident in the long run, and during the periods of explosive increases or rapid declines of the price, investors’ interest accelerates the price movements (Kristoufek, 2015).
+These findings are in line with other research findings (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without futher analysing investors interests implied in the semantics.
-inspired on analysis of the influence of twitter bullishness on the stock market by Mao et al.
+Inspired by analysis of the influence of twitter bullishness on the stock market by Mao et al.
 (2015), this paper applies the similar method to Bitcoin prices.\\
@@
 For our data, we collected 2 separate time series datasets.
-One showing the twitter activity regarding bitcoin and the second one showing the bitcoin price development.
-Both datasets, were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
-We chose the hourly basis to be able to do a statistical analysis with a certain amount of observations in the restricted processing time for this homework.
+One showing the twitter activity regarding bitcoin, with the second one showing the historic bitcoin price development.
+Both datasets were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
+We chose the hourly basis to conduct statistical analysis with a limited amount of observations as demanded by the feasibility of our project.
 For the twitter data we aggregated every hour the total number of tweets mentioning bitcoin.

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 Both datasets were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
-We chose the hourly basis to conduct statistical analysis with a limited amount of observations as demanded by the feasibility of our project.
-For the twitter data we aggregated every hour the total number of tweets mentioning bitcoin.
-For the bitcoin prices we selected prices at the last second of every hour.\\
-The following figure displays the twitter activity regarding bitcoin for the observed time period.
-The first plot shows the hourly change of the aggregate number of tweets containing bitcoin.
-In the second and third plots we did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
+We chose the hourly basis to conduct statistical analysis with a limited amount of observations as demanded by the feasibility of such a complex project.
+For the twitter data we aggregated by each hour all tweets mentioning "bitcoin".
+We used prices at the last second of every hour to represent the hourly bitcoin price.\\
+The following figure displays the twitter activity with regard to bitcoin for the observed time period.
+The first plot shows the hourly change of the aggregate number of tweets containing "bitcoin".
+In the second and third plots we respectively did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
 The graphs show overall a cyclical movement arount 1200 tweets and a single outburst on the 22.12.2017 for the time interval between 15:00:01 and 21:00:00 with highest value being 4622 tweets in one hour.\\

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 In the second and third plots we respectively did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
-The graphs show overall a cyclical movement arount 1200 tweets and a single outburst on the 22.12.2017 for the time interval between 15:00:01 and 21:00:00 with highest value being 4622 tweets in one hour.\\
+The graphs show overall a cyclical movement around 1200 tweets and a single outburst befalling on 22.12.2017 between 15:00:01 and 21:00:00, with highest value being 4622 tweets in one hour.\\
 

### 2018-01-04 paper/paper.tex

@@
 The first plot shows the hourly changes of bitcoin prices.
-The second and third plots are once again first difference transormations of the main variable for the later analysis.
-In this graph we observe a notably volatile movement and no spesific direction.
-This contradicts the recent trend of rising bitcoin prices in the months, but that happens because we observe a small period of a week in which bitcoin happened to have a neutral price development.\\
+The second and third plots are once again first difference transormations of the main variable for later analysis.
+In this graph we observe a notably volatile movement with no spesific direction.
+This contradicts the general rising trend of bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 \label{sec:EconometricModellingandResults}
-As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
+As stated in the beginning, we want to examine the underlying relationship between twitter price movement and bitcoin price fluctuations.
 From our data collection, we are left with two time series datasets representing two variables.

### 2018-01-04 paper/paper.tex
Update paper.tex

--- 2018-01-04 paper/paper.tex
@@
 For our data, we collected 2 separate time series datasets.
-One showing the twitter activity regarding bitcoin, with the second one showing the historic bitcoin price development.
+One showing the twitter activity regarding bitcoin, with the second one showing the historical bitcoin price development.
 Both datasets were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
@@
 \label{sec:EconometricModellingandResults}
-As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
+As stated in the beginning, our purpose is to examine the underlying relationship between twitter buzz and bitcoin price fluctuations.
 From our data collection, we are left with two time series datasets representing two variables.

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
-To generate the econometric results that follow we used the statistical software STATA.
+To generate the following econometric results we used the statistical software STATA.
 
 \subsection{Stationarity}
-Before estimating a VAR model, the time series data must be checked for stationary.
-Accordingly, the means and variances are constant over time and the dataset does not show any trending behavior.
-Non-stationary data can lead to an inaccurate model which is undesirable.
-To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test.\\
+Before estimating a VAR model, the time series data's stationarity must be confirmed.
+Namely, we need to demonstrate that the means and variances are constant over time and that the dataset does not show any trending behavior.
+Non-stationary data can lead to an inaccurate estimation with VAR model.
+To conduct stationarity test, we use the Augmented Dickey-Fuller (ADF) test.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 Before estimating a VAR model, the time series data's stationarity must be confirmed.
-Namely, we need to demonstrate that the means and variances are constant over time and that the dataset does not show any trending behavior.
+Namely, we need to demonstrate that the means and variances are constant over time, and that the dataset does not show any trending behavior.
 Non-stationary data can lead to an inaccurate estimation with VAR model.
@@
 
-First, we check for stationarity for the twitter data (variable name: nr\_of\_tweets).
-Because this variable may not be stationary we also check for the first difference (df\_nr\_of\_tweets) and the logarithmic first difference of this variable (log\_df\_nr\_of\_tweets).
+We shall test the stationarity for the "crude" twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets).
 The results of the augmented Dickey-Fuller test are listed in the following table:\\
@@
 
-From these result we can see that only the first variable is not stationary.
-This is because the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475).
-The second variable is stationary (14.167 $>$ 3.475) and from here onwards we are going to continuous the analysis by using this first difference transformetion, which fulfils stationarity.\\
+From the results we can see that only the first variable (i.e.
+the untransformed tweet count) is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence.
+The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis by using the first difference tweet count, which fulfills the stationarity requirement.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 the untransformed tweet count) is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence.
-The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis by using the first difference tweet count, which fulfills the stationarity requirement.\\
+The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis with only the first difference tweet count, whose test statistic falls furthest into the rejection zone.\\
 
-Secondly, we have to check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price).
-Here we also included the first difference (variable name: df\_bpi\_closing\_price) and the logarithmic first difference (variable name: log\_df\_bpi\_closing\_price) transformations.
+Out of the similar concern stated above, we shall check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price).
+As before, we also include the first difference bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference ones (variable name: log\_df\_bpi\_closing\_price) transformations.
 The ADF test for these variables gives the following results:\\
@@
 
-These result also suggest to use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
+Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
 

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 
-\subsection{Stationarity}
+\subsection{Preparing for VAR: Stationarity Test}
 Before estimating a VAR model, the time series data's stationarity must be confirmed.
@@
 
-Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
+Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for it succeeds best the ADF test.
 
-\subsection{Lag-Specification}
+\subsection{Preparing for VAR: Lag-Specification}
 To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria.
-Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
+Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
 The calculations of these criteria for our specific data set are shown in the following table.\\
@@
 
-As can be seen, STATA calculates and presents various information criteria (AIC, HQIC, SBIC).
+As can be seen, STATA calculates and presents various information criteria (AIC: Akaike Information Criterion, HQIC: Hannan–Quinn information criterion, SBIC: Schwarz-Bayesian Information Criterion).
 The asterisk indicates the optimal lag lenght to use for the regression analysis.

### 2018-01-04 paper/paper.tex
Update paper.tex

@@
 
-\subsection{Regression Model}
+\subsection{VAR Regression Model}
 After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\

### 2018-01-04 paper/paper.tex
Bitcoin and Twitter in Capital letters; Added citations in Bibtex format

--- 2018-01-04 paper/paper.tex
@@
 \pagenumbering{Roman}
-This paper, examines the dynamics between the amount of twitter activity regarding bitcoin and the actual price fluctuation of bitcoin.
+This paper, examines the dynamics between the amount of Twitter activity regarding Bitcoin and the actual price fluctuation of Bitcoin.
 For the analysis two sets of data have been collected.
-One reflecting twitter activity and the other one showing the bitcoin prices for the same period.
+One reflecting Twitter activity and the other one showing the Bitcoin prices for the same period.
 Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
-The evaluation of the model showed that changes in twitter activity on bitcoin have a minimal and insignificant effect on the future price development of bitcoin.
-Accordingly, aggregate twitter fees are not a good source to predict changes in bitcoin prices.
+The evaluation of the model showed that changes in Twitter activity on Bitcoin have a minimal and insignificant effect on the future price development of Bitcoin.
+Accordingly, aggregate Twitter fees are not a good source to predict changes in Bitcoin prices.
 This result must be understood with caution, because it only applies for the specific time interval of our observations, which is about 8 days and not for the past or future trend of cryptocurrencies.
@@
 
-%************************** Chapters 1 - Introduction **************************
+%************************** Chapter 1 - Introduction **************************
 \begin{spacing}{1.2}
@@
 Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors.
-The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
-\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices.
-As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict bitcoin prices.
+The large fluctuation of the Bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on Bitcoin and Twitter.
+\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices.
+As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict Bitcoin prices.
 
@@
 
-As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the frequency of bitcoin topics on twitter.
+As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter.
 The goal should be reached by answering the following research question: \\
-In what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
+In what extent does the amount of Twitter tweets about Bitcoin has an effect on the price movement of Bitcoin?
 
@@
 The second part is characterized as the theory part.
-The theory aims to provide the reader with the necessary background information by introducing relevant bitcoin and twitter information in context of the paper.
+The theory aims to provide the reader with the necessary background information by introducing relevant Bitcoin and Twitter information in context of the paper.
 The conducted research is based on forward research and using relevant sources.
@@
 Since the results are based on the observation of a short period, they have to be interpreted carefully.
-The data set consists of two data sources with the following characteristics: (1) twitter tweets which contain the buzzword "bitcoin" and (2) those containing historical bitcoin prices.
+The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "Bitcoin" and (2) those containing historical Bitcoin prices.
 The two sources has been aggregated with another python script.
@@
 
-%************************** Chapters 2 - Background and Data Collection **************************
+%************************** Chapter 2 - Background and Data Collection **************************
 \section{Background and Data Collection}
@@
 \subsection{Bitcoin}
-In the aftermath of the global financial crisis, Satoshi Nakamoto (2008, p.
-1) claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
-Starting from this whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions \footnote{blockchain} has been developed (Nakamoto, 2008, p.
-1).\\
+In the aftermath of the global financial crisis, \textcite[p.~1]{Nakamoto2008Bitcoin} claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
+Starting from this whitepaper, Bitcoin {-} the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions \footnote{Blockchain} has been developed (\cite[p.~1]{Nakamoto2008Bitcoin}).\\
 
-Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
-Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for a means of payment.
-Even more, several authors argue that the Bitcoin price and transaction volumes are mainly driven by speculative investments rather than its actual use as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013).
-Kristoufek (2015) points out that there are other influencing factors such as its use in trade, the supply of currencies and price level, which all contribute to determining the Bitcoin price in the long term.
-However, according to the same author, evidence shows that investors’ interest plays an even greater role in bitcoin's price movements, and their correlation is even more evident in the long run, and during the periods of explosive increases or rapid declines of the price, investors’ interest accelerates the price movements (Kristoufek, 2015).
-These findings are in line with other research findings (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\
+Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap\footnote{https://coinmarketcap.com/}.
+Even if the \textit{daily transaction volume}\footnotemark[2] increased rapidly over time, this does not necessarily mean that Bitcoin is used for payment purposes.
+Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (\cite{corbet2017datestamping}; \cite{Forbes2017}; \cite{yermack2013bitcoin}).
+\textcite{kristoufek2015main} points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term.
+However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency.
+\textcite{kristoufek2015main} further explains the correlation is most evident in the long run.
+During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (\cite{kristoufek2015main}).
+These findings are in line with other researchers (see \cite[]{garcia2014digital}; \cite[]{kondor2014rich}).\\
 
-In previous research Madan,Saluja, and Zhao (2015)applied \textit{machine learning} algorithms to predict Bitcoin prices.
-By using the \textit{Bayesian regression}, Shah, Devavrat and Zhang (2015) achieved a return on investment of 89 percent over an investment period of 50 days.
-However, research in this area is still limited and most of them do not take into consideration the individuals' sentiments (Colianni, Rosales \& Signorotti, 2015, p.
-1).\\
+In previous research \textcite{madan2015automated} applied \textit{machine learning} algorithms to predict Bitcoin prices.
+By using the \textit{bayesian regression}, \textcite{shah2014bayesian} achieved a return on investment of 89 percent over an investment period of 50 days.
+However, research in this area is still limited and most of them do not take into consideration the individuals' sentiments (\cite[p.~1]{colianni2015algorithmic}).\\
 
-One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices(Mao et al., 2015, p.
-3).
-A widely used approach to measure investors’ interests is done through sentiment analysis of Twitter data, which will be covered in the following section.\\
+One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices (\cite[p.~3]{mao2015quantifying}).
+A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data, which will be covered in the following section.\\
 
 \subsection{Twitter}
-With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018).
-Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community, respectively in a computer-based communication network (p.
-12).
-This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p.
-6) provided by such communities or communication networks.\\
+With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to \textcite{Statista2018a}.
+\textcite[p.~12]{Gabriel2017socialmedia} define social networks as a loose connection of people in an online or internet community, respectively in a computer-based communication network.
+This paper exploits the possibility to analyse shared “thoughts, views and opinions” (\cite[p.~6]{stenqvist2017predicting}) provided by such communities or communication networks.\\
 
-Twitter was founded in 2006 and gained rapidly worldwide popularity (Twitter 2018).
-and reached 330 million active users in the third quarter of 2017 (Twitter 2017, Statista 2018).
+Twitter was founded in 2006 and gained rapidly worldwide popularity and reached 330 million active users in the third quarter of 2017  (\cite[]{twitterinc2018}; \cite[]{Statista2018b}).
 As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics.
@@
 Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos.
-Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)\\
+Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(\cite{Schmidt2018socialmedia})\\
 
 In this way, Twitter users create millions of posts that contain interests, opinions and informations in both a private and professional context.
-Due to the semi-structured form, the message length restriction and classifying nature, Stenqvist and Lönnö (2017, p.
-6) argue, that “Twitter has become a gold mine for opinionated data”, which is further supported in the wide adoption of researchers to analyse sentiments.\\
+Due to the semi-structured form, the message length restriction and classifying nature, \textcite[p.~6]{stenqvist2017predicting} argue, that “Twitter has become a gold mine for opinionated data”, which is further supported in the wide adoption of researchers to analyse sentiments.\\
 
-In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p.
-7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017).
-Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without futher analysing investors interests implied in the semantics.
-Inspired by analysis of the influence of twitter bullishness on the stock market by Mao et al.
-(2015), this paper applies the similar method to Bitcoin prices.\\
+In relation to Bitcoin, researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies \textcite[p.~7]{stenqvist2017predicting} , by either using a \textit{polarity classification} {-} classifying the language in tweets as either positive or negative (see \cite{colianni2015algorithmic}) {-} or a \textit{lexicon based approach} {-} attributes predefined words to specific sentiment classifications (see \cite{stenqvist2017predicting}).
+Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
+Based on analysis of the influence of twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
 
 \subsection{Data Collection}
-For our data, we collected 2 separate time series datasets.
-One showing the twitter activity regarding bitcoin, with the second one showing the historical bitcoin price development.
+For our data, we collected two separate time series datasets.
+One showing the Twitter activity regarding Bitcoin, with the second one showing the historical Bitcoin price development.
 Both datasets were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
 We chose the hourly basis to conduct statistical analysis with a limited amount of observations as demanded by the feasibility of such a complex project.
-For the twitter data we aggregated by each hour all tweets mentioning "bitcoin".
-We used prices at the last second of every hour to represent the hourly bitcoin price.\\
-The following figure displays the twitter activity with regard to bitcoin for the observed time period.
-The first plot shows the hourly change of the aggregate number of tweets containing "bitcoin".
+For the Twitter data we aggregated by each hour all tweets mentioning "Bitcoin".
+We used prices at the last second of every hour to represent the hourly Bitcoin price.\\
+The following figure displays the Twitter activity with regard to Bitcoin for the observed time period.
+The first plot shows the hourly change of the aggregate number of tweets containing "Bitcoin".
 In the second and third plots we respectively did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_nr_tweets.png}
-	\caption{Number of Tweets regarding bitcoin}
+	\caption{Number of Tweets regarding Bitcoin}
 	\end{subfigure}\hfill
@@
 
-Next we display the time series data on bitcoin price development for the observed time period.
-The first plot shows the hourly changes of bitcoin prices.
+Next we display the time series data on Bitcoin price development for the observed time period.
+The first plot shows the hourly changes of Bitcoin prices.
 The second and third plots are once again first difference transormations of the main variable for later analysis.
 In this graph we observe a notably volatile movement with no spesific direction.
-This contradicts the general rising trend of bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
+This contradicts the general rising trend of Bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when Bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
 
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_bpi.png}
-	\caption{Hourly development of bitcoin prices}
+	\caption{Hourly development of Bitcoin prices}
 	\end{subfigure}\hfill
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_df_bpi.png}
-	\caption{First difference of bitcoin prices}
+	\caption{First difference of Bitcoin prices}
 	\end{subfigure}\hfill
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_log_df_bpi.png}
-	\caption{Log first difference of bitcoin prices}
+	\caption{Log first difference of Bitcoin prices}
 	\end{subfigure}
@@
 
-%************************** Chapters 3 - Econometric Modelling and Results **************************
+%************************** Chapter 3 - Econometric Modelling and Results **************************
 \section{Econometric Modelling and Results}
 \label{sec:EconometricModellingandResults}
-As stated in the beginning, our purpose is to examine the underlying relationship between twitter buzz and bitcoin price fluctuations.
+As stated in the beginning, our purpose is to examine the underlying relationship between the number of tweets containing "Bitcoin" and Bitcoin price fluctuations.
 From our data collection, we are left with two time series datasets representing two variables.
@@
 
-We shall test the stationarity for the "crude" twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets).
+We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference Twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets).
 The results of the augmented Dickey-Fuller test are listed in the following table:\\
@@
 
-Out of the similar concern stated above, we shall check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price).
-As before, we also include the first difference bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference ones (variable name: log\_df\_bpi\_closing\_price) transformations.
+Out of the similar concern stated above, we shall check for stationarity for the second variable, the Bitcoin prices (variable name: bpi\_closing\_price).
+As before, we also include the first difference Bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference ones (variable name: log\_df\_bpi\_closing\_price) transformations.
 The ADF test for these variables gives the following results:\\
@@
 
-Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
+Once again, the test result suggests we use the first difference transformation of the variable Bitcoin prices, for it succeeds best the ADF test.
 
@@
 This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term.
-In our research approach we ask the question, if the amount of tweets mentioning bitcoin in the past, has an effect on the bitcoin prices in the periods that follow.
+In our research approach we ask the question, if the amount of tweets mentioning Bitcoin in the past, has an effect on the Bitcoin prices in the periods that follow.
 This question is reflected in the second equation of this model.\\
@@
 As said before the relevant equation in the model is the second one which is listed on the right column (B\textsubscript{t}).
-The coefficient of 0.00463 (a\textsubscript{21}) implies that a change of tweets by 1 tweet, changes the bitcoin price by 0.005 \$.
+The coefficient of 0.00463 (a\textsubscript{21}) implies that a change of tweets by 1 tweet, changes the Bitcoin price by 0.005 \$.
 This effect is very small and statistically insignificant (p value $>$ 0.1).
-This answers our research question with the following statement:\\ The amount of tweets mentioning bitcoin has no significant effect on the price development of bitcoin.
+This answers our research question with the following statement:\\ The amount of tweets mentioning Bitcoin has no significant effect on the price development of Bitcoin.
 
@@
 The relevant results for our regression are displayed in the lower row.
-The Null hypothesis here is that the lagged (lag 1) values of the number of tweets does not cause a change in the bitcoin prices.
-The Alternative hypothesis would then be that the lagged values of the number of tweets does cause a change in bitcoin prices.
+The Null hypothesis here is that the lagged (lag 1) values of the number of tweets does not cause a change in the Bitcoin prices.
+The Alternative hypothesis would then be that the lagged values of the number of tweets does cause a change in Bitcoin prices.
 As the results show, the Probability value is 65.7\% which is clearly more than 5\% and constrain us to accept the Null hypothesis and conclude that the regression results stated above are valid.\\
@@
 
-%************************** Chapters 4 - Conclusion **************************
+%************************** Chapter 4 - Conclusion **************************
 \section{Conclusion}
@@
 A variety of methods and approaches have been applied und mixed results have been produced.
-Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between twitter activity regarding bitcoin and the price evolution of bitcoin.
+Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between Twitter activity regarding Bitcoin and the price evolution of Bitcoin.
 After collecting hourly data for approximately 8 days we generated 2 time-series datasets and decided to perform a statistical analysis by using the Vector Autoregression (VAR) approach.\\
 
-According to our regression results, changes in twitter activity due to more or less tweets about bitcoin have a very small and insignificant effect on future changes of bitcoin price.
+According to our regression results, changes in Twitter activity due to more or less tweets about Bitcoin have a very small and insignificant effect on future changes of Bitcoin price.
 The validity of this statement was also verified and confirmed by the Granger causality test.
 At this point, however, it must be pointed out that only a small period of time has been considered in this analysis and the results cannot be generalized for the overall trend of cryptocurrencies in the recent time or for the future.
-We are also aware that we may have observed a period of abnormal behavior of bitcoin prices compared to the trend of the last months.\\
+We are also aware that we may have observed a period of abnormal behavior of Bitcoin prices compared to the trend of the last months.\\
 

### 2018-01-04 paper/paper.tex

@@
 
-\subsection{Lag-Specification}
+\subsection{Preparing for VAR: Lag-Specification}
 To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria.
-Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
+Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
 The calculations of these criteria for our specific data set are shown in the following table.\\

### 2018-01-04 paper/paper.tex
Update paper.tex
"align" command fits better than "split" command here
Update paper.tex
grammar

@@
 
-\begin{equation}
-\begin{split}
+\begin{align}
 T_t = c_1 + a_{11}T_{t-1} + a_{12}B_{t-1} + \epsilon_1 \\
 B_t = c_2 + a_{21}T_{t-1} + a_{22}B_{t-1} + \epsilon_2
-\end{split}
-\end{equation}
+\end{align}
 
 This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term.
-In our research approach we ask the question, if the amount of tweets mentioning Bitcoin in the past, has an effect on the Bitcoin prices in the periods that follow.
-This question is reflected in the second equation of this model.\\
+The second equation is directly relevant to our research question, as it allows to look into the correlation between present bitcoin price and past tweet count.\\
 

### 2018-01-04 paper/paper.tex
Update paper.tex
grammar

@@
 This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term.
-The second equation is directly relevant to our research question, as it allows to look into the correlation between present bitcoin price and past tweet count.\\
+The second equation is directly relevant to our research question, as it allows to look into the correlation between the present bitcoin price and the past tweet count.\\
 

### 2018-01-04 documentation/documentation.tex
adding tweepy, sorting doo, ading chi student id

@@
 \vspace{1.2cm}
-{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - XX-XXX-XXX \par}
+{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - 16-300-915 \par}
 \vspace{1.2cm}
@@
 Such as the open-source package tweepy.
-This package has been used for streaming the twitter data as it simplify the script and enables to gather a broader number of tweets for free.
 
-Tweepy is
-TBD
-TBD
-TBD
+\paragraph{Tweepy}\mbox{}\\{}
+Tweepy is a open-source libary.
+It provides a simple way to gather real time tweets, by managing authentication, connection and tweet information of Twitters streaming API.
+The tweepy instance tweepy.streaming is used for the streaming session and forwards the data to the StreamListener instance.
+The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|.
+With this method all data of filtered tweets are gathered in real time.
+The main function \verb|def main()| manages the required authentication as follow:
+\begin{lstlisting}[language=bash]
+auth = OAuthHandler (ckey, csecret)
+auth.set_access_token(atoken, asecret)
+\end{lstlisting}
+Those authentications are demanded by twitter and explained in more details in the next paragraph.
+Furthermore, the main function starts the running of the stream, while filtering for the buzzword bitcoin by processing \verb|twitterStream.filter(track=["bitcoin"]|.
+Tweepy has been applied for this assignment because it simplify the script and enables to gather a huge number of tweets for free.
 
@@
 \begin{lstlisting}[language=bash]
-%https://apps.twitter.com/
+https://apps.twitter.com/
 \end{lstlisting}
@@
 \begin{flushleft}
-................................\\
 Alen Stepic - 11-475-258\\\bigskip\bigskip  
-................................\\
 Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip
-................................\\
 Severin Kranz - 13-606-355\\\bigskip\bigskip
-................................\\
 Joël Sonderegger - 11-495-488\\\bigskip\bigskip
-................................\\
-Chi Xu - XX-XXX-XXX
+Chi Xu - 16-300-915
 

### 2018-01-04 paper/paper.tex
adding tweepy, sorting doo, ading chi student id

--- 2018-01-04 paper/paper.tex
@@
 \pagenumbering{Roman}
-This paper, examines the dynamics between the amount of Twitter activity regarding Bitcoin and the actual price fluctuation of Bitcoin.
+This paper, examines the dynamics between the amount of twitter activity regarding bitcoin and the actual price fluctuation of bitcoin.
 For the analysis two sets of data have been collected.
-One reflecting Twitter activity and the other one showing the Bitcoin prices for the same period.
+One reflecting twitter activity and the other one showing the bitcoin prices for the same period.
 Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
-The evaluation of the model showed that changes in Twitter activity on Bitcoin have a minimal and insignificant effect on the future price development of Bitcoin.
-Accordingly, aggregate Twitter fees are not a good source to predict changes in Bitcoin prices.
+The evaluation of the model showed that changes in twitter activity on bitcoin have a minimal and insignificant effect on the future price development of bitcoin.
+Accordingly, aggregate twitter fees are not a good source to predict changes in bitcoin prices.
 This result must be understood with caution, because it only applies for the specific time interval of our observations, which is about 8 days and not for the past or future trend of cryptocurrencies.
@@
 
-%************************** Chapter 1 - Introduction **************************
+%************************** Chapters 1 - Introduction **************************
 \begin{spacing}{1.2}
@@
 Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors.
-The large fluctuation of the Bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on Bitcoin and Twitter.
-\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices.
-As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict Bitcoin prices.
+The large fluctuation of the bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on bitcoin and twitter.
+\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices.
+As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict bitcoin prices.
 
@@
 \label{sec:ResearchQandGoal}
+As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of bitcoin and the frequency of bitcoin topics on twitter.
+The goal should be reached by answering the following research question: \\
 
-As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter.
-The goal should be reached by answering the following research question: \\
-In what extent does the amount of Twitter tweets about Bitcoin has an effect on the price movement of Bitcoin?
+In what extend does the amount of twitter tweets about bitcoin has an effect on the price movement of bitcoin?
 
@@
 The second part is characterized as the theory part.
-The theory aims to provide the reader with the necessary background information by introducing relevant Bitcoin and Twitter information in context of the paper.
+The theory aims to provide the reader with the necessary background information by introducing relevant bitcoin and twitter information in context of the paper.
 The conducted research is based on forward research and using relevant sources.
@@
 Since the results are based on the observation of a short period, they have to be interpreted carefully.
-The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "Bitcoin" and (2) those containing historical Bitcoin prices.
+The data set consists of two data sources with the following characteristics: (1) twitter tweets which contain the buzzword "bitcoin" and (2) those containing historical bitcoin prices.
 The two sources has been aggregated with another python script.
@@
 The paper's focus lies on the scientific discussion of empirical test results.
-The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results, rather than writing a high-quality scientific paper.
+The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results.
 As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days.
+However, the results provide a first impression and can be further be developed.
 The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in a separate documentation paper.
@@
 
-%************************** Chapter 2 - Background and Data Collection **************************
+%************************** Chapters 2 - Background and Data Collection **************************
 \section{Background and Data Collection}
@@
 \subsection{Bitcoin}
-In the aftermath of the global financial crisis, \textcite[p.~1]{Nakamoto2008Bitcoin} claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
-Starting from this whitepaper, Bitcoin {-} the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions \footnote{Blockchain} has been developed (\cite[p.~1]{Nakamoto2008Bitcoin}).\\
+In the aftermath of the global financial crisis, Satoshi Nakamoto (2008, p.
+1) claimed, that a purely peer-to-peer version of electronic cash could bypass financial institutions as third parties for commercial transactions.
+Starting from this whitepaper, Bitcoin – the first electronic payment system that relies on the cryptographic concatenation of ongoing transactions \footnote{blockchain} has been developed (Nakamoto, 2008, p.
+1).\\
 
-Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap\footnote{https://coinmarketcap.com/}.
-Even if the \textit{daily transaction volume}\footnotemark[2] increased rapidly over time, this does not necessarily mean that Bitcoin is used for payment purposes.
-Even more, several authors argue that the Bitcoin price and transaction volumes are mainly pushed by speculative investments rather than actual usage as a currency (\cite{corbet2017datestamping}; \cite{Forbes2017}; \cite{yermack2013bitcoin}).
-\textcite{kristoufek2015main} points out that there are other influencing factors such as usage in trade, money supply and price level, that influence the Bitcoin price in the long term.
-However, evidence shows that the level of Bitcoin prices are clearly driven by investors’ interest in the digital currency.
-\textcite{kristoufek2015main} further explains the correlation is most evident in the long run.
-During explosive increases or rapid declines of the price higher investors’ interest further boosts the movement in the direction (\cite{kristoufek2015main}).
-These findings are in line with other researchers (see \cite[]{garcia2014digital}; \cite[]{kondor2014rich}).\\
+Today, Bitcoin is the most popular of thousands of cryptocurrencies worldwide and increased in value over 1700 percent within the last year according to Coinmarketcap (https://coinmarketcap.com/).
+Even if the daily transaction volume increased rapidly over time (https://coinmarketcap.com/), this does not necessarily mean that Bitcoin is used for a means of payment.
+Even more, several authors argue that the Bitcoin price and transaction volumes are mainly driven by speculative investments rather than its actual use as a currency (Corbet, Lucey \& Yarovya, 2017; Forbes, 2017; Yermack, 2013).
+Kristoufek (2015) points out that there are other influencing factors such as its use in trade, the supply of currencies and price level, which all contribute to determining the Bitcoin price in the long term.
+However, according to the same author, evidence shows that investors’ interest plays an even greater role in bitcoin's price movements, and their correlation is even more evident in the long run, and during the periods of explosive increases or rapid declines of the price, investors’ interest accelerates the price movements (Kristoufek, 2015).
+These findings are in line with other research findings (see Garcia, Tessone, Mayrodiev \& Perony, 2014; Kondor, Posfai, Csabai, \&Vattay, 2014).\\
 
-In previous research \textcite{madan2015automated} applied \textit{machine learning} algorithms to predict Bitcoin prices.
-By using the \textit{bayesian regression}, \textcite{shah2014bayesian} achieved a return on investment of 89 percent over an investment period of 50 days.
-However, research in this area is still limited and most of them do not take into consideration the individuals' sentiments (\cite[p.~1]{colianni2015algorithmic}).\\
+In previous research Madan,Saluja, and Zhao (2015)applied \textit{machine learning} algorithms to predict Bitcoin prices.
+By using the \textit{Bayesian regression}, Shah, Devavrat and Zhang (2015) achieved a return on investment of 89 percent over an investment period of 50 days.
+However, research in this area is still limited and most of them do not take into consideration the individuals' sentiments (Colianni, Rosales \& Signorotti, 2015, p.
+1).\\
 
-One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices (\cite[p.~3]{mao2015quantifying}).
-A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data, which will be covered in the following section.\\
+One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices(Mao et al., 2015, p.
+3).
+A widely used approach to measure investors’ interests is done through sentiment analysis of Twitter data, which will be covered in the following section.\\
 
 \subsection{Twitter}
-With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to \textcite{Statista2018a}.
-\textcite[p.~12]{Gabriel2017socialmedia} define social networks as a loose connection of people in an online or internet community, respectively in a computer-based communication network.
-This paper exploits the possibility to analyse shared “thoughts, views and opinions” (\cite[p.~6]{stenqvist2017predicting}) provided by such communities or communication networks.\\
+With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018).
+Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community, respectively in a computer-based communication network (p.
+12).
+This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p.
+6) provided by such communities or communication networks.\\
 
-Twitter was founded in 2006 and gained rapidly worldwide popularity and reached 330 million active users in the third quarter of 2017  (\cite[]{twitterinc2018}; \cite[]{Statista2018b}).
+Twitter was founded in 2006 and gained rapidly worldwide popularity (Twitter 2018).
+and reached 330 million active users in the third quarter of 2017 (Twitter 2017, Statista 2018).
 As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics.
@@
 Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos.
-Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(\cite{Schmidt2018socialmedia})\\
+Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)\\
 
 In this way, Twitter users create millions of posts that contain interests, opinions and informations in both a private and professional context.
-Due to the semi-structured form, the message length restriction and classifying nature, \textcite[p.~6]{stenqvist2017predicting} argue, that “Twitter has become a gold mine for opinionated data”, which is further supported in the wide adoption of researchers to analyse sentiments.\\
+Due to the semi-structured form, the message length restriction and classifying nature, Stenqvist and Lönnö (2017, p.
+6) argue, that “Twitter has become a gold mine for opinionated data”, which is further supported in the wide adoption of researchers to analyse sentiments.\\
 
-In relation to Bitcoin, researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies \textcite[p.~7]{stenqvist2017predicting} , by either using a \textit{polarity classification} {-} classifying the language in tweets as either positive or negative (see \cite{colianni2015algorithmic}) {-} or a \textit{lexicon based approach} {-} attributes predefined words to specific sentiment classifications (see \cite{stenqvist2017predicting}).
-Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
-Based on analysis of the influence of twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
+In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p.
+7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017).
+Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without futher analysing investors interests implied in the semantics.
+Inspired by analysis of the influence of twitter bullishness on the stock market by Mao et al.
+(2015), this paper applies the similar method to Bitcoin prices.\\
 
 \subsection{Data Collection}
-For our data, we collected two separate time series datasets.
-One showing the Twitter activity regarding Bitcoin, with the second one showing the historical Bitcoin price development.
+For our data, we collected 2 separate time series datasets.
+One showing the twitter activity regarding bitcoin, with the second one showing the historic bitcoin price development.
 Both datasets were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC.
 We chose the hourly basis to conduct statistical analysis with a limited amount of observations as demanded by the feasibility of such a complex project.
-For the Twitter data we aggregated by each hour all tweets mentioning "Bitcoin".
-We used prices at the last second of every hour to represent the hourly Bitcoin price.\\
-The following figure displays the Twitter activity with regard to Bitcoin for the observed time period.
-The first plot shows the hourly change of the aggregate number of tweets containing "Bitcoin".
+For the twitter data we aggregated by each hour all tweets mentioning "bitcoin".
+We used prices at the last second of every hour to represent the hourly bitcoin price.\\
+The following figure displays the twitter activity with regard to bitcoin for the observed time period.
+The first plot shows the hourly change of the aggregate number of tweets containing "bitcoin".
 In the second and third plots we respectively did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_nr_tweets.png}
-	\caption{Number of Tweets regarding Bitcoin}
+	\caption{Number of Tweets regarding bitcoin}
 	\end{subfigure}\hfill
@@
 
-Next we display the time series data on Bitcoin price development for the observed time period.
-The first plot shows the hourly changes of Bitcoin prices.
+Next we display the time series data on bitcoin price development for the observed time period.
+The first plot shows the hourly changes of bitcoin prices.
 The second and third plots are once again first difference transormations of the main variable for later analysis.
 In this graph we observe a notably volatile movement with no spesific direction.
-This contradicts the general rising trend of Bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when Bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
+This contradicts the general rising trend of bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
 
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_bpi.png}
-	\caption{Hourly development of Bitcoin prices}
+	\caption{Hourly development of bitcoin prices}
 	\end{subfigure}\hfill
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_df_bpi.png}
-	\caption{First difference of Bitcoin prices}
+	\caption{First difference of bitcoin prices}
 	\end{subfigure}\hfill
@@
 	\includegraphics[width=1.12\textwidth]{stata_export_graphs/graph_plot_log_df_bpi.png}
-	\caption{Log first difference of Bitcoin prices}
+	\caption{Log first difference of bitcoin prices}
 	\end{subfigure}
@@
 
-%************************** Chapter 3 - Econometric Modelling and Results **************************
+%************************** Chapters 3 - Econometric Modelling and Results **************************
 \section{Econometric Modelling and Results}
 \label{sec:EconometricModellingandResults}
-As stated in the beginning, our purpose is to examine the underlying relationship between the number of tweets containing "Bitcoin" and Bitcoin price fluctuations.
+As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations.
 From our data collection, we are left with two time series datasets representing two variables.
@@
 In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
-To generate the following econometric results we used the statistical software STATA.
+To generate the econometric results that follow we used the statistical software STATA.
 
-\subsection{Preparing for VAR: Stationarity Test}
-Before estimating a VAR model, the time series data's stationarity must be confirmed.
-Namely, we need to demonstrate that the means and variances are constant over time, and that the dataset does not show any trending behavior.
-Non-stationary data can lead to an inaccurate estimation with VAR model.
-To conduct stationarity test, we use the Augmented Dickey-Fuller (ADF) test.\\
+\subsection{Stationarity}
+Before estimating a VAR model, the time series data must be checked for stationary.
+Accordingly, the means and variances are constant over time and the dataset does not show any trending behavior.
+Non-stationary data can lead to an inaccurate model which is undesirable.
+To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test.\\
 
-We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference Twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets).
+First, we check for stationarity for the twitter data (variable name: nr\_of\_tweets).
+Because this variable may not be stationary we also check for the first difference (df\_nr\_of\_tweets) and the logarithmic first difference of this variable (log\_df\_nr\_of\_tweets).
 The results of the augmented Dickey-Fuller test are listed in the  following table:\\
@@
 
-From the results we can see that only the first variable (i.e.
-the untransformed tweet count) is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence.
-The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis with only the first difference tweet count, whose test statistic falls furthest into the rejection zone.\\
+From these result we can see that only the first variable is not stationary.
+This is because the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475).
+The second variable is stationary (14.167 $>$ 3.475) and from here onwards we are going to continuous the analysis by using this first difference transformetion, which fulfils stationarity.\\
 
-Out of the similar concern stated above, we shall check for stationarity for the second variable, the Bitcoin prices (variable name: bpi\_closing\_price).
-As before, we also include the first difference Bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference ones (variable name: log\_df\_bpi\_closing\_price) transformations.
+Secondly, we have to check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price).
+Here we also included the first difference (variable name: df\_bpi\_closing\_price) and the logarithmic first difference (variable name: log\_df\_bpi\_closing\_price) transformations.
 The ADF test for these variables gives the following results:\\
@@
 
-Once again, the test result suggests we use the first difference transformation of the variable Bitcoin prices, for it succeeds best the ADF test.
+These result also suggest to use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
 
-\subsection{Preparing for VAR: Lag-Specification}
+\subsection{Lag-Specification}
 To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria.
-Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
+Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
 The calculations of these criteria for our specific data set are shown in the following table.\\
@@
 
-As can be seen, STATA calculates and presents various information criteria (AIC: Akaike Information Criterion, HQIC: Hannan–Quinn information criterion, SBIC: Schwarz-Bayesian Information Criterion).
+As can be seen, STATA calculates and presents various information criteria (AIC, HQIC, SBIC).
 The asterisk indicates the optimal lag lenght to use for the regression analysis.
@@
 
-\subsection{VAR Regression Model}
+\subsection{Regression Model}
 After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\
@@
 This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term.
-In our research approach we ask the question, if the amount of tweets mentioning Bitcoin in the past, has an effect on the Bitcoin prices in the periods that follow.
+In our research approach we ask the question, if the amount of tweets mentioning bitcoin in the past, has an effect on the bitcoin prices in the periods that follow.
 This question is reflected in the second equation of this model.\\
@@
 As said before the relevant equation in the model is the second one which is listed on the right column (B\textsubscript{t}).
-The coefficient of 0.00463 (a\textsubscript{21}) implies that a change of tweets by 1 tweet, changes the Bitcoin price by 0.005 \$.
+The coefficient of 0.00463 (a\textsubscript{21}) implies that a change of tweets by 1 tweet, changes the bitcoin price by 0.005 \$.
 This effect is very small and statistically insignificant (p value $>$ 0.1).
-This answers our research question with the following statement:\\ The amount of tweets mentioning Bitcoin has no significant effect on the price development of Bitcoin.
+This answers our research question with the following statement:\\ The amount of tweets mentioning bitcoin has no significant effect on the price development of bitcoin.
 
@@
 The relevant results for our regression are displayed in the lower row.
-The Null hypothesis here is that the lagged (lag 1) values of the number of tweets does not cause a change in the Bitcoin prices.
-The Alternative hypothesis would then be that the lagged values of the number of tweets does cause a change in Bitcoin prices.
+The Null hypothesis here is that the lagged (lag 1) values of the number of tweets does not cause a change in the bitcoin prices.
+The Alternative hypothesis would then be that the lagged values of the number of tweets does cause a change in bitcoin prices.
 As the results show, the Probability value is 65.7\% which is clearly more than 5\% and constrain us to accept the Null hypothesis and conclude that the regression results stated above are valid.\\
@@
 
-%************************** Chapter 4 - Conclusion **************************
+%************************** Chapters 4 - Conclusion **************************
 \section{Conclusion}
@@
 A variety of methods and approaches have been applied und mixed results have been produced.
-Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between Twitter activity regarding Bitcoin and the price evolution of Bitcoin.
+Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between twitter activity regarding bitcoin and the price evolution of bitcoin.
 After collecting hourly data for approximately 8 days we generated 2 time-series datasets and decided to perform a statistical analysis by using the Vector Autoregression (VAR) approach.\\
 
-According to our regression results, changes in Twitter activity due to more or less tweets about Bitcoin have a very small and insignificant effect on future changes of Bitcoin price.
+According to our regression results, changes in twitter activity due to more or less tweets about bitcoin have a very small and insignificant effect on future changes of bitcoin price.
 The validity of this statement was also verified and confirmed by the Granger causality test.
 At this point, however, it must be pointed out that only a small period of time has been considered in this analysis and the results cannot be generalized for the overall trend of cryptocurrencies in the recent time or for the future.
-We are also aware that we may have observed a period of abnormal behavior of Bitcoin prices compared to the trend of the last months.\\
+We are also aware that we may have observed a period of abnormal behavior of bitcoin prices compared to the trend of the last months.\\
 
@@
 \item that the topic or parts of it are not already the object of any work or examination of another course unless this has been explicitly agreed on with the faculty member in advance and is referred to in the thesis;
-\item that we will not pass on copies of this work to third parties or publish them without the University’s written consent if a direct connection can be established with the University of St.Gallen or its faculty members;
 \item that we are aware that our work can be electronically checked for plagiarism and that we hereby grant the University of St.Gallen copyright in accordance with the Examination Regulations in so far as this is required for administrative action;
@@
 \begin{flushleft}
-................................\\
+Alen Stepic - 11-475-258\\\bigskip\bigskip  
 Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip
-................................\\
 Severin Kranz - 13-606-355\\\bigskip\bigskip
-................................\\
 Joël Sonderegger - 11-495-488\\\bigskip\bigskip
-................................\\
-Alen Stepic - 11-475-258\\\bigskip\bigskip
-................................\\
-Chi Xu - XX-XXX-XXX
+Chi Xu - 16-300-915
 

### 2018-01-05 documentation/documentation.tex
adding tweepy reference and bib
correcting citation
reformulated introduction part; Wrote Bitcoin and Twitter in capital letters

@@
 \listoffigures\bigskip 
-\section*{List of Abbreviation} 
+\section*{List of Abbreviations} 
 \begin{acronym}[ASECRETTT]
@@
 \section{Introduction}
-In the academic environment accountability and reproducibility is important.
-However, the publishing process of papers and journals seem to be outdated as reproducability is not evaluated by many journals.
-\parencite[p.~888]{mccullough2003} New ways of data collection and data processing exist by using computational economics.
-The usage of algorithms can increase effectiveness and efficiency.
+In the academic environment both accountability and reproducibility are important to ensure a high quality of research.
+However, the publishing process of scientific papers and journals seems to be outdated, as reproducibility is not evaluated by leading journals.
+\parencite[p.~888]{mccullough2003} Driven by digitisation, new ways of data collection and processing arise by using computational economics.
+On the one hand, the usage of scripts, automation or machine learning can increase effectiveness and efficiency.
 Hence, much larger data sets can be proceeded.
-However, this creates also new challenges regarding traceability and reproducibility.
-Often cited academic paper exist, where the initial computation is not reproducible \parencite[pp.~874--887]{mccullough2003}.
-Replicating data or existing results do not provide any new knowledge at all.
-Nevertheless, the ability to reproduce is key in science, and non-reproducible work can not be characterized as science or used as a basis for policy-making \parencite[p.~888]{mccullough2003}.
-This explains why reproduction is of great relevance.
+On the other hand, this creates also new challenges to trace and reproduce data sets, procedures or analysis.
+There are often cited academic papers, where the initial computation is neither clearly documented nor reproducible \parencite[pp.~874--887]{mccullough2003}.
+Replicating data or existing results does not provide any new knowledge at all.
+Nevertheless, the ability to understand what researchers have done is key.
+Non-reproducible work cannot be characterised as science or used as a basis for policy-making \parencite[p.~888]{mccullough2003}.
+Therefore, clear documentation of processes, used scripts and tools should be the basis of every scientific publication.
 
-\subsection{Goal of the paper}
-The goal of this documentation is the provision of a description.
-This description should enable the reader to reproduce the results discussed in the accompanying paper.
-Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed.
-In other words, the input data, the model core, the model parameters and the applied math program are explained.
+\subsection{Goal}
+The objective of this documentation is the provision of a description of the research process, used hardware, software, procedures or tools of the accompanying paper in detail.
+This description enables the reader to reproduce the results discussed in our work.
+Thus, it contains an explanation of how  input data have been gathered, stored, aggregated and analysed.
 
 \subsection{Methodology}
-This documentation consists out of seven chapters.
-The first five chapters are going to be discussed, as they are relevant for the reproduction of the results.
-The first chapter contains a short introduction and provides the reader with an overview of the topic.
-Furthermore, it points out the relevance of the documentation.
-In the second chapter the requirements (setup) are discussed to enable the reproducibility and run the own written code scripts in Python.
-Python has been used as it was suggested in the course Software Engineering for Economists.
-The third chapter discusses the input data.
-This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data.
-The data have been gathered by using Application Programming Interfaces (API) to ensure high quality of the data.
-The fourth chapter discusses how the data is aggregated wrangled to enable the subsequent analysis.
-The fifth chapter explains how the analysis has been conducted whit STATA.
+After pointing out the relevance of this documentation, the second chapter is an explanation of the required set-up in order to reproduce our results by running our Python scripts available from Github.
+The programming language Python has been chosen, as it comes with a high variety of modules and is especially suitable for data science.
+The third chapter discusses the input data of our project.
+This includes the process of gathering and storing tweets from Twitter, as well as the collecting Bitcoin price data for the same time frame.
+Both Twitter and Bitcoin data have been gathered by using an Application Programming Interface (API), to ensure a high data quality.
+Further on, the fourth chapter explains, how the data has been aggregated and wrangled to enable the subsequent analysis.
+The analysis has been conducted with STATA and is discussed in detail the last chapter of this documentation.
 
 \subsection{Scope}
-The scope of the documentation is the provision of an overview of the different steps which have been conducted to obtain the results in the paper.
-It does not contain any discussions about the results of the accompanying paper.
-It is not a deep description of the code as the code itself as the code is documented separately.
+The scope of the documentation is to provide an overview of the different steps that have been conducted to obtain the results of the paper.
+Therefore, this documentation includes all information necessary to understand and reproduce our findings from the accompanying paper.
+However, it does not contain any further information about the content and results of our research and is only meant as supportive material.
+Furthermore, it does not provide a detailed description of the code itself, in order to avoid redundancy of information with the existing code documentation within the scripts.
 \clearpage
 
-\section{Setup}
-This section goes through the setup that you need for exectuing the code that is discussed in this documentation.
-\subsection{Github Repository}
+\section{Set-up}
+This section goes through the set-up that you need for executing the code that is discussed in this documentation.
+\subsection{Github ritepository}
 All code is available on the following github repository:
@@
 However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}.
-On the other hand, Python offers different twitter libraries.
+On the other hand, Python offers different Twitter libraries.
 Such as the open-source package tweepy.
@@
 The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|.
-With this method all data of filtered tweets are gathered in real time.
+\parencite{tweepy} With this method all data of filtered tweets are gathered in real time.
 The main function \verb|def main()| manages the required authentication as follow:
@@
 \end{lstlisting}
-Those authentications are demanded by twitter and explained in more details in the next paragraph.
-Furthermore, the main function starts the running of the stream, while filtering for the buzzword bitcoin by processing \verb|twitterStream.filter(track=["bitcoin"]|.
+Those authentications are demanded by Twitter and explained in more details in the next paragraph.
+Furthermore, the main function starts the running of the stream, while filtering for the buzzword Bitcon by processing \verb|twitterStream.filter(track=["bitcoin"]|.
 Tweepy has been applied for this assignment because it simplify the script and enables to gather a huge number of tweets for free.
@@
 \paragraph{Twitter Authentication}\mbox{}\\{}
-To access the twitter data, twitter requests an identification of the user.
+To access the Twitter data, Twitter requests an identification of the user.
 The identification is assured by different keys and access tokens.
@@
 
-To obtain the mentioned keys and tokens a twitter account is needed.
-Once, a twitter account exist a application has to be created.
-This has to be conducted by login with the twitter account credentials under the following link:
+To obtain the mentioned keys and tokens a Twitter account is needed.
+Once, a Twitter account exist a application has to be created.
+This has to be conducted by login with the Twitter account credentials under the following link:
 \begin{lstlisting}[language=bash]
@@
 \paragraph{Running the Python Script}\mbox{}\\{}
-By running the Python script \verb|collectTwitterData.py| real-time twitter data is gathered on an ongoing basis until you stop the script forcefully.
+By running the Python script \verb|collectTwitterData.py| real-time Twitter data is gathered on an ongoing basis until you stop the script forcefully.
 \begin{lstlisting}[language=bash]
@@
 
-\subsubsection{Hardware Setup}
-As explained in the previous section the Tweepy API was used to gather tweets in real-time based on the buzzword "bitcoin".
+\subsubsection{Hardware set-up}
+As explained in the previous section the Tweepy API was used to gather tweets in real-time based on the buzzword "Bitcon".
 The Python script was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
@@
 
-\subsubsection{API: Bitcoinaverage.com}
+\subsubsection{API: bitcoinaverage.com}
 Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin.

### 2018-01-05 documentation/documentation.tex

@@
 The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|.
-\parencite{tweepy} With this method all data of filtered tweets are gathered in real time.
-The main function \verb|def main()| manages the required authentication as follow:
+With this method all data of filtered tweets are gathered in real time.
+\parencite{tweepy} The main function \verb|def main()| manages the required authentication as follow:
 \begin{lstlisting}[language=bash]

### 2018-01-05 documentation/documentation.tex
corrected spelling, punctuation and grammar in sections 2, 3 and 4; ensured captial letters for the word Python

@@
 \section{Set-up}
-This section goes through the set-up that you need for executing the code that is discussed in this documentation.
-\subsection{Github ritepository}
-All code is available on the following github repository:
+This section goes through the set-up that is necessary in order to execute the code discussed in this documentation.
+
+\subsection{Github repository}
+All code is available on the following Github repository:
 \newline
@@
 
-You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
+You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from \verb|python.org|.
 \newline \newline
-On top you need various Python packages.
+On top, you need various Python packages.
 We created a requirements file \verb|requirements.txt|, which contains all required packages to run the Python scripts of this project.
-You can find the  \verb|requirements.txt| in the root directory of our github repository.
+You can find the \verb|requirements.txt| in the root directory of our Github repository.
 The list of packages can be installed using pip install like so:
@@
 When seeking for statistical analysis, regression analysis or data management, STATA is a capable tool.
-To reproduce our results, you need to have the STATA software installed in your local computer and after starting the program you can follow the guidelines in chapter 4 (data analysis).
+To reproduce our results, you need to have the STATA software installed on your local computer.
+After starting the program you can follow the guidelines in chapter 5 (Data Analysis).
 
@@
 \section{Data Collection}
-This section contains a detailed description of how the data for the sequential analysis is gathered and stored.
+The following section contains a detailed description of how the data for the sequential analysis is gathered and stored.
 Two separate data sets will be collected: (1) Tweets data and (2) Bitcoin price index data.
 \subsection{Tweets Data}
-Whit the Python script real-time Twitter data are streamed and stored. This happens with help of a Raspberry Pi.
+With the Python script real-time Twitter data are streamed and stored using the Python library Tweepy. A Raspberry Pi can be used to gather Twitter data over a longer period.
 \subsubsection{Python Script}
-Twitter offers different API for collecting data.
-However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}.
-On the other hand, Python offers different Twitter libraries.
-Such as the open-source package tweepy.
+Twitter offers different APIs for the collection of Twitter data.
+However, the time frame to gather data from the past with full access is limited to seven days \parencite{twitterinc2017a}.
+To gather a data set over a longer period, without using payed services Twitter data therefore have to be streamed and saved in real-time.
+Python offers different Twitter libraries such as the package Tweepy.
 
@@
 It provides a simple way to gather real time tweets, by managing authentication, connection and tweet information of Twitters streaming API.
-The tweepy instance tweepy.streaming is used for the streaming session and forwards the data to the StreamListener instance.
+The Tweepy instance tweepy.streaming is used for the streaming session and forwards the data to the StreamListener instance.
 The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|.
-With this method all data of filtered tweets are gathered in real time.
-\parencite{tweepy} The main function \verb|def main()| manages the required authentication as follow:
+With this method all data of filtered tweets are gathered in real-time.
+\parencite{tweepy} The main function \verb|def main()| manages the required authentication as follows:
 \begin{lstlisting}[language=bash]
@@
 Those authentications are demanded by Twitter and explained in more details in the next paragraph.
-Furthermore, the main function starts the running of the stream, while filtering for the buzzword Bitcon by processing \verb|twitterStream.filter(track=["bitcoin"]|.
-Tweepy has been applied for this assignment because it simplify the script and enables to gather a huge number of tweets for free.
+Furthermore, the main function starts to run the stream, while filtering for the buzzword "Bitcoin" by processing \verb|twitterStream.filter(track=["bitcoin"]|.
+Tweepy has been applied for this project because it simplifies the script and enables its users to gather a huge number of tweets without any costs.
 
 \paragraph{Installing Tweepy}\mbox{}\\{}
-Tweepy is installed very simply by running following commands in the command prompt. 
+Tweepy is installed easily by running following commands in the command prompt. 
 \begin{lstlisting}[language=bash]
@@
 
-If the previous downloaded python installation package does not contain the tweepy library, the tweepy package has to be downloaded. The package can be downloaded for free from the following link:
+If the previously downloaded Python installation package does not contain the tweepy library, the tweepy package has to be downloaded manually.
+The package can be downloaded for free from the following link:
 \begin{lstlisting}[language=bash]
@@
 To obtain the mentioned keys and tokens a Twitter account is needed.
-Once, a Twitter account exist a application has to be created.
-This has to be conducted by login with the Twitter account credentials under the following link:
+Once, a Twitter account exists, an application has to be created by logging in the developer area with the credentials under the following link:
 \begin{lstlisting}[language=bash]
@@
 
-After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.\\
+After the creation of an application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.\\
 \begin{figure}[H]
@@
 
-The Tweepy API provides the tweets data in a Java Script Object Notation (JSON) format.
+The Twitter API provides the tweets data in a Java Script Object Notation (JSON) format.
 Tweets are only received in case a tweet contains the predefined key word \verb|bitcoin|.
@@
 The \verb|text| attribute needs to be encoded from the raw JSON format into the UTF-8 format for further analysis.
-After successfully encoding the \verb|text| attribute a tweet is appended to the \verb|twitterData.csv| file as a new row and saved in the fo
+After successfully encoding the \verb|text| attribute a tweet is appended to the \verb|twitterData.csv| file as a new row and saved in the data folder.
 
-Furthermore, to ensure a high quality data set it needs to be complete without missing any data points for the observed period.
-Thus, we have built in an exception handler into the \verb|collectTwitterData.py| script.
+To ensure a high quality data set, without missing any data points for the observed period, we have built in an exception handler into the \verb|collectTwitterData.py| script.
 If an error occurs an email will be sent with the error message.
-Additionaly, any exception that occurs during the exectuing of the script will be added to the log file \verb|/data/tweet_collection_error_log.csv|.
+Additionally, any exception that occurs during the execution of the script will be added to the log file \verb|/data/tweet_collection_error_log.csv|.
 
 \subsubsection{Hardware set-up}
-As explained in the previous section the Tweepy API was used to gather tweets in real-time based on the buzzword "Bitcon".
+As explained in the previous section the Twitter API was used to gather tweets in real-time based on the buzzword "Bitcoin" by using Tweepy.
 The Python script was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
 This approach allowed us to ensure a continuous data stream while being able to access the program output regardless of time and location.
-Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient option compared to a personal computer or NAS Server.
-The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\\
+Furthermore, due to a low energy consumption of the RPI, the method is also the most cost efficient option compared to a personal computer or NAS Server.
+The following section describes the different steps that have been taken in order to set up the RPI 2, SSH, Git and Python3.\\
 
@@
 \begin{enumerate}
-\item Install Python3 using the command: sudo apt-get install Python3 \newline
-\item Install the tweepy module for python using the command
+\item Install Python3 using the command: \begin{lstlisting}[language=bash]
+sudo apt-get install Python3
+\end{lstlisting}
+\item Install the tweepy module for Python using the command
 \begin{lstlisting}[language=bash]
@@
 
-In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.
+In summary, this approach worked well and ran smoothly. A clean set-up is recommended to ensure a continuous data stream over a longer period.
 
 \subsection{Bitcoin Price Data}
-We wrote a Python script which collects Bitcoin price data as there was no preexisting data set that satisfied our needs.
+We wrote a Python script which collects Bitcoin price data as there was no pre-existing data set that satisfied our needs.
 The Bitcoin price is best expressed by the Bitcoin Price Index.
@@
 The objective of the script was to gather hourly Bitcoin Price Index data for at least the time period in which we gather the tweets data.
-We found the an API by bitcoinaverage.com which sufficed our needs.
-An API description follows later.
+We found the an API by bitcoinaverage.com which was sufficed our needs.
+A detailed description of the API follows in section 3.2.3.
 
 \subsubsection{Execution}
-By executing the python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
+By executing the Python script \verb|collectCryptocurrencyData.py| hourly data for the Bitcoin Price Index is retrieved.
 \begin{lstlisting}[language=bash]
@@
 \subsubsection{Output}
-After successfully running the python script \verb|CollectCryptocurrencyData.py| the file \verb|bpi.csv| is generated in the folder \verb|/data|.
+After successfully running the Python script \verb|CollectCryptocurrencyData.py| the file \verb|bpi.csv| is generated in the folder \verb|/data|.
 It is important to note that every execution of the script overwrites any existing \verb|bpi.csv| file.
@@
 The registration and generation of an API key is freely available on bitcoinaverage.com.
-The collectCryptocurrencyData.py already contains the necessary keys.
-This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.
+The \verb|collectCryptocurrencyData.py| already contains the necessary keys.
+This means that you need no register or generate keys to execute the script \verb|collectCryptocurrencyData.py.|
 \begin{lstlisting}[language=bash]
@@
 After the tweets and BPI data set is generated needs to be aggregated before it can be analyzed.
-In addition, some data wrangling is necessary to bring the data in a format which than can be analyzed.
-The script \verb|aggregateTwitterBpi.py| does all this.
+In addition, some data wrangling is necessary to bring the data in a format which than can be analysed.
+The script \verb|aggregateTwitterBpi.py| does all of these steps.
 
@@
 
-Here a short description of what happens at the various steps: 
+Short description of what happens at the various steps: 
 \paragraph{Load BPI data set}\mbox{}\\
@@
 
-\paragraph{Count number of tweets on an hourly basis}\mbox{}\\ F
-irst, groups the tweets by hour. Second, counts the number of tweets for every hour.
+\paragraph{Count number of tweets on an hourly basis}\mbox{}\\ First, groups the tweets by hour. Second, counts the number of tweets for every hour.
 
@@
 The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated.
-Again, the reason for calculating these values is given in the data analysis section.
+Again, the reason for calculating these values is given in chapter 5 (Data Analysis).
 
 \paragraph{Merge number of tweets with BPI data (incl. first differences)}\mbox{}\\
-Up to this point there are the two seperate data frames df\_tweets\_per\_hour and df\_bpi.
+Up to this point, there are the two separate data frames df\_tweets\_per\_hour and df\_bpi.
 
@@
 \subsection{Execution}
-By executing the Python script \verb|aggregateTwitterBpi.py| a aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
+By executing the Python script \verb|aggregateTwitterBpi.py| an aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
 \begin{lstlisting}[language=bash]
@@
 \subsection{Output}
-After successfully running the Python script \verb|aggregateTwitterBpi.py| the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
+After successfully running the Python script \verb|aggregateTwitterBpi.py|, the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
 It is important to note that every execution of the script overwrites any existing \verb|nr_of_tweets_bpi_closing_price.csv| file.

### 2018-01-05 documentation/documentation.tex
adjusted punctuation grammar and spelling section5

@@
 
-\subsection{Stata}
+\subsection{STATA}
 For the data analysis, we used the statistical software STATA (version 14.2).
@@
 The data analysis was performed with the statistical software STATA (version 14.2).
-The corresponding stata file and .do file are stored in the folder stata\_analysis.
-Following we describe all the commands used to produce our econometric model.
+The corresponding .dta file and .do file are stored in the folder stata\_analysis of the Git repository.
+Following, we describe all the commands used to produce our econometric model.
 
 Step 1:\\
-After starting stata the first step was to import the data file (.csv file) into stata. We did so by following command (be carefull your location of the .csv file will differ):\\
+After starting STATA the first step was to import the data file (.csv file) into STATA. We did so by following command (be careful, your location of the .csv file will differ):\\
 \begin{lstlisting}[language=bash]
@@
 STATA is not recognizing our variable "time" as a date variable.
-Therefore we create a new variable "time2" and giving it the same values as "time" in the same format as "time".
-At the end we define "time2" to be a time series with an hourly progress\\
+Therefore, we create a new variable "time2" and giving it the same values as "time" in the same format as "time".
+At the end, we define "time2" to be a time series with an hourly progress.\\
 	\begin{lstlisting}[language=bash]
@@
 Step 4:\\
-To check for stationarity we run the Augmented Dickey-Fuller (ADF) test for all variables with a time delay of 0 periods (lag 0).\\
+To check for stationarity, we run the Augmented Dickey-Fuller (ADF) test for all variables with a time delay of 0 periods (lag 0).\\
 	\begin{lstlisting}[language=bash]
@@
 
-Additionally:\\
-The VAR regression results were exportet to a latex format by instaling and using the outreg2 package.
+Step 8:\\
+The VAR regression results were exported to a latex format by installing and using the outreg2 package.
 The generated piece of latex code was then inserted into in the latex file of the paper.

### 2018-01-05 paper/paper.tex
resolve merge issue

--- 2018-01-04 paper/paper.tex
@@
 The goal should be reached by answering the following research question: \\
-In what extent does the amount of Twitter tweets about Bitcoin has an effect on the price movement of Bitcoin?
+To what extent does the amount of Twitter tweets about Bitcoin has an effect on the price movement of Bitcoin?
 

### 2018-01-05 paper/paper.tex
added and sorted acronyms, added footnotes

@@
 
-\section*{List of Abbreviation} 
+\section*{List of Abbreviations} 
 \begin{acronym}[ASECRETTT]
-\acro{VAR}{Vector Autoregression}
+\acro{ADF}{Augmented Dickey-Fuller}
+\acro{AIC}{Akaike Information Criterion}
 \acro{EMH}{Efficient Market Hypothesis}
 \acro{etc}{et cetera}
+\acro{HQIC}{Hannan–Quinn information criterion}
+\acro{SBIC}{Schwarz-Bayesian Information Criterion}
+\acro{VAR}{Vector Autoregression}
 \end{acronym}
@@
 The goal should be reached by answering the following research question: \\
-To what extent does the amount of Twitter tweets about Bitcoin has an effect on the price movement of Bitcoin?
+To what extent does the amount of Twitter tweets about Bitcoin correlate with the price movement of Bitcoin?
 
@@
 From our data collection, we are left with two time series datasets representing two variables.
-A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach.
+A broadly used statistical method to simultaneously analyse multiple time series is the Vector Autoregression (VAR) approach.
 In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
@@
 We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference Twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets).
-The results of the augmented Dickey-Fuller test are listed in the following table:\\
+The results of the augmented Dickey-Fuller (ADF) test are listed in the following table:\\
 
@@
 To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria.
-Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
+Information criteria measure the trade-off between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}).
 The calculations of these criteria for our specific data set are shown in the following table.\\
@@
 
-As can be seen, STATA calculates and presents various information criteria (AIC: Akaike Information Criterion, HQIC: Hannan–Quinn information criterion, SBIC: Schwarz-Bayesian Information Criterion).
-The asterisk indicates the optimal lag lenght to use for the regression analysis.
+As can be seen, STATA calculates and presents various information criteria (AIC\footnote{Akaike Information Criterion}, HQIC\footnote{Hannan–Quinn information criterion}, SBIC\footnote{Schwarz-Bayesian Information Criterion}).
+The asterisk indicates the optimal lag length to use for the regression analysis.
 In this case all criteria suggest a lag length of 1.

### 2018-01-05 paper/paper.tex
adjusted Abstract

@@
 \pagenumbering{Roman}
-This paper, examines the dynamics between the amount of Twitter activity regarding Bitcoin and the actual price fluctuation of Bitcoin.
-For the analysis two sets of data have been collected.
-One reflecting Twitter activity and the other one showing the Bitcoin prices for the same period.
-Based on that an econometric model is used for the statistical analysis and the interpretation of the results.\\
-The evaluation of the model showed that changes in Twitter activity on Bitcoin have a minimal and insignificant effect on the future price development of Bitcoin.
-Accordingly, aggregate Twitter fees are not a good source to predict changes in Bitcoin prices.
-This result must be understood with caution, because it only applies for the specific time interval of our observations, which is about 8 days and not for the past or future trend of cryptocurrencies.
+Based on previous research in the stock market, this paper uses a Twitter sentiment analysis to determine the dynamics between the amount of Twitter activity regarding Bitcoin and the market price of Bitcoin.
+The analysis is based on two different data sets.
+Twitter activity has been measured by the number of tweets containing the term "Bitcoin" while Bitcoin prices were measured in the Bitcoin price index.
+The Vector Autoregression (VAR) model was used for the statistical analysis and the interpretation of the results.\\
+
+The evaluation of the econometric model showed that changes in Twitter activity on Bitcoin have only a minimal and insignificant effect on the future price development of Bitcoin.
+This result must be understood with caution, because it only applies for the specific time interval of 8 days in which Twitter data have been gathered.
+Further on, researchers are being encouraged to elaborate on our observations, by applying our methodology over a longer time period and for additional cryptocurrencies.
 \\
-This work was created in the context of a programming course for economists at the university of St.
-Gallen.
-To not exceed the framework of this study we require extensive knowledge in econometrics and take concepts as known.
-The underlying goal was to get familiar with software engineering tools and project management.
-Therefore, the academic content of this work is neither completed nor concluding.\\
+
 \end{abstract}
@@
 \listoffigures\bigskip\bigskip
+
 \listoftables

### 2018-01-05 paper/paper.tex
adjusted and corrected chapter 1

@@
 The large fluctuation of the Bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on Bitcoin and Twitter.
-\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices.
-As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict Bitcoin prices.
+\textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword "bullishness" can indeed be used as a sentiment indicator for stock prices.
+As the modern economy becomes more digitised, crypotocurrencies, as a financial asset, draw more attention.
+This paper seeks to shed light on whether the tweets can be used to predict Bitcoin prices.
 
@@
 
-As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter.
+As existing research focuses mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter.
 The goal should be reached by answering the following research question: \\
-To what extent does the amount of Twitter tweets about Bitcoin correlate with the price movement of Bitcoin?
+To what extent does the number of tweets about Bitcoin correlate with the price movement of Bitcoin?
 
@@
 \label{sec:Methodology}
-To answer the above mentioned research question a scientific approach has been applied.
+To answer the above mentioned research question, a scientific approach has been applied.
 The paper consists out of three parts.
-The first part contains an introduction into the topic by pointing out the relevance of the topic, the research question, methodology and the scope.
-This is conducted in chapter \ref{sec:intro}.
-The second part is characterized as the theory part.
-The theory aims to provide the reader with the necessary background information by introducing relevant Bitcoin and Twitter information in context of the paper.
-The conducted research is based on forward research and using relevant sources.
-Furthermore, it contains a short introduction into the Vector Autoregression (VAR) approach and its constrains in context with the paper.
-This is conducted in chapters \ref{sec:Background} and \ref{sec:EconometricModellingandResults}.
-The third part contains the discussion of the results and a conclusion.
-The conclusion is based on the theory and our mathematical computation.
-The computation is based on a data set, which was gathered by coded python scripts for the time period December 20th - 27th.
+First, the relevance of the topic is pointed out by the introduction , the research question, methodology and the scope (see chapter \ref{sec:intro}).
+Secondly, the related theory has been analysed to provide the reader with the necessary background information by briefly introducing both Bitcoin and Twitter in context of price prediction and behavioural finance.
+The covered research is based on forward research in regard to the stock market and cryptocurrencies with a special focus on sentiment analysis and Bitcoin \ref{sec:Background}.
+Further on,  Vector Autoregression (VAR) approach is introduced and its constrains in context of the paper are being outlined (see chapter \ref{sec:EconometricModellingandResults}).
+The third part contains the discussion of the results.
+The computation is based on a data set, which was gathered by Python scripts for the time period December 20th - 27th.
 Since the results are based on the observation of a short period, they have to be interpreted carefully.
 The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "Bitcoin" and (2) those containing historical Bitcoin prices.
-The two sources has been aggregated with another python script.
-The output of aggregation was further processed with Stata to conduct the VAR on a daily basis.
-The third part of the paper is discussed in the chapters \ref{sec:EconometricModellingandResults} and \ref{sec:Conclustion}.
+The two sources have been aggregated by using Python.
+The output of the aggregation was further processed with STATA.
+The third part of the paper is discussed in the chapter \ref{sec:EconometricModellingandResults} followed by a brief conclusion in chapter \ref{sec:Conclustion}.
 
@@
 The paper's focus lies on the scientific discussion of empirical test results.
-The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results.
-As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days.
-However, the results provide a first impression and can be further be developed.
-The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in a separate documentation paper.
+The research question has consciously been narrowed,in order to build up on a existing methodology for sentiment analysis in the stock market while simultaneously extending the research scope in the area of behavioural finance and sentiment analysis for cryptocurrencies.
+The short time frame of our project further limited the period of data collection which has a direct impact on the reliability of our results.\\
+Further on, this paper should act as a blueprint for further research in the area of Twitter sentiment analysis for cryptocurrencies.
+Therefore, the accompanying project documentation can be used as a guideline for further research.
 
@@
 As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics.
-In comparison to other social networks, twitter limits its posts (tweets) to relatively short messages of 140 characters.
+In comparison to other social networks, Twitter limits its posts (tweets) to relatively short messages of 140 characters.
 Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos.
@@
 Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
-Based on analysis of the influence of twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
+Based on analysis of the influence of Twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
 
@@
 This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term.
-The second equation is directly relevant to our research question, as it allows to look into the correlation between the present bitcoin price and the past tweet count.\\
+The second equation is directly relevant to our research question, as it allows to look into the correlation between the present Bitcoin price and the past tweet count.\\
 

### 2018-01-05 documentation/documentation.tex
final reading and minor grammar/spelling changes

@@
 However, the publishing process of scientific papers and journals seems to be outdated, as reproducibility is not evaluated by leading journals.
-\parencite[p.~888]{mccullough2003} Driven by digitisation, new ways of data collection and processing arise by using computational economics.
+\parencite[p.~888]{mccullough2003} Driven by digitalization, new ways of data collection and processing arise by using high computational capacity and advanced econometric methods.
 On the one hand, the usage of scripts, automation or machine learning can increase effectiveness and efficiency.
@@
 \subsection{Goal}
-The objective of this documentation is the provision of a description of the research process, used hardware, software, procedures or tools of the accompanying paper in detail.
+The objective of this documentation is to provide a detailed description of the research process, used hardware, software, procedures and tools of the accompanying paper.
 This description enables the reader to reproduce the results discussed in our work.
-Thus, it contains an explanation of how  input data have been gathered, stored, aggregated and analysed.
+Thus, it contains an explanation of how  input data have been gathered, stored, aggregated and analyzed.
 
@@
 Further on, the fourth chapter explains, how the data has been aggregated and wrangled to enable the subsequent analysis.
-The analysis has been conducted with STATA and is discussed in detail the last chapter of this documentation.
+Finally, the statistical analysis has been conducted with STATA and is discussed in the last chapter of this documentation.
 
@@
 \subsection{STATA}
-For the data analysis, we used the statistical software STATA (version 14.2).
+For the statistical analysis of our data, we used the statistical software STATA (version 14.2).
 When seeking for statistical analysis, regression analysis or data management, STATA is a capable tool.
 To reproduce our results, you need to have the STATA software installed on your local computer.
-After starting the program you can follow the guidelines in chapter 5 (Data Analysis).
+After starting the program, you can follow the guidelines in chapter 5 (Data Analysis).
 
@@
 The data analysis was performed with the statistical software STATA (version 14.2).
-The corresponding .dta file and .do file are stored in the folder stata\_analysis of the Git repository.
+The corresponding .dta file and .do file are stored in the folder stata\_analysis in the Github repository.
 Following, we describe all the commands used to produce our econometric model.
@@
 Step 1:\\
-After starting STATA the first step was to import the data file (.csv file) into STATA. We did so by following command (be careful, your location of the .csv file will differ):\\
+After starting STATA the first step was to import the data file (.csv file). We did so by following command (be careful, your location of the .csv file will probably differ):\\
 \begin{lstlisting}[language=bash]
@@
 STATA is not recognizing our variable "time" as a date variable.
-Therefore, we create a new variable "time2" and giving it the same values as "time" in the same format as "time".
+Therefore, we had to create a new variable "time2" and give it the same values as "time" in the same format as "time".
 At the end, we define "time2" to be a time series with an hourly progress.\\
@@
 Step 6:\\
-Running the VAR regression for our two variables. With recommended lag of 1 (from Step 4).\\
+Running the VAR regression for our two variables. With recommended lag of 1 (from Step 5).\\
 	\begin{lstlisting}[language=bash]

### 2018-01-05 paper/paper.tex
final reading of paper.tex and minor grammar/spelling changes

@@
 The digitalisation leads to an increased network effect, where information can be shared over the globe.
-Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors.
+Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioral and emotional role of investors.
 The large fluctuation of the Bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on Bitcoin and Twitter.
 \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword "bullishness" can indeed be used as a sentiment indicator for stock prices.
-As the modern economy becomes more digitised, crypotocurrencies, as a financial asset, draw more attention.
+As the modern economy becomes more digitised, cryptocurrencies, as a financial asset, draw more attention.
 This paper seeks to shed light on whether the tweets can be used to predict Bitcoin prices.
@@
 The paper consists out of three parts.
-First, the relevance of the topic is pointed out by the introduction , the research question, methodology and the scope (see chapter \ref{sec:intro}).
-Secondly, the related theory has been analysed to provide the reader with the necessary background information by briefly introducing both Bitcoin and Twitter in context of price prediction and behavioural finance.
+First, the relevance of the topic is pointed out by the introduction, the research question, methodology and the scope (see chapter \ref{sec:intro}).
+Secondly, the related theory has been analysed to provide the reader with the necessary background information by briefly introducing both Bitcoin and Twitter in context of price prediction and behavioral finance.
 The covered research is based on forward research in regard to the stock market and cryptocurrencies with a special focus on sentiment analysis and Bitcoin \ref{sec:Background}.
@@
 The paper's focus lies on the scientific discussion of empirical test results.
-The research question has consciously been narrowed,in order to build up on a existing methodology for sentiment analysis in the stock market while simultaneously extending the research scope in the area of behavioural finance and sentiment analysis for cryptocurrencies.
+The research question has consciously been narrowed, in order to build up on a existing methodology for sentiment analysis in the stock market while simultaneously extending the research scope in the area of behavioral finance and sentiment analysis for cryptocurrencies.
 The short time frame of our project further limited the period of data collection which has a direct impact on the reliability of our results.\\
@@
 
-In previous research \textcite{madan2015automated} applied \textit{machine learning} algorithms to predict Bitcoin prices.
+In previous research, \textcite{madan2015automated} applied \textit{machine learning} algorithms to predict Bitcoin prices.
 By using the \textit{bayesian regression}, \textcite{shah2014bayesian} achieved a return on investment of 89 percent over an investment period of 50 days.
@@
 
-One core assumption of behavioural finance is that investors’ interests influence their behaviour and therefore stock prices (\cite[p.~3]{mao2015quantifying}).
+One core assumption of behavioral finance is that investors’ interests influence their behavior and therefore stock prices (\cite[p.~3]{mao2015quantifying}).
 A widely used approach to measure investors’ interests is the sentiment analysis of Twitter data, which will be covered in the following section.\\
@@
 In comparison to other social networks, Twitter limits its posts (tweets) to relatively short messages of 140 characters.
-Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos.
-Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(\cite{Schmidt2018socialmedia})\\
+Tweets can contain observations, thoughts, links to various content, websites, uploaded pictures or videos.
+Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles (\cite{Schmidt2018socialmedia}).\\
 
@@
 In the second and third plots we respectively did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
-The graphs show overall a cyclical movement around 1200 tweets and a single outburst befalling on 22.12.2017 between 15:00:01 and 21:00:00, with highest value being 4622 tweets in one hour.\\
+The graphs show overall a cyclical movement around 1200 tweets per hour and a single outburst befalling on 22.12.2017 between 15:00:01 and 21:00:00, with highest value being 4622 tweets in one hour.\\
 
@@
 The first plot shows the hourly changes of Bitcoin prices.
-The second and third plots are once again first difference transormations of the main variable for later analysis.
-In this graph we observe a notably volatile movement with no spesific direction.
-This contradicts the general rising trend of Bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when Bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
+The second and third plots are once again first difference transformations of the main variable.
+In this graph we observe a notably volatile movement with no specific direction.
+This contradicts the general rising trend of Bitcoin prices of the past months.
+The problem may indeed arise if we happen to select a short period of one week when Bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
 
@@
 From our data collection, we are left with two time series datasets representing two variables.
-A broadly used statistical method to simultaneously analyse multiple time series is the Vector Autoregression (VAR) approach.
-In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
+A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach.
+In this method, the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
 To generate the following econometric results we used the statistical software STATA.
@@
 Namely, we need to demonstrate that the means and variances are constant over time, and that the dataset does not show any trending behavior.
-Non-stationary data can lead to an inaccurate estimation with VAR model.
-To conduct stationarity test, we use the Augmented Dickey-Fuller (ADF) test.\\
+Non-stationary data can lead to an inaccurate estimation.
+To conduct stationarity, we use the Augmented Dickey-Fuller (ADF) test.\\
 
-We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference Twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets).
+We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference (df\_nr\_of\_tweets) and the logarithmic first difference (log\_df\_nr\_of\_tweets) transformations.
 The results of the augmented Dickey-Fuller (ADF) test are listed in the following table:\\
@@
 
-From the results we can see that only the first variable (i.e.
-the untransformed tweet count) is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence.
-The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis with only the first difference tweet count, whose test statistic falls furthest into the rejection zone.\\
+From the results we can see that only the first variable is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence.
+The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis with only the first difference tweet count.\\
 
 Out of the similar concern stated above, we shall check for stationarity for the second variable, the Bitcoin prices (variable name: bpi\_closing\_price).
-As before, we also include the first difference Bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference ones (variable name: log\_df\_bpi\_closing\_price) transformations.
+As before, we also include the first difference Bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference (variable name: log\_df\_bpi\_closing\_price) transformations.
 The ADF test for these variables gives the following results:\\
@@
 
-\begin{table}
+\begin{table}[H]
 \centering

### 2018-01-05 documentation/documentation.tex
edit documentation.tex. small typos and complements

@@
 \vspace{1.2cm}
-{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
+{Supervisor:\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
 \vspace{0.8cm}
@@
 This includes the process of gathering and storing tweets from Twitter, as well as the collecting Bitcoin price data for the same time frame.
-Both Twitter and Bitcoin data have been gathered by using an Application Programming Interface (API), to ensure a high data quality.
+Both Twitter and Bitcoin data have been gathered by using an Application Programming Interface (API), which allow to access real-life data by a set of explicitly defined and documented methods.
 Further on, the fourth chapter explains, how the data has been aggregated and wrangled to enable the subsequent analysis.
@@
 \subsection{Tweets Data}
-With the Python script real-time Twitter data are streamed and stored using the Python library Tweepy. A Raspberry Pi can be used to gather Twitter data over a longer period.
+With the Python script \verb|collectTwitterData.py| real-time Twitter data are streamed and stored using the Python library Tweepy.
+A Raspberry Pi can be used to gather Twitter data over a longer period.
 \subsubsection{Python Script}
@@
 However, the time frame to gather data from the past with full access is limited to seven days \parencite{twitterinc2017a}.
-To gather a data set over a longer period, without using payed services Twitter data therefore have to be streamed and saved in real-time.
+To gather a data set over a longer period, without using payed services Twitter, data have to be streamed and saved in real-time.
 Python offers different Twitter libraries such as the package Tweepy.
@@
 Tweepy is installed easily by running following commands in the command prompt.
+However, this step should not be necessary if you have previously completed the above described setup using the requirements file \verb|requirements.txt|.
 \begin{lstlisting}[language=bash]
@@
     {
+        ...
         "created_at": Tue Dec 19 20:40:49 +0000 2017, 
         "text": "Singapore issues bitcoin warning after price rise - #BTC #Bitcoin #Crypto"
+        ...
     }
@@
 The \verb|text| attribute needs to be encoded from the raw JSON format into the UTF-8 format for further analysis.
-After successfully encoding the \verb|text| attribute a tweet is appended to the \verb|twitterData.csv| file as a new row and saved in the data folder.
+After successfully encoding the \verb|text| attribute a tweet is appended to the \verb|twitterData.csv| file as a new row and saved in the /data folder.
 
@@
 \subsubsection{Hardware set-up}
-As explained in the previous section the Twitter API was used to gather tweets in real-time based on the buzzword "Bitcoin" by using Tweepy.
+As explained in the previous section the Twitter API was used to gather tweets in real-time based on the buzzword "bitcoin" by using Tweepy.
 The Python script was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection.
@@
 We wrote a Python script which collects Bitcoin price data as there was no pre-existing data set that satisfied our needs.
-The Bitcoin price is best expressed by the Bitcoin Price Index.
-The Bitcoin price index (BPI) is an index of the exchange rate between the Bitcoin (BTC) and the US dollar (USD) (\cite{kristoufek2015main}).
+The Bitcoin price is best expressed by the Bitcoin Price Index (\cite{kristoufek2015main}).
+The Bitcoin price index (BPI) is an index of the exchange rate between the Bitcoin (BTC) and the US dollar (USD).
 The objective of the script was to gather hourly Bitcoin Price Index data for at least the time period in which we gather the tweets data.
-We found the an API by bitcoinaverage.com which was sufficed our needs.
+We found an API by bitcoinaverage.com which was sufficed our needs.
 A detailed description of the API follows in section 3.2.3.
@@
 The \verb|collectCryptocurrencyData.py| already contains the necessary keys.
-This means that you need no register or generate keys to execute the script \verb|collectCryptocurrencyData.py.|
+This means that you need not to register or generate keys to execute the script \verb|collectCryptocurrencyData.py.|
 \begin{lstlisting}[language=bash]
@@
 [
+    ...
     {
@@
     }
+    ...
 ]
@@
 \section{Data Aggregation and Data Wrangling}
-After the tweets and BPI data set is generated needs to be aggregated before it can be analyzed.
+After the tweets and BPI data set is generated it needs to be aggregated before the data can be analyzed.
 In addition, some data wrangling is necessary to bring the data in a format which than can be analysed.
+Some attibutes are not necessary for the subsequent analysis, thus, can be deleted in order to enhance performance and reduce data volume, while other attributes need to be generated.
 The script \verb|aggregateTwitterBpi.py| does all of these steps.
@@
 
-Short description of what happens at the various steps: 
+Here is a short description of what happens at the various steps: 
 \paragraph{Load BPI data set}\mbox{}\\
-The script takes the BPI data set that is located at \verb|data/bpi.csv|.
+The script takes the BPI data set that is located at \verb|data/bpi.csv|. Then, BPI closing prices are added to every data point.
 
@@
 The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated.
-The reason for calculating these values is given in the data analysis section.
+The reason for calculating these values is provided in chapter 5 (Data Analysis).
 
@@
 \paragraph{Merge number of tweets with BPI data (incl. first differences)}\mbox{}\\
-Up to this point, there are the two separate data frames df\_tweets\_per\_hour and df\_bpi.
+Up to this point, there are the two separate data frames df\_tweets\_per\_hour and df\_bpi. Here is an excerpt of an the two data frames look at this point:
 
@@
 \end{figure}
-By using the \verb|pandas.DataFrame.join| function the columns of the  \verb|df_tweets_per_hour| are joined with  \verb|df_bpi| on the  \verb|MultiIndex(Y, M, D, H)|.
-The code snipped looks as following\:
+By using the \verb|pandas.DataFrame.join| function the columns of the \verb|df_tweets_per_hour| are joined with  \verb|df_bpi| on the  \verb|MultiIndex(Y, M, D, H)|. The code snipped for the join \:
 \begin{lstlisting}[language=bash]
@@
 \end{lstlisting}
+An example of the joined data frame looks the following:
 \begin{figure}[H]
@@
 \subsection{Execution}
-By executing the Python script \verb|aggregateTwitterBpi.py| an aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
+By executing the Python script \verb|aggregateTwitterBpi.py| an the aggregated data set that contains number of tweets and Bitcoin Price Index, both on an hourly basis, gets generated. 
 \begin{lstlisting}[language=bash]
@@
 \subsection{Output}
-After successfully running the Python script \verb|aggregateTwitterBpi.py|, the file \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
-It is important to note that every execution of the script overwrites any existing \verb|nr_of_tweets_bpi_closing_price.csv| file.
+After successfully running the Python script \verb|aggregateTwitterBpi.py|, the file \\ \verb|nr_of_tweets_bpi_closing_price.csv| is generated in the folder \verb|/data|.
+It is important to note that every execution of the script overwrites any existing \\ \verb|nr_of_tweets_bpi_closing_price.csv| file.
 
@@
 The data analysis was performed with the statistical software STATA (version 14.2).
-The corresponding .dta file and .do file are stored in the folder stata\_analysis in the Github repository.
+The corresponding .dta file and .do file are stored in the folder  \verb|/documentation/stata_analysis/| in the Github repository.
 Following, we describe all the commands used to produce our econometric model.

### 2018-01-05 documentation/documentation.tex
final review of documentation.tex

@@
 However, the publishing process of scientific papers and journals seems to be outdated, as reproducibility is not evaluated by leading journals.
-\parencite[p.~888]{mccullough2003} Driven by digitalization, new ways of data collection and processing arise by using high computational capacity and advanced econometric methods.
+\parencite[p.~888]{mccullough2003} Driven by digitalization, new ways of data collection and processing arise, by using high computational capacity and advanced econometric methods.
 On the one hand, the usage of scripts, automation or machine learning can increase effectiveness and efficiency.
 Hence, much larger data sets can be proceeded.
-On the other hand, this creates also new challenges to trace and reproduce data sets, procedures or analysis.
-There are often cited academic papers, where the initial computation is neither clearly documented nor reproducible \parencite[pp.~874--887]{mccullough2003}.
+On the other hand, this creates also new challenges to trace and reproduce data sets, procedures or analyses.
+There are often cited academic papers, where the initial computation is neither clearly documented, nor reproducible \parencite[pp.~874--887]{mccullough2003}.
 Replicating data or existing results does not provide any new knowledge at all.
@@
 This includes the process of gathering and storing tweets from Twitter, as well as the collecting Bitcoin price data for the same time frame.
-Both Twitter and Bitcoin data have been gathered by using an Application Programming Interface (API), which allow to access real-life data by a set of explicitly defined and documented methods.
+Both Twitter and Bitcoin data have been gathered by using an Application Programming Interface (API), which allows to access real-life data by a set of explicitly defined and documented methods.
 Further on, the fourth chapter explains, how the data has been aggregated and wrangled to enable the subsequent analysis.
@@
 \subsection{STATA}
-For the statistical analysis of our data, we used the statistical software STATA (version 14.2).
+For the statistical analysis of our data, we used the statistic software STATA (version 14.2).
 When seeking for statistical analysis, regression analysis or data management, STATA is a capable tool.
@@
 Those authentications are demanded by Twitter and explained in more details in the next paragraph.
-Furthermore, the main function starts to run the stream, while filtering for the buzzword "Bitcoin" by processing \verb|twitterStream.filter(track=["bitcoin"]|.
+Furthermore, the main function starts to run the stream, while filtering for the buzzword "bitcoin" by processing \verb|twitterStream.filter(track=["bitcoin"]|.
 Tweepy has been applied for this project because it simplifies the script and enables its users to gather a huge number of tweets without any costs.
@@
 
-In summary, this approach worked well and ran smoothly. A clean set-up is recommended to ensure a continuous data stream over a longer period.
+In summary, this approach worked well and ran smoothly.
+A clean set-up is recommended to ensure a continuous data stream over a longer period.
+The final data set used for our analysis is available through the link provided in the data folder on Github.
 
@@
 The request to get the data for an per hour monthly sliding window looks as follows.
-This request require authentication that requires registration and the generation of an API key.
+This request requires an authentication that therefore the registration and generation of an API key.
 The registration and generation of an API key is freely available on bitcoinaverage.com.
 The \verb|collectCryptocurrencyData.py| already contains the necessary keys.
-This means that you need not to register or generate keys to execute the script \verb|collectCryptocurrencyData.py.|
+This means that you do not need to register or generate keys to execute the script \verb|collectCryptocurrencyData.py.|
 \begin{lstlisting}[language=bash]

### 2018-01-05 paper/paper.tex
final review of paper

@@
 The analysis is based on two different data sets.
-Twitter activity has been measured by the number of tweets containing the term "Bitcoin" while Bitcoin prices were measured in the Bitcoin price index.
+Twitter activity has been measured by the number of tweets containing the term "bitcoin" while Bitcoin prices were measured in the Bitcoin price index.
 The Vector Autoregression (VAR) model was used for the statistical analysis and the interpretation of the results.\\
@@
 Since the results are based on the observation of a short period, they have to be interpreted carefully.
-The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "Bitcoin" and (2) those containing historical Bitcoin prices.
+The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "bitcoin" and (2) those containing historical Bitcoin prices.
 The two sources have been aggregated by using Python.
@@
 In relation to Bitcoin, researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies \textcite[p.~7]{stenqvist2017predicting} , by either using a \textit{polarity classification} {-} classifying the language in tweets as either positive or negative (see \cite{colianni2015algorithmic}) {-} or a \textit{lexicon based approach} {-} attributes predefined words to specific sentiment classifications (see \cite{stenqvist2017predicting}).
-Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further.
+Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “bitcoin” without analysing investors interests any further.
 Based on analysis of the influence of Twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\
@@
 We chose the hourly basis to conduct statistical analysis with a limited amount of observations as demanded by the feasibility of such a complex project.
-For the Twitter data we aggregated by each hour all tweets mentioning "Bitcoin".
+For the Twitter data we aggregated by each hour all tweets mentioning "bitcoin".
 We used prices at the last second of every hour to represent the hourly Bitcoin price.\\
 The following figure displays the Twitter activity with regard to Bitcoin for the observed time period.
-The first plot shows the hourly change of the aggregate number of tweets containing "Bitcoin".
+The first plot shows the hourly change of the aggregate number of tweets containing "bitcoin".
 In the second and third plots we respectively did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis.
@@
 \label{sec:EconometricModellingandResults}
-As stated in the beginning, our purpose is to examine the underlying relationship between the number of tweets containing "Bitcoin" and Bitcoin price fluctuations.
+As stated in the beginning, our purpose is to examine the underlying relationship between the number of tweets containing "bitcoin" and Bitcoin price fluctuations.
 From our data collection, we are left with two time series datasets representing two variables.
@@
 Understanding, describing and predicting the current phenomenon of cryptocurrencies has been the objective of many researchers.
-A variety of methods and approaches have been applied und mixed results have been produced.
-Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between Twitter activity regarding Bitcoin and the price evolution of Bitcoin.
-After collecting hourly data for approximately 8 days we generated 2 time-series datasets and decided to perform a statistical analysis by using the Vector Autoregression (VAR) approach.\\
+A variety of methods and approaches have been applied and mixed results have been produced.
+Our goal for this project was to investigate the possibility of the existence of a correlation between Twitter activity regarding Bitcoin and the price evolution of Bitcoin.
+After collecting hourly data for 8 days, we generated two time-series datasets and decided to perform a statistical analysis by using the Vector Autoregression (VAR) approach.\\
 
-According to our regression results, changes in Twitter activity due to more or less tweets about Bitcoin have a very small and insignificant effect on future changes of Bitcoin price.
+According to our regression results, changes in Twitter activity caused by a higher or lower number of tweets about Bitcoin, have a very small and insignificant effect on future changes of Bitcoin price.
 The validity of this statement was also verified and confirmed by the Granger causality test.
 At this point, however, it must be pointed out that only a small period of time has been considered in this analysis and the results cannot be generalized for the overall trend of cryptocurrencies in the recent time or for the future.
-We are also aware that we may have observed a period of abnormal behavior of Bitcoin prices compared to the trend of the last months.\\
+We are also aware, that we may have observed a period of abnormal behavior of Bitcoin prices compared to the trend of the last months.\\
 
-We encourage further research in the same direction as this paper and would be interested to see an analysis with observations over a longer period.
+We encourage further research in the same direction as this paper could serve as a blueprint together with the accompanying process documentation and would be interested to see an analysis with observations over a longer period.
 
